---
title: "Codebook For C1 Data"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
---

```{r setup, include=F}
rm(list=ls());gc()
unlink('codebook_cache', recursive = TRUE)
guardar_tablas <- function (x,y) {writexl::write_xlsx(as.data.frame(x, keeprownames= T),paste0(y,".xlsx"))}

local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually better for debugging
  echo = TRUE  # show R code
)
ggplot2::theme_set(ggplot2::theme_bw())
pander::panderOptions("table.split.table", Inf)
#file:///C:/Users/andre/OneDrive/Escritorio/RUTS/codebook%20tutorial.pdf
#https://cran.r-project.org/web/packages/codebook/vignettes/codebook_tutorial.html
if(!require(codebook)){install.packages("codebook")}
if(!require(future)){install.packages("future")}
if(!require(dplyr)){install.packages("dplyr")}
```

```{r prepare_codebook, include=T}
load("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/9.RData")

codebook_data <- as.data.frame(CONS_C1_df_dup_SEP_2020)
# to import an SPSS file from the same folder uncomment and edit the line below
# codebook_data <- rio::import("mydata.sav")
# for Stata
# codebook_data <- rio::import("mydata.dta")
# for CSV
# codebook_data <- rio::import("mydata.csv")

muestra=0
if(muestra==1){
# omit the following lines, if your missing values are already properly labelled
codebook_data <- detect_missing(codebook_data,
    only_labelled = TRUE, # only labelled values are autodetected as
                                   # missing
    negative_values_are_missing = FALSE, # negative values are missing values
    ninety_nine_problems = FALSE,   # 99/999 are missing values, if they
                                   # are more than 5 MAD from the median
    )
}
# If you are not using formr, the codebook package needs to guess which items
# form a scale. The following line finds item aggregates with names like this:
# scale = scale_1 + scale_2R + scale_3R
# identifying these aggregates allows the codebook function to
# automatically compute reliabilities.
# However, it will not reverse items automatically.
#codebook_data <- detect_scales(codebook_data)
```
<br>

In the following Tables and graphics, there is a summary of the variables and documentation of their characteristics. This high-level summary may permit us find errors on coding, help us to understand missingness and guide us towards an objective, or lead us to more questions. If a variable contains the symbol `(*)`, it means that this variable has a concatenation of values among continuous entries in treatments.

<br>

```{r codebook}
  metadata(codebook_data)$name <- "Agreement 1 SENDA"
  metadata(codebook_data)$description <- "Information About Agreement 1 of SENDA and MINSAL. Contians information about treatments.(*) Intermediate events are collapsed and concatenated in some variables; Criteria to select values from entries that were collapsed into single treatments: Wide format(a),Maximum/Last value(b), Minimum/First value(c), Kept more vulnerable category(d), Same value(e), Largest treatment(f), Favored dgs.-a(g), Sum values(h). In case of 'tipo_de_plan_2','dias_treat_imp_sin_na', 'diff_bet_treat', 'cum_dias_trat_sin_na', 'mean_cum_dias_trat_sin_na' & 'cum_diff_bet_treat', the first variable, 10 variables were generated for each variable and represents each treatment of user, since the first(1) to the last(10)"

  #dplyr::select(-consentimiento_informado)%>%
codebook(codebook_data)


#Permite exportar los valores de cada variable de tipo factor.
invisible=9
df<-NULL
df<- data.frame()
  for (i in names(Filter(is.factor,codebook_data))) { 
        fac<-data.table::data.table(table(codebook_data[i], exclude=NULL))%>% 
            dplyr::mutate(variable=paste0(i),export=paste0(row_number(),".",V1))%>%
            dplyr::rename("cat"="V1")%>%
            dplyr::select(variable,export,cat,N)%>%
          dplyr::filter(!grepl("\\.NA$",export))
      df_titulo<-data.frame(variable=paste0(i),export=NA_character_,cat=NA_character_, N=9999999)
      df<- rbind(df,df_titulo,fac)
  }
df<-
  as.data.frame(df)%>%
    dplyr::group_by(variable)%>%
    dplyr::mutate(rn=row_number())%>%
    select(variable,rn,everything())%>%
  dplyr::ungroup()

  guardar_tablas(df, "labels_codebook")
  options(OutDec=',')
  guardar_tablas(df, "labels_codebook_comma")
  
  #1. Copiar datos del libro de códigos
  #2. Pegar en google spreadsheet codebook
  #3. Correr comando eliminar filas y eliminar columnas de la s -Z
  #4. Correr comando Añadir filas (con el 3), 
  #5. Añadir columna a la derecha de label
  #6. Separar por "/"
  #7. Fijarse que no se superponga a otra variable
  #8. Añadir columna a la derecha de A, y en B1 incorporar la siguiente fórmula: =ArrayFormula(SI(FILA(A1:A)<=COINCIDIR(2,1/(A:A<>""),1),BUSCAR(FILA(A1:A),FILA(A1:A)/SI(A1:A<>"",VERDADERO,FALSO),A1:A),))
  #8. Fijarse que la última variable tenga todas las categorías llenas con Nombre Variable Estandarizado (abajo al final)
  #9. Añadir Propiedad a la izquierda de Tipos de Datos (Data Type) (insertar a la izquierda) y poner la fórmula =BUSCARV(A4,'Base de Datos C1 Jul2020'!A:D,4,0)
  #10. Pegar como valor (para no depender de la fórmula, dejar el comentario)
  #11. Eliminar la columna A
  #12. Ver cómo lo hago con labels_codebook, ya sea para pegarlo directamente en la hoja 'para_pegar_cat_factores'
  #13. Tengo que evaluar si la coma y el punto de los decimales era problemático. #14. En una de esas abrir el archio con google drive para saltarse ese problema
  #15. Pararse en n_missing y generar una columna a la izquierda, pegando el siguiente formula: =SI(SI.ERROR(BUSCARV(CONCATENAR(A4,"_",CONTAR.SI($A$4:$A4,A4)-1),para_pegar_cat_factores!g:i,3,0),"")=9999999,"",SI.ERROR(BUSCARV(CONCATENAR(A4,"_",CONTAR.SI($A$4:$A4,A4)-1),para_pegar_cat_factores!g:i,3,0),""))
  #16. Después pararse en la columna etiquetas (debiese ser la G), y generar una columna a la derecha
  #17. Reemplazar value_labels por valores (eliminar value_labels y dejar el de la formula en formato valores), lo mismo de la columna vacia
  #18. Agregar la siguiente fórmula =SI(I4="",G4,SI.ERROR(BUSCARV(CONCATENAR(A4,"_",CONTAR.SI($A$4:$A4,A4)-1),para_pegar_cat_factores!g:i,2,0),""))
  #19. Introducir codebook file y pegar encabezados debajo de los labels antiguos
  #20. Agregar filtro 
  #21. Eliminar fila 2
  #22. Poner cie10 en la oclumna al final =SI.ERROR(BUSCARV(G4,est_cod_dsm_iv_cie10!A:C,3,0),"")
```