---
title: "Duplicated Cases in SISTRAT C1"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
  ---

<style type="text/css">

code.r{
  font-size: 8px;
}
</style>

```{r load myData, include=FALSE}
 load("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/.RData")
```

```{r setup, include = FALSE}
#Libraries used in the routine. Dont change the order
if(!require(tidyr)){install.packages("tidyr")}
if(!require(data.table)){install.packages("data.table")}
if(!require(DataExplorer)){install.packages("DataExplorer")}
if(!require(stringi)){install.packages("stringi")}
if(!require(stringr)){install.packages("stringr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(Hmisc)){install.packages("Hmisc")}
if(!require(kableExtra)){install.packages("kableExtra")}
if(!require(plotly)){install.packages("plotly")}
if(!require(rbokeh)){install.packages("rbokeh")}
if(!require(altair)){install.packages("altair")}
```

# Duplicated Cases in SISTRAT C1

There were `r CONS_C1_df %>% dplyr::filter(hash_rut_completo!="") %>% nrow()` cases with an alternative HASH key, in case the first does not match any of the proposed HASH Keys. In the following table, we can see that duplicated cases may be around 7% per yearly datasets.

```{r echo=T, paged.print=TRUE}
#Cases by year.
CONS_C1_df %>% 
      group_by(ano_bd) %>% 
      tally() %>%
      as.data.frame() %>%
      mutate(ano_bd=as.numeric(ano_bd)) %>%
      assign("cant_ano",., envir = .GlobalEnv)
CONS_C1_df %>% 
  dplyr::group_by(ano_bd) %>% 
  distinct(id) %>% 
  dplyr::summarize(n=n()) %>% 
  dplyr::mutate(ano_bd= as.numeric(ano_bd)) %>%
  dplyr::left_join(cant_ano,by="ano_bd") %>% 
  mutate(dif=`n.y`-`n.x`, "%"=paste0(round(100 * dif/`n.y`, 1), "%")) %>%
  dplyr::rename("Year"=ano_bd, "Unique ID's"=n.x, "Total Cases"=n.y, "Diff."=dif) %>%
  knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 1. Differences between cases and unique cases by year",
                 align ="cccc")  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 10)
```
&nbsp;
&nbsp;

There were `r CONS_C1_df %>% dplyr::select(ano_bd,id,HASH_KEY) %>% dplyr::group_by(ano_bd,id) %>% tally() %>% dplyr::mutate(n_col=n) %>% dplyr::filter(n>1) %>% as.data.frame() %>% reshape::cast(.,ano_bd+id~n) %>% dplyr::arrange(ano_bd,id) %>% nrow()` that has more than 1 repeated ID in a yearly dataset. This same analysis but considering more than 1 repeated HASH in a yearly dataset is around `r CONS_C1_df %>% dplyr::select(ano_bd,id,HASH_KEY) %>% dplyr::group_by(ano_bd,HASH_KEY) %>% tally() %>%  dplyr::mutate(n_col=n) %>%   dplyr::filter(n>1) %>%   as.data.frame() %>%   reshape::cast(.,ano_bd+HASH_KEY~n) %>%   dplyr::arrange(ano_bd, HASH_KEY) %>% nrow()`.

```{r echo=T, paged.print=TRUE}
  CONS_C1_df %>%
  dplyr::filter(id=="AALE119101986")  %>%
      dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>%
      dplyr::select(row, ano_bd, HASH_KEY, hash_rut_completo, id_mod,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
  knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 2. Case of example that showed more than one ID",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "250px")
```

 &nbsp;

This ID had 2 cases in 2010. The last one show 179 days of treatment, but the first only register 153. What happens if we do the same excercise but with a HASH-Key?

```{r echo=T, paged.print=TRUE}
  CONS_C1_df %>%
    dplyr::filter(HASH_KEY=="0007678b8b35fa0961d1e8110fbf9620")  %>%
      dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>%
      dplyr::select(row, ano_bd, HASH_KEY, hash_rut_completo, id_mod,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
    knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 3. Case of example that showed more than one HASH",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```

&nbsp;

This HASH in 2017 assisted to CT "Tiempo de Esperanza (PROSEC) and CT Tiempos Nuevos (PROSEC) in two opportunities (in Tiempo de Esperanza, the first time, in 2016). The first case of the year 2017, gather 266 days of treatment (must note that the same case of 2016 is equal in days of treatment, date of admission, date of discharge and cause of discharge. In case of both of the cases with admissions in "CT Tiempos Nuevos", were in Iquique and had different days of treatment between each other, the last one with 49 days vs. 34.

Considering this cases, one index could be the last treatment date (Fecha.Ultimo.Tratamiento), number of previous treatments (Numero.de.Tratamientos.Anteriores), Date of admission (fech_ing), Date of discharge (fech_egres) and cause of discharge (motivodeegreso).

**We need to distinguish between duplicated cases and admissions through 2010 to 2019**  

There were `r CONS_C1_df %>% dplyr::mutate(concat=paste0(id,"_",HASH_KEY,"_",fech_ing,"_",fech_egres,"_",motivodeegreso,"_",dias_trat,"_",Fecha.Ultimo.Tratamiento)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% nrow() ` (which represents the 73.2% of the 163,146 cases), with distinct cases with a unique ID, HASH, date of admission, date of discharge, cause of discharge, days treated and days of last treatment. Comparing the explanatory power of each variable: cause of discharge does not impact in the number of unique cases, maintaining other variables, neither dates of admission and discharge removed separately, maintaining the other variables, but if both are removed, we get `r CONS_C1_df %>% dplyr::mutate(concat=paste0(id,"_",HASH_KEY,"_",motivodeegreso,"_",dias_trat,"_",Fecha.Ultimo.Tratamiento)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% nrow()` unique cases. Days of treatment does, lowering into `r  CONS_C1_df %>% dplyr::mutate(concat=paste0(id,"_",HASH_KEY,"_",fech_ing,"_",fech_egres,"_",motivodeegreso,"_",Fecha.Ultimo.Tratamiento)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% nrow()` unique cases. If we remove the ID we get `r CONS_C1_df %>% dplyr::mutate(concat=paste0(HASH_KEY,"_",fech_ing,"_",fech_egres,"_",motivodeegreso,"_",dias_trat,"_",Fecha.Ultimo.Tratamiento)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% nrow() ` unique cases.

&nbsp;

```{r echo=F, paged.print=TRUE}
  CONS_C1_df %>%
    dplyr::mutate(concat=paste0(id_mod,"_",HASH_KEY,"_",fech_ing,"_", fech_egres,"_",
                                motivodeegreso,"_", dias_trat,"_",Fecha.Ultimo.Tratamiento)) %>%
    dplyr::filter(id=="MASO113121967") %>% 
    dplyr::select(-id, -TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>%
      dplyr::select(row, ano_bd, HASH_KEY, hash_rut_completo, id_mod,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
  knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 4. Case of example that showed more than one concatenated (concat) criteria",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```
&nbsp;

In Table 4 we can appreciate that this case had 1671 days of treatment, which is far from the 1095 days proposed by the SENDA professional, and being admitted from 2013-05-08 to 2017-12-04.

However, these distinctions may be arbitrary, since ID or HASH may be biased. In the following examples, We will show cases in which the HASH or ID may be confusing.

Of the `r CONS_C1_df %>% nrow()` cases, around `r CONS_C1_df %>%  mutate(concat=paste0(id,"_",HASH_KEY)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% nrow()` had a unique combination of ID and HASH. There are `r CONS_C1_df %>%  dplyr::distinct(HASH_KEY, .keep_all = TRUE) %>% nrow()` unique HASHs, and `r CONS_C1_df %>%  dplyr::distinct(id, .keep_all = TRUE) %>% nrow()` unique IDs.

&nbsp;



```{r echo=F, paged.print=TRUE}
CONS_C1_df %>% 
  dplyr::filter(HASH_KEY=="0a36a632748c09dcf24fdc962bde1f1a"|HASH_KEY=="f962de15f9497f826905d858dbabd4b4"|HASH_KEY=="c65548c5f42e998f306235e5a4b808f1"|HASH_KEY=="f7dd4290da3ce3c118204b7097053150"|HASH_KEY=="abe310c84a4fc081f4eedf8004680207"|HASH_KEY=="f10a0720f991874eb71b7c620c6c585e") %>%
  dplyr::arrange(HASH_KEY, ano_bd, row) %>%
    dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>%
      dplyr::select(row, ano_bd, HASH_KEY, hash_rut_completo, id_mod,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
 knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 5. Examples of problematic HASHs",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "450px")
```

&nbsp;

There were `r CONS_C1_df %>% mutate(concat=paste0(id,"_",HASH_KEY)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% dplyr::filter(duplicated(HASH_KEY)) %>% dplyr::arrange(HASH_KEY) %>%  dplyr::select(HASH_KEY,id,hash_rut_completo) %>% nrow()` cases with duplicated ID's en each hash. This represents a `r paste0(round((4414/136146)*100,1),"%")` of the total cases.


For example, the first randomly selected HASHs with different id's, had 6 ("ROAN115061980", "ROAN106061980", "ROAN115062014", "ROAN115101980", "ROAN116051980" and "ROAN115061999"), the second had 3 different id's ("YECH213011983", "YECH213011982" and "JECH213011983"), the third had 3 ("DACO104121968", "DACO104121965" and "DACO104121966"), the fourth had 3 ("ELGA214031992", "ELGA214031991", "ELGR203031991") and the fifth had 3 ("JICA215051979", "JIBE215051979" and "XIBE215051979").


```{r echo=F, paged.print=TRUE}
CONS_C1_df %>% 
  dplyr::filter(id=="MASA124091985"|id=="NIAG108091996"|id=="JUGA108021973"|id=="MAMO108111971") %>%
  dplyr::arrange(id) %>%
      dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>%
      dplyr::select(row, ano_bd, HASH_KEY, hash_rut_completo, id_mod,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
 knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 6. Examples of problematic IDs",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```
&nbsp;

In this case, we can appreciate that an id like "JUGA108021973"contain different HASH_KEYs: `r  CONS_C1_df %>% dplyr::filter(id=="MAMO108111971") %>% dplyr::distinct(HASH_KEY) %>%  dplyr::filter(row_number()==1)` and `r  CONS_C1_df %>% dplyr::filter(id=="MAMO108111971") %>% dplyr::distinct(HASH_KEY) %>%  dplyr::filter(row_number()==2)`.

There were `r CONS_C1_df %>% mutate(concat=paste0(id,"_",HASH_KEY)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% dplyr::filter(duplicated(id)) %>% dplyr::arrange(id) %>%  dplyr::select(HASH_KEY,id,hash_rut_completo) %>% nrow()` patients with duplicated HASH's in each ID. This represents a `r paste0(round((205/136146)*100,1),"%")` of the total cases.

&nbsp;

```{r echo=T, paged.print=TRUE}
#Take which has a combination of IDs and HASH Keys distinct to the rest
#With this I may be subestimating the number of cases with a different concatenation.
#Considering all the distinct combinations, i take what they have a duplicate ID
#Select the duplicate IDs, it orders and...
#Filter only cases that has distinct id.
CONS_C1_df %>% mutate(concat=paste0(id,"_",HASH_KEY)) %>% dplyr::distinct(concat, .keep_all = TRUE) %>% #once here, n° of cases has been replaced by distinct or                                                                                                            unique combinations of IDs and HASH keys.
  dplyr::filter(duplicated(id)) %>% dplyr::arrange(id) %>%  #filter cases in which there is more than one ID, despite there is differents combinations of HASH and                                                             IDs, and then arrange IDs. This is possible only if a different HASH-Key contains more than one ID or                                                              viceversa.
  dplyr::distinct(id) %>% #take distincts IDs (exclude duplicated repeated IDs)
  assign("ids_more_one_hash",., envir = .GlobalEnv) # Differently put, take the distints IDs per HASH-Key, of the cases in which there are different combinations                                                      # of IDs and hash, and in which subgroup exists duplicated IDs.
 
#IMPORTANT: IF THE ID IS DUPLICATED, MIGHT NOT BE REFLECTED IN THIS RESUME IN TERMS OF QUANTITY.

# Then, apply these cases to the whole population
CONS_C1_df %>%
dplyr::filter(id %in% as.character(as.vector(unlist(as.data.table(unlist(ids_more_one_hash)))))) %>% # Select IDs of cited cases
dplyr::arrange(id) %>% #ordeno por ids 
  #762 cases. 409 cases without duplicates.
      dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>% #762 casos
      dplyr::select(row, ano_bd, id_mod, HASH_KEY, hash_rut_completo ,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
 knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 7. Total cases that each ID have more than one HASH-KEY",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```
&nbsp;

## Age in datasets

<br>

Based on the reunion on Dec. 05 of 2019, one of the main challenges was to check wether age was linked to the last 4 numbers of each ID. As we can see in the Figure 1, we can see a very clear correlation with a few residuals. If year of birth is regressed on year, we find that the intercept is `r coef(lm(ano_nac ~Edad, data= CONS_C1_df))[1]` and the slope is `r coef(lm(ano_nac ~Edad, data= CONS_C1_df))[2]`.

<br>

##### Figure 1. Scatterplot of Year of Birtth and Age
```{r fig_fecha_nac_edad, fig.height=4, fig.width=8, warning=FALSE}
#plot(CONS_C1_df$ano_nac, CONS_C1_df$Edad, ylab="Age", xlab="Year of Birth")

#figure() %>%
 # ly_points(ano_nac, Edad, data = CONS_C1_df,
#    hover = c(row,ano_bd)) %>%
#  ly_abline(lm(ano_nac ~Edad, data= CONS_C1_df), type = 2, legend = "Regression") %>%
 #   x_axis(label = "Year of Birth")
 #   y_axis(label = "Age")
plot_ly(CONS_C1_df, x = ~ano_nac, y = ~Edad, 
        text =  ~paste("Row: ", row, '<br>Year DB:', ano_bd),
        mode = "markers") %>% layout(xaxis=list(title="Year of Birth"), 
                                     yaxis=list(title="Age"))
```


<br>

We identified the outliers, ending up with 3 cases in which the expected age and year of birth presented a difference greater than 1 year. In Table 8 we can see the first 6 cases that had differences ordered by the magnitude of the difference. The rest of the `r CONS_C1_df %>% dplyr::mutate(dif_edad=ano_nac-(2019-Edad)) %>% filter(dif_edad!=0) %>% nrow() %>% sum(-3)` had 12 months of difference.

<br>


```{r edad_fecha_nac, echo=T, paged.print=TRUE}
    CONS_C1_df %>%
    dplyr::mutate(dif_edad=ano_nac-(2019-Edad)) %>%
      filter(dif_edad!=0) %>%
      arrange(desc(dif_edad)) %>%
      dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>%
      dplyr::select(row, ano_bd, ano_nac, Edad, dif_edad,
                    HASH_KEY, hash_rut_completo, id_mod,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, 
                    ID.centro, everything()) %>%
      head() %>%
 knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 8. Cases that have a different year of birth and age",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```


<br>

However, we may take account that there are `r paste0(round(CONS_C1_df %>% dplyr::filter(Edad<18|Edad>90) %>% dplyr::summarise(n())/nrow(CONS_C1_df),3)*100,"%")` cases with inappropiate years, considering `r CONS_C1_df %>% dplyr::filter(Edad<18) %>% dplyr::summarise(n()) ` cases with less than 18 years, and `r CONS_C1_df %>% dplyr::filter(Edad>90) %>% dplyr::summarise(n()) ` cases with more than 90 years. Most of these IDs represent a date of admission, as can be seen in Table 9:

<br>

```{r wrong ages, echo=T, paged.print=TRUE}
  CONS_C1_df %>% filter(Edad<18|Edad>90) %>%
    dplyr::select(row, HASH_KEY, id_mod, ano_nac, ano_bd,fech_ing) %>%
 knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 9. Cases that have a wrongly asigned age",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```

<br>

This may condition the data linkage, given that if I assign a missing value to a patient that in other registry has the correct age, it won't be match within the block assigned. In order to account for this possible bias, we checked whether cases may be replaced with data from 

<br>

```{r wrong ages duplicates, echo=T, paged.print=TRUE}
#list of distinct HASHs that have a wrongly assigned age
CONS_C1_df %>% dplyr::filter(Edad<18|Edad>90) %>%
  dplyr::distinct(HASH_KEY) %>%
  assign("distinct_hash_wrong_age",., envir = .GlobalEnv)
#Then, apply these cases to the whole population
CONS_C1_df %>%
dplyr::filter(HASH_KEY %in% as.character(as.vector(unlist(as.data.table(unlist(distinct_hash_wrong_age)))))) %>% # select hashs of wrongly assigned ages
dplyr::arrange(HASH_KEY) %>% #order by hashs 
#  dplyr::filter(!duplicated(Edad)) %>% #filtro, 
    #54 patients, 1,231 cases.
      dplyr::select(-id,-TABLE,-14,-16,-17,-26,-27,-28,-29,-35,-36,-37,-88,-93,-94,-96,-101) %>% #762 casos
      dplyr::select(row, ano_bd, HASH_KEY, id_mod, ano_nac, ano_bd,fech_ing, fech_egres,tipo_de_plan, tipo_de_programa, ID.centro, everything()) %>%
 knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption="Table 10. Total cases with wrong ages but have more than one age",
                 align =rep('c', 101))  %>%
  kable_styling(bootstrap_options = c("striped", "hover"),font_size = 8) %>%
  scroll_box(width = "100%", height = "350px")
```


<br>

We found that the age is a time invariant variable. In order to identify similar matches, we need to identify the date of admission and the HASH Key, but considering the year. In Table 11 we can see that 45,526 cases had at least one case with the same combination of HASH-Key and date of admission.

<br>

```{r duplicated rows, echo=T, paged.print=TRUE}
duplicated_rows_concat <- data.frame(duplicated = duplicated(CONS_C1_df_dup[,c("HASH_KEY","fech_ing_ano","fech_ing_mes","fech_ing_dia")]), 
                                       row = 1:nrow(CONS_C1_df_dup[,c("HASH_KEY","fech_ing_ano","fech_ing_mes","fech_ing_dia")])) #%>%
  
# Duplicated rows
  data.frame(table(duplicated_rows_concat$duplicated,exclude=NULL),
             `%`=paste0(round(prop.table(table(duplicated_rows_concat$duplicated,exclude=NULL)),3)*100,"%")) %>%
  as.data.frame(.) %>%  
  knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
                   caption="Table 11. Duplicated rows of the combination of HASH-Key & Date of Admission", col.names= c(" ", " Frequencies", "Percentage"), 
                 align =rep('c', 2))  %>%
    kable_styling(bootstrap_options = c("striped", "hover"),font_size = 12)
```

<br>

In Figure 2 we can see every case and the distribution of duplicated ones.

<br>

```{r dup rows, fig.height=4, fig.width=8, warning=FALSE}
# Plot duplicated rows as black lines
  ggplot(duplicated_rows_concat, aes(xintercept = row)) +
    geom_vline(aes(xintercept = row, color=duplicated)) + # plot a black line for each duplicated row
    scale_color_manual(values = c('white','black'),name = "Duplicated", labels = c("No", "Yes")) +
    ggtitle("Figure 2. Indexes of duplicated rows") + # add a title
    labs(x=NULL, y=NULL) +
    coord_flip() + scale_x_reverse() + #flip x & y axis and reverse the x axis
    theme_bw()  
```
