---
title: "Chilean prosecutor's office Data merge"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide  
    toc: true # table of content true
    toc_depth: 5  # upto three depths of headings (specified by #, ## and ###)
    toc_float: true
    theme: flatly
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{=html}
<style type="text/css">
.tablelines table, .tablelines td, .tablelines th {
        border: 1px solid black;
        }
.centrado {
    text-align: center;
}
.table.center {
    margin-left:auto; 
    margin-right:auto;
  }
.table_wrapper{
    display: block;
    overflow-x: auto;
    white-space: nowrap;
}
code.r{
  font-size: 8px;
}
body{ /* Normal  */
      text-align: justify;
  }
.superbigimage{
    overflow-y:scroll;
    white-space: nowrap;
}
.superbigimage img{
    overflow-y: scroll;
    overflow-x: hidden;
}
</style>
```
```{=html}
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px; text-align: justify;}
</style>
```
```{r prev_setup, include = FALSE, cache=T}
rm(list=ls());gc()

path<-rstudioapi::getSourceEditorContext()$path

if (grepl("CISS Fondecyt",path)==T){
    setwd("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/");load("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2019 (github)/9.Rdata")
  } else if (grepl("andre",path)==T){
    setwd('C:/Users/andre/Desktop/SUD_CL/');load("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/9.Rdata")
  } else if (grepl("E:",path)==T){
    setwd("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/");load("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/9.Rdata")
  } else {
    setwd("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/");load("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/9.Rdata")
  }
rm(list=setdiff(ls(), c("CONS_C1_df_dup_SEP_2020_match","CONS_C1_df_dup_SEP_2020","CONS_C1")))
```

```{r setup, include = FALSE, cache=T, error=T}
#Libraries used in the routine. Dont change the order
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})
copiar_nombres <- function(x,row.names=FALSE,col.names=TRUE,dec=",",...) {
  if(class(ungroup(x))[1]=="tbl_df"){
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)    
        }
  } else {
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)       
  }
 }
}  
#packageVersion("codebook")
#https://github.com/RevolutionAnalytics/checkpoint
#if(!require(checkpoint)){install.packages("checkpoint")}
#if(!require(here)){install.packages("here")}
#checkpoint::checkpoint("2020-02-19",project=here::here(),checkpointLocation=paste0(here::here(),"/dedup"), use.lock=F, use.knitr=T, auto.install.knitr = T,scan.rnw.with.knitr=T, forceInstall=T,scanForPackages = TRUE)
#checkpointArchives(tempdir(), full.names = TRUE)

#if(!require(tidyr)){install.packages("tidyr")}
#if(!require(DataExplorer)){install.packages("DataExplorer")}
#if(!require(stringi)){install.packages("stringi")}
#if(!require(stringr)){install.packages("stringr")}
#if(!require(ggplot2)){install.packages("ggplot2")}
#if(!require(Hmisc)){install.packages("Hmisc")}
#if(!require(kableExtra)){install.packages("kableExtra")}
#if(!require(plotly)){install.packages("plotly")}
#if(!require(rbokeh)){install.packages("rbokeh")}
#if(!require(altair)){install.packages("altair")}
#if(!require(zoo)){install.packages("zoo")}
#if(!require(codebook)){install.packages("codebook")}
#if(!require(broom)){install.packages("broom")}
#if(!require(sqldf)){install.packages("sqldf")} 
#if(!require(devtools)){install.packages("devtools")}
#if(!require(Statamarkdown)){install_github("hemken/Statamarkdown")}
#if(!require(data.table)){install.packages("data.table")}
#if(!require(dplyr)){install.packages("dplyr")}

#if(!require(boot)){install.packages("boot")}
#if(!require(plyr)){install.packages("plyr")}
#if(!require(matrixStats)){install.packages("matrixStats")}
#if(!require(radiant)){install.packages("radiant", repos = "https://radiant-rstats.github.io/minicran/")}

try(library(boot))
library(matrixStats)
library(knitr)
library(tidyr)
library(stringi)
library(stringr)
library(ggplot2)
library(Hmisc)
library(kableExtra)
library(plotly)
library(janitor)
library(rbokeh)
library(zoo)
library(broom)
library(sqldf)
library(devtools)
library(codebook)
library(data.table)
library(panelr)
library(RColorBrewer)
library(lsmeans)
library(finalfit)
suppressPackageStartupMessages(library(ggiraph))
suppressPackageStartupMessages(library(sf))
library(treemapify)
library(dplyr)
library(tidyverse)
library(epiR)
library(survminer)
library(ggfortify)
library(survMisc)

library(foreign)
library(Hmisc)
library(gridExtra)
library(reshape2)
library(stargazer)
library(tableone)
library(MatchIt)
library(cobalt)
library(eha)
library(igraph)
library(Amelia)
library(DiagrammeR) 
library(mstate)
library(flexsurv)
library(muhaz)
library(Metrics)
library(rpivotTable)
library(caret)
library(polycor)
library(ClusterR)
options(scipen=999) #display numbers rather scientific number

#library(mstateutils)
#remotes::install_github("chjackson/flexsurv-dev", upgrade = "never")
#devtools::install_github("stulacy/multistateutils", build_vignettes=TRUE, upgrade = "never")
#devtools::install_github("hputter/mstate", upgrade = "never")
#unlink("C:/Users/CISS Fondecyt/OneDrive/Documentos/R/win-library/4.0/mstate", recursive=T, force=T)

if(!require(radiant.update)){install.packages("radiant.update", repos = "https://radiant-rstats.github.io/minicran/")}
#install.packages( repos = "https://radiant-rstats.github.io/minicran/")
#install.packages("radiant.update", repos = "https://radiant-rstats.github.io/minicran/")

#tryCatch(source("https://raw.githubusercontent.com/radiant-rstats/minicran/gh-pages/update.R"), error = function(e) print("updated package, radiant"))

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

try_with_time_limit <- function(expr, cpu = Inf, elapsed = Inf)
{
  y <- try({setTimeLimit(cpu, elapsed); expr}, silent = TRUE) 
  if(inherits(y, "try-error")) NULL else y 
}
eval_fork <- function(..., timeout=60){

  #this limit must always be higher than the timeout on the fork!
  setTimeLimit(timeout+5);      

  #dispatch based on method
  ##NOTE!!!!! Due to a bug in mcparallel, we cannot use silent=TRUE for now.
  myfork <- parallel::mcparallel({
    eval(...)
  }, silent=FALSE);

  #wait max n seconds for a result.
  myresult <- parallel::mccollect(myfork, wait=FALSE, timeout=timeout);

  #try to avoid bug/race condition where mccollect returns null without waiting full timeout.
  #see https://github.com/jeroenooms/opencpu/issues/131
  #waits for max another 2 seconds if proc looks dead 
  while(is.null(myresult) && totaltime < timeout && totaltime < 2) {
     Sys.sleep(.1)
     enddtime <- Sys.time();
     totaltime <- as.numeric(enddtime - starttime, units="secs")
     myresult <- parallel::mccollect(myfork, wait = FALSE, timeout = timeout);
  }

  #kill fork after collect has returned
  tools::pskill(myfork$pid, tools::SIGKILL);    
  tools::pskill(-1 * myfork$pid, tools::SIGKILL);  

  #clean up:
  parallel::mccollect(myfork, wait=FALSE);

  #timeout?
  if(is.null(myresult)){
    stop("R call did not return within ", timeout, " seconds. Terminating process.", call.=FALSE);      
  }

  #move this to distinguish between timeout and NULL returns
  myresult <- myresult[[1]];

  #reset timer
  setTimeLimit();     

  #forks don't throw errors themselves
  if(inherits(myresult,"try-error")){
    #stop(myresult, call.=FALSE);
    stop(attr(myresult, "condition"));
  }

  #send the buffered response
  return(myresult);  
}
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#GET LOCAL
#dir.create(paste0(getwd(),"/renv_local"))
#Sys.setenv(RENV_PATHS_LOCAL = paste0(getwd(),"/renv_local"))
#install.packages(paste0(getwd(),"/renv_local/gurobi_9.1-0.zip"), repos = NULL, type="source")
#install.packages(paste0("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/renv_local/gurobi_9.1-0.zip"), repos = NULL, type="source")
#"G:/Mi unidad/Alvacast/SISTRAT 2019 (github)"
#Sys.getenv("R_LIBS_USER")

fitstats.flexsurvreg = function(x){
  ll = x$loglik
  aic = x$AIC
  k = length(x$coefficients)
  n = sum(x$data$m["(weights)"])
  aicc = aic + ((2 * k) * (k + 1) / (n - k - 1))
  bic = - 2 * ll + (k * log(n))
  data.frame(
   Df = k,
    "n2ll" = -2 * ll,
    AIC = aic,
    AICc = aicc,
    BIC = bic
  )
}


if(.Platform$OS.type == "windows") withAutoprint({
  memory.size()
  memory.size(TRUE)
  memory.limit()
})
memory.limit(size=56000)
```

<br>

# Obtain the database

<br>

<div style="border: 1px solid #ddd; padding: 5px; overflow-y: scroll; height:400px; overflow-x: scroll; width:100%">
```{r traer_base,dpi = 96, message=F, error=T,eval=T, warnings=F}
library(readxl)
base_fiscalia <- read_excel(gsub("/SUD_CL/Fiscalia_merge.Rmd","/BASE.xlsx",rstudioapi::getSourceEditorContext()$path), 
    sheet = "BASE", skip = 4, guess_max = min(1000000, 1000000)) %>% janitor::clean_names()
#PASAR A FORMATO FECHA ENTENDIBLE Y HACERLO EN NUMERO: fec_comision  termino_relacion fec_cbiorelacion
#ESTUDIAR ADVERTENCIAS
#Todas. Número con que se identifica una causa o juicio en el sistema informático. Es único para todo el país, generalmente lo crea el Ministerio Público y nace y muere con la causa.
#https://obtienearchivo.bcn.cl/obtienearchivo?id=documentos/10221.1/57046/1/GlosarioTerminos_PoderJudicial.pdf
#irrelevante para nosotros: gls_sitiosuceso, cod_sitiosuceso, lugar_ocurrencia
glimpse(base_fiscalia)

#CLASIFICACION_PENA 55

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#Sirve: encontrado_como_victima, encontrado_como_imputado, tipo_termino, agrupa_terminos, gls_materia, familia_delito, gls_tipo_sujeto_vic,  familia_delito, gls_region, gls_parentesco
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#encontrado_como_victima encontrado_como_imputado, ¿puede ser ambas?

#

#Investigar si sirve: gls_proctermino

#idsujeto_victima varía por hash? puede porque él no sea víctima

# Investigar consistencia de edad y sexo en función de gls_parentesco. Ver si varía por fecha para un mismo hash


#Ver si  gls_region agrupa bien a las comunas
#Ver si los agrupa/familia hacen bien la clasificación
#Hay inconsistencia en gls_materia vs. cod_delito
#Ver si hay información icompleta por quienes tienen medidas. Ver qué significa 155 pp e ip; también ver que es 43 a 58

#Hacer prueba de aleatoriedad

#Por lo visto nos metieron gente que no calza con la base de datos o que no está en nuestra base. Ver si corresponde a gente que descartamos.
```
</div>

```{r tab1_descr_c1_baseline_vs_type_treatd,dpi = 96, message=F, error=T,eval=T, warnings=F}
library(compareGroups)


base_fiscalia<-
  base_fiscalia %>% 
  dplyr::mutate(gls_region=dplyr::case_when(gls_region=="REGION METROPOLITANA CENTRO NORTE"~ "RM Centro Norte",
                                            gls_region=="REGION METROPOLITANA OCCIDENTE"~ "RM Occidente",
                                            gls_region=="REGION METROPOLITANA ORIENTE"~ "RM Oriente",
                                            gls_region=="REGION METROPOLITANA SUR"~ "RM Sur",
                                            T~NA_character_)) %>% 
  dplyr::mutate(region_delito=dplyr::case_when(region_delito=="REGION METROPOLITANA CENTRO NORTE"~ "RM Centro Norte",
                                            region_delito=="REGION METROPOLITANA OCCIDENTE"~ "RM Occidente",
                                            region_delito=="REGION METROPOLITANA ORIENTE"~ "RM Oriente",
                                            region_delito=="REGION METROPOLITANA SUR"~ "RM Sur",
                                            T~NA_character_)) %>%   
   

no_mostrar=1
if(no_mostrar==0){
CONS_C1_df_dup_SEP_2020_match<-
  CONS_C1_df_dup_SEP_2020 %>% 
  dplyr::filter(dup==1) %>% #, tipo_de_plan_2 %in% c("PG-PR","M-PR","PG-PAI","M-PAI","PG-PAB","M-PAB")
  dplyr::mutate(tipo_de_plan_res=dplyr::case_when(grepl("PR",as.character(tipo_de_plan_2))~1,
                                                  grepl("PAI",as.character(tipo_de_plan_2))~0,
                                                  grepl("PAB",as.character(tipo_de_plan_2))~0,
                                                  TRUE~NA_real_)) %>% 
  dplyr::mutate(tipo_de_plan_res=factor(tipo_de_plan_res)) %>% 
  dplyr::mutate(abandono_temprano_rec=factor(if_else(as.character(motivodeegreso_mod_imp)=="Early Drop-out",TRUE,FALSE,NA))) %>% 
  dplyr::mutate(dg_trs_cons_sus_or=factor(if_else(as.character(dg_trs_cons_sus_or)=="Drug dependence",TRUE,FALSE,NA))) %>% 
  dplyr::mutate(tipo_centro_pub=factor(if_else(as.character(tipo_centro)=="Public",TRUE,FALSE,NA))) %>% 
  dplyr::mutate(condicion_ocupacional_corr=factor(condicion_ocupacional_corr),cat_ocupacional_corr=factor(cat_ocupacional_corr)) %>% 
  dplyr::mutate(dg_trs_fis_rec=factor(dplyr::case_when(as.character(diagnostico_trs_fisico)=="En estudio"~"Diagnosis unknown (under study)",as.character(diagnostico_trs_fisico)=="Sin trastorno"~'Without physical comorbidity',cnt_diagnostico_trs_fisico>0 ~'With physical comorbidity',
                                             TRUE~NA_character_)))%>%
    dplyr::mutate(escolaridad_rec=parse_factor(as.character(escolaridad_rec),levels=c('3-Completed primary school or less', '2-Completed high school or less', '1-More than high school'), ordered=T,trim_ws=T,include_na =F, locale=locale(encoding = "Latin1"))) %>%   
dplyr::mutate(freq_cons_sus_prin=parse_factor(as.character(freq_cons_sus_prin),levels=c('Did not use', 'Less than 1 day a week','2 to 3 days a week','4 to 6 days a week','1 day a week or more','Daily'), ordered =T,trim_ws=T,include_na =F, locale=locale(encoding = "UTF-8"))) %>% 
  dplyr::mutate(evaluacindelprocesoteraputico=dplyr::case_when(grepl("1",as.character(evaluacindelprocesoteraputico))~'1-High Achievement',grepl("2",as.character(evaluacindelprocesoteraputico))~'2-Medium Achievement',grepl("3",as.character(evaluacindelprocesoteraputico))~'3-Minimum Achievement', TRUE~as.character(evaluacindelprocesoteraputico))) %>% 
  dplyr::mutate(evaluacindelprocesoteraputico=parse_factor(as.character(evaluacindelprocesoteraputico),levels=c('1-High Achievement', '2-Medium Achievement','3-Minimum Achievement'), ordered =T,trim_ws=T,include_na =F, locale=locale(encoding = "UTF-8"))) %>% 
  dplyr::select_(.dots = match.on_tot) %>% 
  dplyr::mutate(more_one_treat=factor(ifelse(duplicates_filtered>1,1,0))) %>% 
  data.table::data.table()
}

invisible("Comentarios")

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
kableone <- function(x, caption=NULL, col.names=NA, smd=T, test=T, varLabels=T, noSpaces=T, printToggle=T, dropEqual=F, ...) {
  capture.output(x <- print(x, smd=T, test=test, varLabels=varLabels,noSpaces=noSpaces, printToggle=printToggle, dropEqual=dropEqual, ...))
  
  knitr::kable(x,format= "html", format.args= list(decimal.mark= ".", big.mark= ","),
               caption= caption, col.names= col.names)
}
as.data.frame.TableOne <- function(x, ...) {
    
    capture.output(print(x, showAllLevels = TRUE, smd=T, test=T, varLabels=T, ...) -> x)
    
    y <- as.data.frame(x)
    y$characteristic <- na_if(rownames(x), "")
    y <- y %>%
        #fill(characteristic, .direction = "down") %>%
        select(characteristic, everything())
    
    rownames(y) <- NULL
    y 
}

options(knitr.kable.NA = '')

#attr(CONS_C1_df_dup_SEP_2020_match$sus_ini_mod_mvv,"label")<-"Starting Substance"

## Vector of variables to summarize
myVars <-dput(names(dplyr::select(base_fiscalia, -c("rut_enc_saf","ruc","idrelacion","cod_delito","cod_lugarocurrencia","cod_parentescoimputado","cod_mottermino","cod_motsuspension","cod_proctermino","idsujeto_imputado","idsujeto_victima","impcod_tiposujeto","cod_lugarocurrencia","cod_sitiosuceso","cod_comunadelito","cod_region"))))

## Vector of categorical variables that need transformation
catVars <- c("encontrado_como_victima", "encontrado_como_imputado", "gls_tipo_sujeto_vic", "gls_region",
             "tipo_termino", "agrupa_terminos", "gls_materia","familia_delito","relacion_vifsaf","gls_parentesco","gls_mottermino","gls_motsuspension","gls_proctermino","gls_tipo_imputado","lugar_ocurrencia","gls_sitiosuceso","gls_comuna","region_delito","medidas_155","medidas_pp","medidas_ip","marca_suspension_43","marca_pena_44","marca_multa_45","medida_alternativa_46","clasificacion_pena_47","tramos_condena_48","clasificacion_penarpa_1_49","clasificacion_penarpa_2_50","marca_suspension_51","marca_pena_52","marca_multa_53","medida_alternativa_54","clasificacion_pena_55","tramos_condena_56","clasificacion_penarpa_1_57","clasificacion_penarpa_2_58")
## Create a TableOne object
tab1 <- CreateTableOne(vars = myVars, data = base_fiscalia[,myVars], factorVars = catVars, 
                       smd=T, includeNA=T,test=T)

kableone(as.data.frame.TableOne(tab1), size=11, first.strip=T, hide.no="no",
           format="html",caption= "Table 1. Summary descriptives",
         smd=T, test=T, varLabels=T,noSpaces=T, printToggle=T, dropEqual=F) %>% #,col.names=c("Variables","Residential", "Ambulatory", "p-value")) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover","condensed"),font_size= 10) %>%
  row_spec(1, bold=T, italic=T,color="black",hline_after=T,extra_latex_after="\\arrayrulecolor{white}",font_size= 11) %>%
  kableExtra::add_footnote(c("Note. Continuous variables are presented as Medians and Percentiles 25 and 75 were shown;", "Categorical variables are presented as number (%)"), notation = "none")%>%
  kableExtra::scroll_box(width = "100%", height = "375px")
```

```{r tab2_descr_c1_baseline_vs_type_treatd,dpi = 96, message=F, error=T,eval=T, warnings=F}
tab2 <- CreateTableOne(vars = myVars, data = base_fiscalia[,myVars], factorVars = catVars, 
                       smd=T, strata="encontrado_como_imputado", includeNA=T,test=T)

kableone(as.data.frame.TableOne(tab2), size=11, first.strip=T, hide.no="no",
           format="html",caption= "Table 2. Summary descriptives, by accused",
         smd=T, test=T, varLabels=T,noSpaces=T, printToggle=T, dropEqual=F) %>% #,col.names=c("Variables","Residential", "Ambulatory", "p-value")) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover","condensed"),font_size= 10) %>%
  row_spec(1, bold=T, italic=T,color="black",hline_after=T,extra_latex_after="\\arrayrulecolor{white}",font_size= 11) %>%
  kableExtra::add_footnote(c("Note. Continuous variables are presented as Medians and Percentiles 25 and 75 were shown;", "Categorical variables are presented as number (%)"), notation = "none")%>%
  kableExtra::scroll_box(width = "100%", height = "375px")

```

<br>

```{r hetcor, echo=T, cache= T, paged.print=TRUE, eval=F, error=F, dpi=320, fig.align="center", fig.cap="Figure 2. Latent classes"}

mydata <- 
  base_fiscalia %>% 
  dplyr::mutate(accused=dplyr::case_when(encontrado_como_victima=="SI" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 encontrado_como_victima=="NO" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 T~"VICTIMA")) %>%
  dplyr::select(-c("rut_enc_saf","gls_region","gls_tipo_sujeto_vic","ruc","idrelacion","cod_delito","cod_lugarocurrencia","cod_parentescoimputado","cod_mottermino","cod_motsuspension","cod_proctermino","idsujeto_imputado","idsujeto_victima","impcod_tiposujeto","cod_lugarocurrencia","cod_sitiosuceso","cod_comunadelito","iddelito","cod_region")) %>% 
  dplyr::select(-c("encontrado_como_victima","encontrado_como_imputado","fec_comision", "termino_relacion", "fec_cbiorelacion", "gls_comuna", "lugar_ocurrencia")) %>% 
  dplyr::filter(accused=="IMPUTADO") %>% 
   # glimpse()
  dplyr::mutate(across(, ~ifelse(is.na(.),9999,as.numeric(factor(.)))))


f_df<-with(mydata, cbind(tipo_sujeto_vic, reg, tipo_termino, agrupa_terminos, 
gls_materia, familia_delito, relacion_vifsaf, gls_parentesco, 
gls_mottermino, gls_motsuspension, gls_proctermino, gls_tipo_imputado, 
gls_sitiosuceso, region_delito, medidas_155, medidas_pp, 
medidas_ip, marca_suspension_43, marca_pena_44, marca_multa_45, 
medida_alternativa_46, clasificacion_pena_47, tramos_condena_48, 
clasificacion_penarpa_1_49, clasificacion_penarpa_2_50, marca_suspension_51, 
marca_pena_52, marca_multa_53, medida_alternativa_54, clasificacion_pena_55, 
tramos_condena_56, clasificacion_penarpa_1_57, clasificacion_penarpa_2_58, 
accused)~1)
```

<br>


# Missingness

```{r miss, echo=T, cache= T, paged.print=TRUE, eval=T, error=T, dpi=320, fig.align="center"}
cols<-base_fiscalia %>%
    #dplyr::filter(resp_status=="partial") %>%  
    dplyr::select(p3_siente_1:p47_demo_medio_transp_09) %>% names() #si fuera desde SPSS, sería p47_demo_medio_transp_otr

tot<-
base_fiscalia %>%
  # dplyr::filter(resp_status=="partial") %>% 
  nrow()
#Ordenar variables
missing.values <- 
  base_fiscalia %>%
  #dplyr::filter(resp_status=="partial") %>%  
  #dplyr::select(p3_siente_1:p47_demo_medio_transp_09) %>% #si fuera desde SPSS, sería p47_demo_medio_transp_otr
    tidyr::gather(key = "key", value = "val") %>%
    dplyr::mutate(is.missing = is.na(val)) %>%
    #dplyr::left_join(cols_labels,by=c("key"="V1")) %>% 
    dplyr::group_by(key, is.missing) %>%
    dplyr::summarise(num.missing = n()) %>%
    dplyr::filter(is.missing==T) %>%
    dplyr::mutate(perc_miss=num.missing/tot) %>% 
    dplyr::select(-is.missing) %>% 
    dplyr::ungroup() %>% 
    dplyr::group_by(key) %>% 
    dplyr::slice(1) %>% 
    dplyr::ungroup()
    #dplyr::mutate(label=paste(stringi::stri_wrap(label, width=20),"<br>"))
    #arrange(desc(num.missing)) 

plot_miss<-
missing.values %>%
  dplyr::ungroup() %>% 
 # slice(1:29) %>% 
  ggplot() +
    geom_bar(aes(x=factor(key), y=perc_miss), stat = 'identity') +
    labs(x='variable', y="Porcentaje de perdidos", caption=paste0("Nota. Porcentaje de perdidos del total (",format(tot, big.mark=","),")")) +
  #theme(axis.text.x = element_text(angle = 45, hjust = 1, size=6))+
  theme(axis.text.x = element_blank())+
  scale_y_continuous(limits=c(0,1))+
  sjPlot::theme_sjplot()+
  coord_flip()


  ggplotly(plot_miss)%>% layout(xaxis= list(showticklabels = FALSE), height = 600, width=800)

``` 
  
<br>


# Near Zero Variance


Check variables that only one unique value (i.e. are zero variance) or predictors that have both of the following characteristics: few unique values given the sample size, and the frequency of the most common value is much more big than the second most common value.

```{r nearZeroVar, echo=T, cache= T, paged.print=TRUE, eval=T, error=T, dpi=320, fig.align="center"}
nzv_vals <- nearZeroVar(base_fiscalia, saveMetrics = TRUE)
nzv_sorted <- arrange(nzv_vals, desc(freqRatio))
head(nzv_sorted)


kable(as.data.frame.TableOne(nzv_sorted), size=11, format="html",
           caption= "Table 2. Near Zero Variance",
      col.names=c("Variable", "freqRatio", "% of Unique values", "Zero Variance", "Near Zero Variance")) %>% #,col.names=c("Variables","Residential", "Ambulatory", "p-value")) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover","condensed"),font_size= 10) %>%
  kableExtra::add_footnote(c("Note. freqRatio= ratio of frequencies for the most common value over the second most common value for that variable"), notation = "none")%>%
  kableExtra::scroll_box(width = "100%", height = "375px")
```
<br>

## Times as accused

- `r table(base_fiscalia$encontrado_como_victima,base_fiscalia$encontrado_como_imputado)[4]` people that is found as accused and as a victim at the same time. Meanwhile, we considered them as accused.


```{r fig1, echo=T, cache= T, paged.print=TRUE, warning=F, eval=T, fig.align="center", fig.cap="Figure 1. Distribution of records in which a user is declared as an accused", fig.height=6}
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
base_fiscalia_acc_imp<-
base_fiscalia %>% 
  dplyr::mutate(accused=dplyr::case_when(encontrado_como_victima=="SI" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 encontrado_como_victima=="NO" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 T~"VICTIMA")) %>% 
  dplyr::filter(accused=="IMPUTADO") %>% 
  dplyr::group_by(rut_enc_saf) %>% 
  dplyr::count() %>% 
  ungroup()
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

p<-
base_fiscalia_acc_imp %>% 
  dplyr::left_join(CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T),by=c("rut_enc_saf"="hash_key")) %>% ggplot(aes(x=n), alpha=.7)+
  geom_histogram_interactive(bins=120)+
  geom_vline(aes(xintercept=median(base_fiscalia_acc_imp$n)), color="darkred", linetype="dashed")+
  geom_vline(aes(xintercept=quantile(base_fiscalia_acc_imp$n, .99)), color="darkmagenta", linetype="solid")+
  geom_vline(aes(xintercept=quantile(base_fiscalia_acc_imp$n, .95)), color="darkblue", linetype="dotted")+
  sjPlot::theme_sjplot2() +
  #facet_wrap(~motivodeegreso_mod_imp)+
labs(y = "Frequency",x="Diff. Between Treatments", caption= paste0("Blue dotted line=", quantile(base_fiscalia_acc_imp$n, .95)," records; Violet solid line=",quantile(base_fiscalia_acc_imp$n, .99)," records; Red dashed line= Median=",median(base_fiscalia_acc_imp$n)," records; Maximum=",max(base_fiscalia_acc_imp$n)," records"))
# xlim(c(-1,2000))

p
```


## Times as victim


```{r fig2, echo=T, cache= T, paged.print=TRUE, warning=F, eval=T, fig.align="center", fig.cap="Figure 2. Distribution of records in which a user is declared as a Victim", fig.height=6}
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
base_fiscalia_acc_vic<-
base_fiscalia %>% 
  dplyr::mutate(accused=dplyr::case_when(encontrado_como_victima=="SI" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 encontrado_como_victima=="NO" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 T~"VICTIMA")) %>% 
  dplyr::filter(accused=="VICTIMA") %>% 
  dplyr::group_by(rut_enc_saf) %>% 
  dplyr::count() %>% 
  ungroup()
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_


p2<-
base_fiscalia_acc_vic %>% 
  dplyr::left_join(CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T),by=c("rut_enc_saf"="hash_key")) %>% ggplot(aes(x=n), alpha=.7)+
  geom_histogram_interactive(bins=120)+
  geom_vline(aes(xintercept=median(base_fiscalia_acc_vic$n)), color="darkred", linetype="dashed")+
  geom_vline(aes(xintercept=quantile(base_fiscalia_acc_vic$n, .99)), color="darkmagenta", linetype="solid")+
  geom_vline(aes(xintercept=quantile(base_fiscalia_acc_vic$n, .95)), color="darkblue", linetype="dotted")+
  sjPlot::theme_sjplot2() +
  #facet_wrap(~motivodeegreso_mod_imp)+
labs(y = "Frequency",x="Diff. Between Treatments", caption= paste0("Blue dotted line=", quantile(base_fiscalia_acc_vic$n, .95)," records; Violet solid line=",quantile(base_fiscalia_acc_vic$n, .99)," records; Red dashed line= Median=",median(base_fiscalia_acc_vic$n)," records; Maximum=",max(base_fiscalia_acc_vic$n)," records"))
# xlim(c(-1,2000))

p2
```

```{r fig3, echo=T, cache= T, paged.print=TRUE, warning=F, eval=T, fig.align="center", fig.cap="Figure 3. Distribution of records in which a user is declared as an accused"}

base_fiscalia_acc_vic %>% 
    dplyr::left_join(CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T),by=c("rut_enc_saf"="hash_key")) %>% distinct(rut_enc_saf)

paste0("Percentage of HASHs that have records as victims: ",
scales::percent(
base_fiscalia_acc_vic %>% 
    dplyr::left_join(CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T),by=c("rut_enc_saf"="hash_key")) %>%  distinct(rut_enc_saf) %>% nrow()/CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T) %>% nrow(),
accuracy=.01
  )
)

```

```{r fig4, echo=T, cache= T, paged.print=TRUE, warning=F, eval=T, fig.align="center", fig.cap="Figure 4. Distribution of records in which a user is declared as a victim"}

paste0("Percentage of HASHs that have records as accused: ",
scales::percent(
base_fiscalia_acc_vic %>% 
    dplyr::left_join(CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T),by=c("rut_enc_saf"="hash_key")) %>%  distinct(rut_enc_saf) %>% nrow()/CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% distinct(hash_key, .keep_all = T) %>% nrow(),
accuracy=.01
  )
)
```

<br>


<div style="border: 1px solid #ddd; padding: 5px; overflow-y: scroll; height:650px; overflow-x: scroll; width:100%">
```{r exporttable, warning=FALSE}
#https://cran.r-project.org/web/packages/rpivotTable/vignettes/rpivotTableIntroduction.html
#
CONS_C1_df_dup_SEP_2020_dup<-
CONS_C1_df_dup_SEP_2020[,c("hash_key","dup")] %>% dplyr::group_by(hash_key) %>% slice_max(dup) %>% ungroup()

pt<-
rpivotTable(data = base_fiscalia %>% 
              dplyr::left_join(CONS_C1_df_dup_SEP_2020_dup, by=c("rut_enc_saf"="hash_key")) %>% 
  dplyr::mutate(accused=dplyr::case_when(encontrado_como_victima=="SI" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 encontrado_como_victima=="NO" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 T~"VICTIMA")), 
  rows="gls_parentesco",
  cols = c("accused"),
  vals = "Cuenta", 
  aggregatorName = "Cuenta",
  subtotals=T,
  locale="es",
  rendererName = "Table",
  width="100%", height="550px")

#htmlwidgets::saveWidget(pt, "test3.html")
```
</div>

<!---
File is available in this [link](https://github.com/FONDECYTACC/SUD_health_Chile.github.io/raw/master/test3.html).
--->


# Structure

```{r s1, echo=T, error=T, paged.print=TRUE, error=T}
hetcor_mat<-polycor::hetcor(base_fiscalia , ML = T, std.err = T, use="pairwise.complete.obs", bins=4, pd=TRUE)

```



```{r s2, echo=T, error=T, paged.print=TRUE, error=T}
library(factoextra)
#let's decide the maximum K to cluster. Say 10: 
k.max <- 10

#we will create a vector of the total within sum of squars, in order to visulize it 
wss <- sapply(1:k.max, function(k){kmeans(base_fiscalia, k, 
                                          nstart=50,iter.max = 1000 )$tot.withinss})

#We can use the built in function fviz_nbclust to display "Elbow": 
fviz_nbclust(base_fiscalia, FUN = kmeans,method = "wss" ,nstart = 50)
#Error: cannot allocate vector of size 1203.1 Gb

base_fiscalia %>%  dplyr::select(encontrado_como_victima:clasificacion_pena_47) %>% replace(., is.na(.), "")

opt.k.sil <- Optimal_Clusters_KMeans(base_fiscalia, max_clusters=10, plot_clusters = TRUE, criterion = "silhouette")
```

```{r s3, echo=T, error=T, paged.print=TRUE}
#base_fiscalia %>%  dplyr::select(encontrado_como_victima:clasificacion_pena_47) %>% glimpse()
#idsujeto_imputado
#iddelito 
#idrelacion
#ruc
#idsujeto_victima
#gls_tipo_sujeto_vic


cat("ID sujeto víctima")
base_fiscalia %>%
    group_by(idsujeto_victima) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n), median=median(n), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
#podría agrupar al resto. De hecho, hay un ID que agrupa a 18,045 filas

cat("ID sujeto imputado")
base_fiscalia %>%
    group_by(idsujeto_imputado) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n), median=median(n), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
#agrupa al resto, me da la impresión, tiene hasta 129 filas con el mismo id sujeto imputado

cat("RUC")
base_fiscalia %>%
    group_by(ruc) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n), median=median(n), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
#El ruc no es específico, tiene hasta 129 filas. Ver si tienen relación con los ID's sjeto imputado o víctima

cat("ID sujeto imputado, RUC")
# base_fiscalia %>%
#     group_by(ruc,idsujeto_imputado) %>% 
#     summarise(n=n()) %>% 
#     summarise(min=min(n), max=max(n), mean=mean(n), median=median(n), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
# No correr, entrega 494,929 casos

cat("ID sujeto víctima, RUC")
# base_fiscalia %>%
#     group_by(idsujeto_victima,ruc) %>% 
#     summarise(n=n()) %>% 
#     summarise(min=min(n), max=max(n), mean=mean(n), median=median(n), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
#no correr. son 514,344 casos
#si pongo al revés, con el RUC primero, 
      # Error: Problem with `summarise()` column `p75`.
      # i `p75 = quantile(n, 0.75)`.
      # x argument is not interpretable as logical
      # i The error occurred in group 40782: ruc = "1000495180-3".
      # Backtrace:
      #   1. `%>%`(...)
      #   9. base::.handleSimpleError(...)
      #  10. dplyr:::h(simpleError(msg, call))
      # In addition: Warning message:
      # In if (na.rm) x <- x[!is.na(x)] else if (anyNA(x)) stop("missing values and NaN's not allowed if 'na.rm' is FALSE") :
      #   the condition has length > 1 and only the first element will be used

cat("ID delito")
base_fiscalia %>%
    group_by(iddelito) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n), median=median(n), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
# algo específica, tiene como máximo 82 filas con el mismo id delito


cat("ID relación")
base_fiscalia %>%
    group_by(idrelacion) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n, na.rm=T), median=median(n, na.rm=T), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))
# más específica, tiene como máximo 2 filas con el mismo id relación


cat("RUC, RUT, ID relación")
agrupacion_base<-
base_fiscalia %>%
    group_by(ruc,rut_enc_saf,idrelacion) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n, na.rm=T), median=median(n, na.rm=T), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))

cat("Por qué ocurre esto???")
agrupacion_base %>% 
    dplyr::filter(max>1)
invisible("Casos en que agrupados las relaciones por rucs y a su vez por cada rut, resultan tener 2 relaciones")
invisible("ruc=='1101216380-2' tiene todo igual con la otra fila")
invisible("ruc=='1200110540-8' tiene todo igual con la otra fila")
invisible("ruc=='1200685456-5' tiene todo igual con la otra fila")
invisible("ruc=='1200685456-5' tiene todo igual con la otra fila")
# ruc          rut_enc_saf                        min   max  mean median  p025   p25   p75  p975
# 1 1101216380-2 6a72664c6071e9728753279c9e9719e5     2     2   2      2    2     2     2     2   
# 2 1200110540-8 471b17aece44998caa6f83fee6b3b483     2     2   2      2    2     2     2     2   
# 3 1200685456-5 f1966360761b422b7e826bab2e1a38dc     2     2   2      2    2     2     2     2   
# 4 1200771867-3 a2aee30c6c0693a9c13f39e3520f666c     2     2   2      2    2     2     2     2   
# 5 1201254538-8 2d3bec94a94304a0b786ab83f7d1021a     2     2   2      2    2     2     2     2   
# 6 1300390161-5 f336b9f3e4097cfe736239a8bb937596     1     2   1.5    1.5  1.02  1.25  1.75  1.98
# 7 1600027649-2 bfc39f93fe4e0958c4e0ec16dddec275     2     2   2      2    2     2     2     2   

cat("RUT")
base_fiscalia %>%
    group_by(rut_enc_saf) %>% 
    summarise(n=n()) %>% 
    summarise(min=min(n), max=max(n), mean=mean(n, na.rm=T), median=median(n, na.rm=T), p025=quantile(n, .025), p25=quantile(n, .25), p75=quantile(n,.75), p975=quantile(n, .975))

```


```{r s4, echo=T, error=T, paged.print=TRUE}
cat("Vista base de datos")
base_fiscalia_ord<-
base_fiscalia %>%
    arrange(rut_enc_saf,fec_comision,ruc,idrelacion)
```


<br>

# Codebook

```{r codebook, echo=T, error=T, paged.print=TRUE}
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually better for debugging
  echo = TRUE  # show R code
)
ggplot2::theme_set(ggplot2::theme_bw())
pander::panderOptions("table.split.table", Inf)

if(!require(codebook)){install.packages("codebook")}
if(!require(future)){install.packages("future")}
if(!require(dplyr)){install.packages("dplyr")}
```


```{r prepare_codebook, include=T}

codebook_data <- dplyr::select(base_fiscalia, -c("rut_enc_saf","ruc","idrelacion","cod_delito","cod_lugarocurrencia","cod_parentescoimputado","cod_mottermino","cod_motsuspension","cod_proctermino","idsujeto_imputado","impcod_tiposujeto","cod_lugarocurrencia","cod_sitiosuceso","cod_comunadelito","cod_region"))

muestra=0
if(muestra==1){
# omit the following lines, if your missing values are already properly labelled
codebook_data <- detect_missing(codebook_data,
    only_labelled = TRUE, # only labelled values are autodetected as
                                   # missing
    negative_values_are_missing = FALSE, # negative values are missing values
    ninety_nine_problems = FALSE,   # 99/999 are missing values, if they
                                   # are more than 5 MAD from the median
    )
}
# If you are not using formr, the codebook package needs to guess which items
# form a scale. The following line finds item aggregates with names like this:
# scale = scale_1 + scale_2R + scale_3R
# identifying these aggregates allows the codebook function to
# automatically compute reliabilities.
# However, it will not reverse items automatically.
#codebook_data <- detect_scales(codebook_data)
```

<br>

In the following Tables and graphics, there is a summary of the variables and documentation of their characteristics. This high-level summary may permit us find errors on coding, help us to understand missingness and guide us towards an objective, or lead us to more questions. If a variable contains the symbol `(*)`, it means that this variable has a concatenation of values among continuous entries in treatments.

<br>

```{r codebook_display}
  metadata(codebook_data)$name <- "Prosecutor Support System (SAF), database of the Public Prosecutor's Office."
  metadata(codebook_data)$description <- "The information was extracted and processed from the Prosecutor Support System (SAF) database in accordance with the criteria established in the methodological document 'Criteria for Extracting Information from the SAF - 11_04_2018', prepared and updated in 2018 by the Studies, Evaluation, Control and Management Development Division. Data obtained at 2021-08-13; Period= 2010 to 2019; Unit of measurement= Relationships; Offenses considered= All; Date to consider= Date of termination of the case; National Coverage; Detail or summary= Detail; In the search for victims, only direct victims were considered; The RUTs indicated are searched only in cases terminated or suspended in the period 2010 - 2019;
The following types of accused are considered: COMPLAINED, ACCUSED, QUERELLED, WITNESS, SUSPECTED AND INVESTIGATED"

codebook(codebook_data)
```

<br>

# Session Info

```{r session_info, echo=T, error=T, paged.print=TRUE}
Sys.getenv("R_LIBS_USER")

rstudioapi::getSourceEditorContext()
#save.image("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/mult_state_carla.RData")

if (grepl("CISS Fondecyt",rstudioapi::getSourceEditorContext()$path)==T){
    save.image("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2019 (github)/10.RData")
  } else if (grepl("andre",rstudioapi::getSourceEditorContext()$path)==T){
    save.image("C:/Users/andre/Desktop/SUD_CL/10.RData")
  } else if (grepl("E:",rstudioapi::getSourceEditorContext()$path)==T){
    save.image("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/10.RData")
  } else {
    save.image("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/10.RData")
  }

sessionInfo()
```


# Exportar

```{r export, warning=FALSE}
if(no_mostrar==0){
  codebook::var_label(surveymonkey_accionsalududp_df2_cor_sel_2) <-
  var_labels_df%>% 
    codebook::dict_to_list()
    
  attr(surveymonkey_accionsalududp_df2_cor_sel_2$rn,"label")<-'Número de Fila'  
    
  for (i in 1:length(surveymonkey_accionsalududp_df2_cor_table)){
      x<-names(surveymonkey_accionsalududp_df2_cor_table)[i]
      attr(surveymonkey_accionsalududp_df2_cor_sel_2[[x]],"label")<- attr(surveymonkey_accionsalududp_df2_cor_table[[x]],"label")
  
  var_labels_df<-data.frame()
  for (i in 1:length(surveymonkey_accionsalududp_df2_cor_sel_2)){
    x<-names(surveymonkey_accionsalududp_df2_cor_sel_2)[i]
  var_labels_df<-rbind.data.frame(var_labels_df, cbind(x, attr(surveymonkey_accionsalududp_df2_cor_sel_2[[x]],"label")))
    }
  }
}

  #dplyr::arrange(hash_key, fech_ing)%>% 
path<-rstudioapi::getSourceEditorContext()$path

  base_fiscalia %>% 
  dplyr::mutate(accused=dplyr::case_when(encontrado_como_victima=="SI" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 encontrado_como_victima=="NO" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 T~"VICTIMA")) %>% 
  dplyr::filter(accused=="VICTIMA") %>% 
    rio::export(file = paste0(gsub("SUD_CL/Fiscalia_merge.Rmd","",path),"fiscalia_mariel_ago_2021.dta"))
```
