---
title: "Chilean prosecutor's office Data merge, step 2"
date: "`r withr::with_locale(new = c('LC_TIME' = 'C'), code =format(Sys.time(),'%B %d, %Y'))`"
output:
  html_document:
    code_folding: hide  
    toc: true # table of content true
    toc_depth: 5  # upto three depths of headings (specified by #, ## and ###)
    toc_float: true
    theme: flatly
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{=html}
<style type="text/css">
.tablelines table, .tablelines td, .tablelines th {
        border: 1px solid black;
        }
.centrado {
    text-align: center;
}
.table.center {
    margin-left:auto; 
    margin-right:auto;
  }
.table_wrapper{
    display: block;
    overflow-x: auto;
    white-space: nowrap;
}
code.r{
  font-size: 8px;
}
body{ /* Normal  */
      text-align: justify;
  }
.superbigimage{
    overflow-y:scroll;
    white-space: nowrap;
}
.superbigimage img{
    overflow-y: scroll;
    overflow-x: hidden;
}
</style>
```
```{=html}
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px; text-align: justify;}
</style>
```
```{r prev_setup, include = FALSE, cache=T}
rm(list=ls());gc()

path<-getwd()

if (grepl("CISS Fondecyt",path)==T){
    setwd("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/");load("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2019 (github)/10.Rdata")
  } else if (grepl("andre",path)==T){
    setwd('C:/Users/andre/Desktop/SUD_CL/');load("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/10.Rdata")
  } else if (grepl("E:",path)==T){
    setwd("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/");load("E:/Mi unidad/Alvacast/SISTRAT 2019 (github)/10.Rdata")
  } else {
    setwd(paste0(path,"/"));load(paste0(path,"/10.Rdata"))
  }
```

```{r setup, include = FALSE, cache=T, error=T, echo=T}
#Libraries used in the routine. Dont change the order
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})
copiar_nombres <- function(x,row.names=FALSE,col.names=TRUE,dec=",",...) {
  if(class(ungroup(x))[1]=="tbl_df"){
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)    
        }
  } else {
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)       
  }
 }
}  

if(!require(pacman)){install.packages("pacman")}
pacman::p_load(withr, boot, matrixStats, knitr, tidyr, stringi,stringr, ggplot2, Hmisc, kableExtra, plotly, janitor, rbokeh, zoo, broom, sqldf, devtools, codebook, data.table, panelr, RColorBrewer, lsmeans, finalfit, ggiraph, sf, treemapify, dplyr, tidyverse, epiR, survminer, ggfortify, survMisc, foreign, reshape2, stargazer, tableone, MarchIt, cobalt, eha, igraph, Amelia, DiagrammeR, mstate, flexsurv, muhaz, Metrics, rpivotTable, caret, polycor, ClusterR, flextable, ggstatsplot, ggside, daff, explore, sjPlot,compareGroups,job)

options(scipen=999) #display numbers rather scientific number

#remotes::install_github("chjackson/flexsurv-dev", upgrade = "never")
#devtools::install_github("stulacy/multistateutils", build_vignettes=TRUE, upgrade = "never")
#devtools::install_github("hputter/mstate", upgrade = "never")

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#GET LOCAL
#dir.create(paste0(getwd(),"/renv_local"))
#Sys.setenv(RENV_PATHS_LOCAL = paste0(getwd(),"/renv_local"))
#install.packages(paste0(getwd(),"/renv_local/gurobi_9.1-0.zip"), repos = NULL, type="source")
#install.packages(paste0("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/renv_local/gurobi_9.1-0.zip"), repos = NULL, type="source")
#Sys.getenv("R_LIBS_USER")

fitstats.flexsurvreg = function(x){
  ll = x$loglik
  aic = x$AIC
  k = length(x$coefficients)
  n = sum(x$data$m["(weights)"])
  aicc = aic + ((2 * k) * (k + 1) / (n - k - 1))
  bic = - 2 * ll + (k * log(n))
  data.frame(
   Df = k,
    "n2ll" = -2 * ll,
    AIC = aic,
    AICc = aicc,
    BIC = bic
  )
}


if(.Platform$OS.type == "windows") withAutoprint({
  memory.size()
  memory.size(TRUE)
  memory.limit()
})
memory.limit(size=56000)
```

<div class = "blue">
Several issues were found in the first stage of the exploration of the matches.
 - Duplicated entries (relationships) 
 - Cases that are victims and imputed at the same time
 - Unspecified dates
 - Correct imputed birth dates & sex of the users
 - Define the a date of censorship
</div>


<br>

```{r prev_define_censorship, echo=T, fig.align='center', message=FALSE, error=T, eval=T}

paste0("relationships with judicial proceedings ending after November 13, 2019\n n=",
       format(as.numeric(table(Base_fiscalia_v2$termino_relacion_simple<"2019-11-13"))[1],big.mark=","),"; ",
       scales::percent(as.numeric(prop.table(table(Base_fiscalia_v2$termino_relacion_simple<"2019-11-13"))), accuracy=0.1)[1])

cat("Information of P.O. using only relationships that ended before November 13, 2019")
paste0('Original Prosecutors Office\n(n = ',format(nrow(subset(Base_fiscalia_v2, termino_relacion_simple<"2019-11-13")),big.mark=","), 
        ';\nCauses= ',subset(Base_fiscalia_v2, termino_relacion_simple<"2019-11-13")%>% dplyr::distinct(ruc)%>% nrow() %>% format(big.mark=','),
        ';\nRel.=',subset(Base_fiscalia_v2, termino_relacion_simple<"2019-11-13")%>%dplyr::distinct(idrelacion)%>%nrow()%>%format(big.mark=','),
        ';\nRUC_Vic_Imp=',subset(Base_fiscalia_v2, termino_relacion_simple<"2019-11-13")%>%dplyr::mutate(rel=paste0(ruc,"_",idsujeto_victima,"_",idsujeto_imputado,"_","iddelito"))%>%dplyr::distinct(rel)%>%nrow()%>%format(big.mark=','),
        ';\nusers= ',subset(Base_fiscalia_v2, termino_relacion_simple<"2019-11-13")%>% dplyr::distinct(rut_enc_saf)%>% nrow() %>% format(big.mark=','),')')

```


```{r fig1, image-ref-for-in-text, echo=T, fig.align='center', message=FALSE, fig.caption="Figure 1.Summary of Process of Data Cleaning and Standardization, Imputation & Matching", fig.height=10, error=T, eval=T, dpi=320}
tab1_lab<- paste0('Original C1 Dataset \n(n = ', formatC(nrow(CONS_C1), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1%>% dplyr::distinct(HASH_KEY)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab2_lab<- paste0('&#8226;Remove duplicated entries\\\\\\l&#8226;Overlapping treatments of users\\\\\\l&#8226;Intermediate events of treatment (continuous referrals)\\\\\\l')
tab3_lab<- paste0('      C1 Dataset          \n(n = ', formatC(nrow(CONS_C1_df_dup_SEP_2020), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1_df_dup_SEP_2020%>% dplyr::distinct(hash_key)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab4_lab<- paste0('Original Prosecutors Office\n(n = ',format(nrow(Base_fiscalia_v2),big.mark=","), 
        ';\nCauses= ',Base_fiscalia_v2%>% dplyr::distinct(ruc)%>% nrow() %>% format(big.mark=','),
        ';\nRel.=',Base_fiscalia_v2%>%dplyr::distinct(idrelacion)%>%nrow()%>%format(big.mark=','),
        ';\nRUC_Vic_Imp=',Base_fiscalia_v2%>%dplyr::mutate(rel=paste0(ruc,"_",idsujeto_victima,"_",idsujeto_imputado,"_","iddelito"))%>%dplyr::distinct(rel)%>%nrow()%>%format(big.mark=','),
        ';\nusers= ',Base_fiscalia_v2%>% dplyr::distinct(rut_enc_saf)%>% nrow() %>% format(big.mark=','),')')
tab5_lab<- paste0('&#8226;Remove duplicated entries\\\\\\l&#8226;Long-to-wide relationships/crimes, end of judicial proceedings, penalty\\\\\\l&#8226;Correct dates (birth, comission of crime, end of judicial proceedings)\\\\\\l&#8226;Define cases that acted as victims & imputed in a cause\\\\\\l')
tab6_lab<- paste0("O.P. Dataset \n(n = ????;\n","","users= ",Base_fiscalia_v2%>% dplyr::distinct(rut_enc_saf)%>% nrow()%>% formatC(big.mark = ","),")")

#https://stackoverflow.com/questions/46750364/diagrammer-and-graphviz
#https://mikeyharper.uk/flowcharts-in-r-using-diagrammer/
#http://blog.nguyenvq.com/blog/2012/05/29/better-decision-tree-graphics-for-rpart-via-party-and-partykit/
#http://blog.nguyenvq.com/blog/2014/01/17/skeleton-to-create-fast-automatic-tree-diagrams-using-r-and-graphviz/
#https://cran.r-project.org/web/packages/DiagrammeR/vignettes/graphviz-mermaid.html
#https://stackoverflow.com/questions/39133058/how-to-use-graphviz-graphs-in-diagrammer-for-r
#https://subscription.packtpub.com/book/big_data_and_business_intelligence/9781789802566/1/ch01lvl1sec21/creating-diagrams-via-the-diagrammer-package
#https://justlegal.be/2019/05/using-flowcharts-to-display-legal-procedures/
#      

library(DiagrammeR) #⋉
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Times, shape = rectangle,fontsize = 9]        
      tab1 [label = '@@1']
      blank [label = '', width = 0.0001, height = 0.0001]
      tab2 [label = '@@2',fontsize = 7]
      tab3 [label = '@@3']
      
      tab4 [label = '@@4',fontsize = 8]
      blank2 [label = '', width = 0.0001, height = 0.0001]
      tab5 [label = '@@5',fontsize = 7]
      tab6 [label= '@@6']
      
      blank3 [label = '', width = 0.0001, height = 0.0001]
      blank4 [label = '', width = 0.0001, height = 0.0001]      
      blank5 [label = '', width = 0.0001, height = 0.0001] 
      
      blank6 [label = '', width = 0.0001, height = 0.0001]
      tab7 [label = '@@7',fontsize = 7]
      tab8 [label= '@@8']
      
      # edge definitions with the node IDs
      rankdir='TB'; rank= same; tab1 -> blank [arrowhead = none,label='  Data wrangling and normalization process',fontsize = 8];
      rankdir='TB'; rank= same; tab1; tab3;   
      blank -> tab2;
                  subgraph {
              rank = same; tab2; blank;
                  }
      rankdir='TB'; rank= same; blank -> tab3;      
            
      tab4 -> blank2 [arrowhead = none,label='  Data wrangling and normalization process',fontsize = 8];
      blank2 -> tab5
      blank2 -> tab6
      blank4 -> blank6 [arrowhead= none, label='⋉']
      blank6 -> tab7
                  subgraph {
        rank = same; blank6; tab7;
                  }
      blank6 -> tab8
                  subgraph {
        rank = same; tab5; blank2;
                  }
                  subgraph {
      rank= same; tab3 -> blank3 -> blank4 -> blank5 -> tab6 [arrowhead= none]
                  }
      }
                  subgraph {
        rank = same; tab3; tab6;
                  }
                  subgraph {
        rank = same; tab1; tab4;
                  }         
                  subgraph {
        rank = same; tab2; tab5;
                  } 
                  subgraph {
        rank = same; tab1; tab3;
        rankdir=TB
        rank=same
                  }
                  subgraph {
        rank = same; tab4; tab6;
        rankdir=TB
        rank=same
                  }                     

      [1]:  tab1_lab
      [2]:  tab2_lab
      [3]:  tab3_lab
      [4]:  tab4_lab
      [5]:  tab5_lab
      [6]:  tab6_lab
      [7]:  ' - asdasd- asdasdad'
      [8]:  'Merged database'
      ")

#https://stackoverflow.com/questions/1554635/graphviz-how-to-have-a-subgraph-be-left-to-right-when-main-graph-is-top-to-bot
#https://stackoverflow.com/questions/65509087/diagrammer-flowchart-align-vertical-nodes
#https://stackoverflow.com/questions/39451158/how-to-specify-vertical-alignment-of-nodes-in-r-package-diagrammer
#https://stackoverflow.com/questions/64323943/graphviz-and-dot-files-horizontal-and-vertical-node-alignment-intervening-node
#https://stackoverflow.com/questions/5424555/changing-edge-direction-in-dot
#https://graphviz.org/docs/attrs/rankdir/
#
```

<br>

# Correct dates

```{r paso1_dates, fig.align='center', fig.caption="Figure 16.Summary of Process of Data Cleaning and Standardization, Imputation & Matching", echo=T, cache= T, paged.print=TRUE, eval=T, error=T, dpi=320, fig.align="center"}
paste0("Patients with more than one date of birth in P.O. DB: ",
Base_fiscalia_v2 %>% 
  dplyr::group_by(rut_enc_saf) %>% 
  dplyr::mutate(n_fec=n_distinct(fec_nacimiento_simple)) %>% 
  dplyr::filter(n_fec>1) %>% nrow())


fech_nac_fisc_vs_senda<-
Base_fiscalia_v2 %>% 
    dplyr::left_join(CONS_C1_df_dup_SEP_2020[,c("hash_key","fech_nac", "edad_al_ing", "edad_ini_cons")] %>% dplyr::distinct(hash_key, .keep_all = T),by=c("rut_enc_saf"="hash_key")) %>%
    dplyr::mutate(fech_nac=as.Date(fech_nac)) %>% 
    dplyr::select(rut_enc_saf,fec_nacimiento_simple,fec_comision_simple, termino_relacion_simple,fech_nac, edad_al_ing, edad_ini_cons) %>% 
    dplyr::filter(dplyr::case_when(fec_nacimiento_simple!=fech_nac~T,T~F)) %>% 
    dplyr::mutate(obs=dplyr::case_when(rut_enc_saf %in% unlist(C1_fech_nac_nas)~"previous problems (Duplicates1)",T~"")) %>% 
  dplyr::distinct(rut_enc_saf, .keep_all = T) %>% 
  #si es fecha inválida, se asume que está bien la de SENDA. Si no, se analiza la diferencia.
  dplyr::mutate(diff=ifelse(fec_nacimiento_simple=="1900-01-01",NA,abs(fec_nacimiento_simple-fech_nac)))
#90,037 casos, pero 11,511 RUTs únicos
fech_nac_fisc_vs_senda %>% 
  ggplot()+
  geom_histogram(aes(x=diff), bins=40)+
  theme_538()+
  xlim(0,20000)+
  ylim(0,2000)+
  labs(caption=paste0("Note. Users with discrepancies are the", scales::percent(nrow(fech_nac_fisc_vs_senda)/length(unique(Base_fiscalia_v2$rut_enc_saf)))," of the sample;\nDifferences due to missing values were not listed (n=",as.numeric(table(is.na(fech_nac_fisc_vs_senda$diff))[2]),");\nMedian= ",median(fech_nac_fisc_vs_senda$diff,na.rm=T)," [",quantile(fech_nac_fisc_vs_senda$diff,.25,na.rm=T),", ",quantile(fech_nac_fisc_vs_senda$diff,.75,na.rm=T),"] days"), ylab="Count", xlab("Abs. difference between date of birth in PO vs. SENDA"))
```

- Define a tolerance value

- Replace with PO in case age was imputed by the research team

- 


```{r paso2_dates, echo=T, cache= T, paged.print=TRUE, eval=T, error=T, dpi=320, fig.align="center"}
#C1_fech_nac_nas

invisible("Ver cómo impacta a las edades imputadas como el edad de inicio de consumo y esas cosas")
#1.4. Replaced invalid ages with same users within the dataset
#1.7.04. Invalid Age Of Onset of Primary Substance, Higher than age
#1.7.05. Invalid Age Of Onset of Drug Use
#3.01.0b.HASH w/ more than one distinct Age of Onset of Drug Use.Minor differences within users,replaced with mean
#3.02.0b.HASH w/ more than one distinct Age of Onset of Drug Use Prim Subs. Minor differences within users,replaced with mea
#3.02.3.HASH w/ more than one distinct Age of Onset of Drug Use Prim Subs.Other;
#3.03.3.XX.HASH w/ more than one distinct Age of Onset Drug Use Primary Substance.Neural network imputation of ties
#1.6.XX.2.Age at admission less 18 years & had another date of birth that could be replaced
#	;1.5. Replaced invalid ages with TOP information
#1.6.02.0b;1.7.04. Invalid Age Of Onset of Primary Substance, Higher than age;
#
#1.6.03.1a;1.7.03. Invalid Age Of Onset of Drug Use, Higher than age;
#1.6.03.1a;1.7.04. Invalid Age Of Onset of Primary Substance, Higher than age;2
#1.6.03.1a;1.7.05. Invalid Age Of Onset of Drug Use, < 5 yrs age;
#1.6.05.2b1;1.7.06. Invalid Age Of Onset of Primary Substance, < 5 yrs age
#1.6.XX.2.Age at admission less 18 years & had another date of birth that could be replaced
#1.7.03. Invalid Age Of Onset of Drug Use, Higher than age
#1.7.04. Invalid Age Of Onset of Primary Substance, Higher than age
#1.7.05. Invalid Age Of Onset of Drug Use, < 5 yrs age
#1.7.06. Invalid Age Of Onset of Primary Substance, < 5 yrs age
#C1_fech_nac_nas
```


```{r bpmn, echo=T, cache= T, paged.print=TRUE, eval=F, error=T, dpi=320, fig.align="center"}
paste0("n= ", format(length(unique(Base_fiscalia_v2$rut_enc_saf)),big.mark=","),"; ",scales::percent(length(unique(Base_fiscalia_v2$rut_enc_saf))/length(unique(CONS_C1_df_dup_SEP_2020$hash_key))),")")

paste0("n= ",format(nrow(fech_nac_fisc_vs_senda),big.mark=","),";\n",
       scales::percent(nrow(fech_nac_fisc_vs_senda)/length(unique(Base_fiscalia_v2$rut_enc_saf))),
       "; ",scales::percent(nrow(fech_nac_fisc_vs_senda)/length(unique(CONS_C1_df_dup_SEP_2020$hash_key))),")")

paste0("n= ",format(length(unique(Base_fiscalia_v2$rut_enc_saf))-nrow(fech_nac_fisc_vs_senda),big.mark=","),";\n",
       scales::percent((length(unique(Base_fiscalia_v2$rut_enc_saf))-nrow(fech_nac_fisc_vs_senda))/length(unique(Base_fiscalia_v2$rut_enc_saf))),"; ",
       scales::percent((length(unique(Base_fiscalia_v2$rut_enc_saf))-nrow(fech_nac_fisc_vs_senda))/length(unique(CONS_C1_df_dup_SEP_2020$hash_key))),")")


```

<br>

# Label

```{r change labels,echo=T, paged.print=TRUE, eval=F}

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

Base_fiscalia_v2%>%
dplyr::mutate_at(c('dg_trs_psiq_cie_10_or','x2_dg_trs_psiq_cie_10_or','x3_dg_trs_psiq_cie_10_or','x2_dg_trs_psiq_sub_cie_10_or','x3_dg_trs_psiq_sub_cie_10_or','compromiso_biopsicosocial','pais_nacimiento','nacionalidad','dg_trs_psiq_sub_dsm_iv_or','x2_dg_trs_psiq_sub_dsm_iv_or','x3_dg_trs_psiq_sub_dsm_iv_or','dg_trs_psiq_sub_cie_10_or','etnia_cor_2','motivodeegreso_mod_imp','fecha_ultimo_tratamiento','fecha_ultimo_tratamiento','tiene_menores_de_edad_a_cargo'),~as.factor(.)) %>%
  dplyr::group_by(hash_key)%>%
  dplyr::mutate(at_least_one_cont_entry=sum(!is.na(diff_bet_treat)))%>%
  ungroup()%>%
  dplyr::mutate(at_least_one_cont_entry= ifelse(at_least_one_cont_entry>0,1,0))%>%
  dplyr::mutate(menor_45_dias_diff= ifelse(diff_bet_treat<45,1,0))%>%
  dplyr::mutate(at_least_one_cont_entry= recode(as.character(at_least_one_cont_entry),"0"="User with no cont. entry","1"="User with cont. entry"))%>%
  dplyr::mutate(menor_45_dias_diff= recode(as.character(menor_45_dias_diff),"0"=">= 45 Days of Difference Between Entries","1"="<45 Days of Difference Between Entries"))%>%
  dplyr::mutate(menor_60_dias_diff= recode(as.character(menor_60_dias_diff),"0"=">= 60 Days of Difference Between Entries","1"="<60 Days of Difference Between Entries"))%>%
  dplyr::mutate(obs_cambios_ninguno= recode(as.character(obs_cambios_ninguno),"0"="At least 1 Change w/ the Next Entry","1"="No Changes w/ the Next Entry"))%>%
  dplyr::mutate(motivoegreso_derivacion= recode(as.character(motivoegreso_derivacion),"0"="Other causes of discharge","1"="Referral"))%>%
  dplyr::mutate_at(vars(at_least_one_cont_entry,menor_45_dias_diff,menor_60_dias_diff,obs_cambios_ninguno,motivoegreso_derivacion,obs_cambios),~as.factor(.))%>%
  assign("Base_fiscalia_v2",., envir = .GlobalEnv)
  
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_  
  
codebook::var_label(Base_fiscalia_v2) <- list(
row= 'Numerador de los eventos presentes en la Base de Datos/Events in the Dataset',
table= 'Origen de los Datos (de los archivos por año)/Source of Data (of files per year)',
hash_key= 'Codificación del RUN/Masked Identifier (RUN)',
ano_bd= 'Año de la Base de Datos/Year of the Dataset (Source)',
id= 'Codigo Identificación de SENDA/SENDA ID',
nombre_centro= 'Nombre del Centro de Tratamiento/Treatment Center',
tipo_centro= 'Tipo de Centro/Type of Center',
region_del_centro= '(original, Recodificado en nombre_region)/',
servicio_de_salud= 'Servicio de Salud/Health Service',
tipo_de_programa= '(original, Recodificado en tipo_de_programa_2)/',
tipo_de_plan= '(original, Recodificado en tipo_de_plan_2)/',
senda= 'SENDA/SENDA',
dias_trat= 'Días de Tratamiento/Days of Treatment',
nmesesentratamiento= 'Número de Meses en Tratamiento/Number of Months in Treatment',
dias_en_senda= 'Días en SENDA/Days in SENDA',
n_meses_en_senda= 'Número de Meses en SENDA/Number of Months in SENDA',
sexo= '(original, Recodificado en sexo_2)/',
edad= 'Edad (número entero)/Age (In years, Discrete Number)',
nombre_usuario= 'Nombre del Usuario (OCULTO y no accesible)/Name of the User (Not Accessible)',
comuna_residencia= '(original, Recodificado en comuna_residencia_cod)/',
origen_de_ingreso= '(original, Recodificado en origen_ingreso)/',
pais_nacimiento= 'País de Nacimiento/Country of Birth',
nacionalidad= 'Nacionalidad/Nationality',
etnia= '(original, recodificado en etnia_cor)/',
estado_conyugal= '(original, Recodificado en estado_conyugal_2)/',
numero_de_hijos= 'Número de Hijos/Number of Children',
num_hijos_ing_trat_res= 'Número de Hijos para Ingreso a Tratamiento Residencial/Number of Children to Residential Treatment',
parentesco_con_el_jefe_de_hogar= '(Sólo presenta valores perdidos)/',
num_trat_ant= 'Número de Tratamientos Anteriores/Number of Previous Treatments',
fecha_ultimo_tratamiento= 'Fecha del Último Tratamiento/Date of the Last Treatment',
sustancia_de_inicio= '(original, Recodificado en sus_ini)/',
edad_inicio_consumo= '(original, Recodificado en edad_ini_cons)/', 
x_se_trata_mujer_emb= 'Mujer Embarazada al Ingreso/Pregnant at Admission',
escolaridad_ultimo_ano_cursado= '(original, Recodificado en escolaridad)/', 
condicion_ocupacional= '(original, Recodificado en estatus_ocupacional)/', 
categoria_ocupacional= '(original, Recodificado en cat_ocupacional)/',
rubro_trabaja= '(original, Recodificado en rubro_trabaja_mod)/',
con_quien_vive= 'Persona con la que vive el Usuario/People that Share Household with the User',
tipo_de_vivienda= '(original, Recodificado en tipo_de_vivienda_mod)/',
tenencia_de_la_vivienda= '(original, Recodificado en tenencia_de_la_vivienda_mod)/',
sustancia_principal= '(original, Recodificado en sus_principal)/',
`otras_sustancias_nº1`= '(original, Recodificado en otras_sus1)/',
`otras_sustancias_nº2`= '(original, Recodificado en otras_sus2)/',
`otras_sustancias_nº3`= '(original, Recodificado en otras_sus3)/',
freq_cons_sus_prin_original= '(original, Recodificado en freq_cons_sus_prin)/',
edad_inicio_sustancia_principal= '(original, Recodificado en edad_ini_sus_prin)/',
via_adm_sus_prin_original= '(original, Recodificado en via_adm_sus_prin)/',
dg_trs_cons_sus_or= 'Diagnósico de Trastorno por Consumo de Sustancias/Diagnosed of Substance Use Disorder',
dg_trs_psiq_dsm_iv_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios DSM IV/Diagnosis of Psychiatric Disorders, DSM-IV criteria',
dg_trs_psiq_sub_dsm_iv_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios DSM IV (Subclasificacion)/Diagnosis of Psychiatric Disorders, DSM-IV criteria (sub-classification)',
x2_dg_trs_psiq_dsm_iv_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios DSM IV (2)/Diagnosis of Psychiatric Disorders, DSM-IV criteria (2)',
x2_dg_trs_psiq_sub_dsm_iv_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios DSM IV (Subclasificacion) (2)/Diagnosis of Psychiatric Disorders, DSM-IV criteria (sub-classification) (2)',
x3_dg_trs_psiq_dsm_iv_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios DSM IV (3)/Diagnosis of Psychiatric Disorders, DSM-IV criteria (3)',
x3_dg_trs_psiq_sub_dsm_iv_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios DSM IV (Subclasificacion) (3)/Diagnosis of Psychiatric Disorders, DSM-IV criteria (sub-classification) (3)',
dg_trs_psiq_cie_10_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios CIE-10/Diagnosis of Psychiatric Disorders, CIE-10 criteria',
dg_trs_psiq_sub_cie_10_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios CIE-10 (Subclasificacion)/Diagnosis of Psychiatric Disorders, CIE-10 criteria (subclassification)',
x2_dg_trs_psiq_cie_10_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios CIE-10 (2)/Diagnosis of Psychiatric Disorders, CIE-10 criteria (2)',
x2_dg_trs_psiq_sub_cie_10_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios CIE-10 (Subclasificacion) (2)/Diagnosis of Psychiatric Disorders, CIE-10 criteria (subclassification) (2)',
x3_dg_trs_psiq_cie_10_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios CIE-10 (3)/Diagnosis of Psychiatric Disorders, CIE-10 criteria (3)',
x3_dg_trs_psiq_sub_cie_10_or= 'Diagnóstico de Trastorno Psiquiátrico, Criterios CIE-10 (Subclasificacion) (3)/Diagnosis of Psychiatric Disorders, CIE-10 criteria (subclassification) (3)',
diagnostico_trs_fisico= 'Diagnóstico de Trastorno Físico/Diagnosis of Physical Disorder',
otros_probl_at_sm_or= 'Otros Problemas de Atención Vinculados a Salud Mental/Other problems linked to Mental Health',
compromiso_biopsicosocial= 'Compromiso Biopsicosocial/Biopsychosocial Involvement',
dg_global_nec_int_soc_or= 'Diagnóstico Global de Necesidades de Integración Social (Al Ingreso)/Global Diagnosis of Social Integration (At Admission)',
dg_nec_int_soc_cap_hum_or= 'Diagnóstico de Necesidades de Integración Social en Capital Humano (Al Ingreso)/Global Diagnosis of Social Integration in Human Capital (At Admission)',
dg_nec_int_soc_cap_fis_or= 'Diagnóstico de Necesidades de Integración Social en Capital Físico (Al Ingreso)/Global Diagnosis of Social Integration in Physical Capital (At Admission)',
dg_nec_int_soc_cap_soc_or= 'Diagnóstico de Necesidades de Integración Social en Capital Social (Al Ingreso)/Global Diagnosis of Social Integration in Social Capital (At Admission)',
fech_ing= 'Fecha de Ingreso a Tratamiento/Date of Admission to Treatment',
fecha_ingreso_a_convenio_senda= 'Fecha de Ingreso a Convenio SENDA (aún no formateada como fecha)/Date of Admission to SENDA Agreement',
usuario_tribunal_trat_droga= 'Usuario de modalidad Tribunales de Tratamiento de Drogas/User of Drug Treatment Courts Modality',
consentimiento_informado= 'Consentimiento Informado/Informed Consent',
fech_egres= 'Fecha de Egreso de Tratamiento/Date of Discharge from Treatment',
motivodeegreso= 'Motivo de Egreso/Cause of Discharge',
tipo_centro_derivacion= 'Tipo de Centro al que el Usuario es Derivado/Type of Center of Derivation',
evaluacindelprocesoteraputico= 'Evaluación del Proceso Terapéutico/Evaluation of the Therapeutic Process',
eva_consumo= 'Evaluación al Egreso Respecto al Patrón de consumo/Evaluation at Discharge regarding to Consumption Pattern',
eva_fam= 'Evaluación al Egreso Respecto a Situación Familiar/Evaluation at Discharge regarding to Family Situation',
eva_relinterp= 'Evaluación al Egreso Respecto a Relaciones Interpersonales/Evaluation at Discharge regarding to Interpersonal Relations',
eva_ocupacion= 'Evaluación al Egreso Respecto a Situación Ocupacional/Evaluation at Discharge regarding to Occupational Status',
eva_sm= 'Evaluación al Egreso Respecto a Salud Mental/Evaluation at Discharge regarding to Mental Health',
eva_fisica= 'Evaluación al Egreso Respecto a Salud Física/Evaluation at Discharge regarding to Physical Health',
eva_transgnorma= 'Evaluación al Egreso Respecto a Trasgresión a la Norma Social/Evaluation at Discharge regarding to Transgression to the Norm',
dg_trs_psiq_cie_10_egres_or= '(Sólo presenta valores perdidos)/',
dg_global_nec_int_soc_or_1= 'Diagnóstico Global de Necesidades de Integración Social (Al Egreso)/Global Diagnosis of Social Integration (At Discharge)',
dg_nec_int_soc_cap_hum_or_1= 'Diagnóstico de Necesidades de Integración Social en Capital Humano (Al Egreso)/Global Diagnosis of Social Integration in Human Capital (At Discharge)',
dg_nec_int_soc_cap_fis_or_1= 'Diagnóstico de Necesidades de Integración Social en Capital Físico (Al Egreso)/Global Diagnosis of Social Integration in Physical Capital (At Discharge)',
dg_nec_int_soc_cap_soc_or_1= 'Diagnóstico de Necesidades de Integración Social en Capital Social (Al Egreso)/Global Diagnosis of Social Integration in Social Capital (At Discharge)',
tiene_menores_de_edad_a_cargo= 'Menores de Edad A Cargo/Minor Dependants',
mot_egres_alt_adm_or= 'Motivo de Egreso Alta Administrativa/Cause of Administrative Discharge',
consorcio=  'Sociedades de Tratamiento Servicios de Salud- Fundaciones- entre otras entidades encargadas de los centros/Consortium',
id_centro= 'ID de Centro/Treatment center ID',
ha_estado_embarazada_egreso= '¿Ha estado embarazada? (al Egreso)/Have you been Pregnant (at Discharge)',
identidad_de_genero= 'Identidad de Género/Gender Identity',
discapacidad= 'Presenta Discapacidad/Disability',
hash_rut_completo= 'HASH alternativo, en el escenario en que se asuma que el individuo al que se le codificó el RUN presente mayor edad/Alternative HASH-Key',
opcion_discapacidad= 'Origen de Discapacidad/Cause of Disability',
sexo_2= 'Sexo Usuario/Sex of User',
embarazo= 'Embarazo al Ingreso /Pregnant at Admission',
tipo_de_plan_2= 'Tipo de Plan/Type of Plan',
tipo_de_programa_2= 'Tipo de Programa de Tratamiento/Type of Program',
fech_egres_sin_fmt= 'Fecha de Egreso de Tratamiento (Sin Formato de Fecha)/Date of Discharge',
id_mod= 'ID de SENDA para Presentación en Página Web (enmascara caracteres 5 y 6)/SENDA ID (mask characters 5 & 6)',
ano_nac= 'Año de Nacimiento (numérico)/Year of Birth (numeric)',
fech_ing_ano= 'Año de Ingreso (numérico)/Year of Admission (numeric)',
fech_ing_mes= 'Mes de Ingreso (numérico)/Month of Admission (numeric)',
fech_ing_dia= 'Día de Ingreso (numérico)/Day of Admission (numeric)',
concat= 'ID de SENDA y HASH Concatenado (permite discriminar más de un HASH en un mismo ID)/Combination of SENDA ID & HASH',
obs= 'Observaciones al Proceso de Limpieza y Estandarización de Casos/Observations to the Process of Data Tidying & Standardization',
dias_trat_inv= 'Días de Tratamiento Invertidos (fecha más reciente, menor valor numérico)/Treatment Days (Reversed)',
fech_nac= 'Fecha de Nacimiento/Date of Birth',
edad_al_ing= 'Edad a la Fecha de Ingreso a Tratamiento (numérico continuo)/Age at Admission to Treatment',
edad_ini_cons= 'Edad de Inicio de Consumo/Age of the Onset of Drug Use',
edad_ini_sus_prin=  'Edad de Inicio de Consumo Sustancia Principal/Age of the Onset of Drug Use of Primary Substance',
dias_trat_alta_temprana= 'Días de tratamiento (<90)/Less than 90 days in treatment',
motivodeegreso_mod= 'Motivo de Egreso (con abandono temprano y tardío)/Cause of Discharge (with late and early withdrawal)',
sus_principal= 'Sustancia Principal de Consumo/Primary or Main Substance of Consumption at Admission',
otras_sus1= 'Otras Sustancias (1)/Other Substances (1)',
otras_sus2= 'Otras Sustancias (2)/Other Substances (2)',
otras_sus3= 'Otras Sustancias (3)/Other Substances (3)',
sus_ini= 'Sustancia de Inicio/Starting Substance',
estado_conyugal_2= 'Estado Conyugal/Marital Status',
estatus_ocupacional= 'Condición Ocupacional/Occupational Status',
cat_ocupacional= 'Categoría Ocupacional/Occupational Category',
edad_grupos= 'Edad agrupada/Age in groups',
origen_ingreso= "(modificado en origen_ingreso_mod)/",
escolaridad= 'Escolaridad: Nivel Eduacional/Educational Attainment',
via_adm_sus_prin= 'Vía de Administración de la Sustancia Principal/Route of Administration of the Primary or Main Substance',
freq_cons_sus_prin= 'Frecuencia de Consumo de la Sustancia Principal (30 días previos a la admisión)/Frequency of Consumption of the Primary or Main Substance (30 days previous to admission)',
dias_trat_knn_imp= 'Días de Tratamiento (Imputados KNN)/Days of Treatment (Imputed KNN)',
fech_egres_knn_imp= 'Fecha de Egreso (Imputados KNN)/Date of Discharge (Imputed KNN)',
dias_trat_alta_temprana_knn_imp= 'Días de Tratamiento con Alta Temprana (<90) (Imputados KNN)/Days of Treatment w Early Withdrawal (Imputed KNN)',
fech_egres_imp= 'Fecha de Egreso (Imputados KNN & Lógico)/Date of Discharge (Imputed KNN & Logic)',
motivodeegreso_imp= 'Motivo de Egreso(Imputados KNN & Lógico)/Cause of Discharge (Imputed KNN & Logic)',
motivodeegreso_mod_imp= 'Motivo de Egreso (con abandono temprano y tardío)(Imputados KNN & Lógico)/Cause of Discharge (with late and early withdrawal)(Imputed KNN & Logic)',
dias_trat_imp= 'Días de Tratamiento (Imputados KNN & Lógico)/Days of Treatment (Imputed KNN & Logic)', 
dias_trat_alta_temprana_imp= 'Días de Tratamiento con Alta Temprana (<90) (Imputados KNN & Lógico)/Days of Treatment w Early Withdrawal (Imputed KNN & Logic)',
via_adm_sus_prin_act= 'Vía de Administración de la Sustancia Principal (Se aplicaron criterios de limpieza)/Route of Administration of the Primary or Main Substance (Tidy)',
etnia_cor= 'Etnia/Ethnic Group',
nacionalidad_2= 'Segunda Nacionalidad/Second Nationality',
etnia_cor_2= 'Etnia (2)/Second Ethnic Group',
sus_ini_2= 'Segunda Sustancia de Inicio/Second Starting Substance',
sus_ini_3= 'Tercera Sustancia de Inicio/Third Starting Substance',
concat_hash_sus_prin= 'Combination of User & Primary Substance',
macrozona= "Macrozona/Macrozones",
nombre_region= " Región del Centro/Chilean Region of the Center",
comuna_residencia_cod= "Comuna de Residencia/Municipality or District of Residence",
sus_ini_mod= "Sustancia de Inicio (Sólo más frecuentes)/Starting Substance (Only more frequent)",
sus_principal_mod= 'Sustancia Principal de Consumo (Sólo más frecuentes)/Primary or Main Substance of Consumption at Admission (Only more frequent)',
origen_ingreso_mod= 'Origen de Ingreso/Motive of Admission to Treatment',
tipo_de_vivienda_mod= 'Tipo de Vivienda/Type of Housing', 
tenencia_de_la_vivienda_mod= 'Tenencia de la Vivienda/Tenure status of Households',
rubro_trabaja_mod= 'Rubro de Trabajo/Area of Work',
edad_al_ing_grupos= 'Edad a la Fecha de Ingreso a Tratamiento en Grupos/Age at Admission to Treatment In Groups',
menor_60_dias_diff= 'Menor a 60 días de diferencia con el registro posterior/Menor a 60 days of difference between the next entry',
menor_45_dias_diff= 'Menor a 45 días de diferencia con el registro posterior/Less than 45 days of difference between the next entry',
diff_bet_treat= 'Días de diferencia con el registro posterior/Days of difference between the next entry',
id_centro_sig_trat= "ID del Centro del registro posterior/Center ID of the Next Treatment",
tipo_plan_sig_trat= "Tipo de Plan del registro posterior/Type of Plan of the Next Entry",
tipo_programa_sig_trat= "Tipo de Programa del registro posterior/Type of Program of the Next Entry", 
senda_sig_trat= "SENDA del registro posterior/SENDA of the Next Entry",
motivoegreso_derivacion= "Motivo de Egreso= Derivación/Cause of Discharge= Derivación",
obs_cambios= "Cambios del tratamiento en comparación al registro posterior/Changes in treatment compared to the Next Entry",
obs_cambios_ninguno= "Sin cambios del tratamiento en comparación al registro posterior/No changes in treatment compared to the Next Entry",
obs_cambios_num= "Recuento de cambios del tratamiento en comparación al registro posterior/Count of changes in treatment compared to the Next Entry",
obs_cambios_fac= "Recuento de cambios del tratamiento en comparación al registro posterior(factor)/Count of changes in treatment compared to the Next Entry(factor)",
at_least_one_cont_entry= "Casos de Usuarios con más de una entrada después de otra/Cases of users with more than one entry after another one"
)
```

# Session Info

```{r session_info, echo=T, error=T, paged.print=TRUE}
Sys.getenv("R_LIBS_USER")

paste0("Editor context: ", path)

if (grepl("CISS Fondecyt",rstudioapi::getSourceEditorContext()$path)==T){
    save.image("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2022 (github)/11.RData")
  } else if (grepl("andre",rstudioapi::getSourceEditorContext()$path)==T){
    save.image("C:/Users/andre/Desktop/SUD_CL/11.RData")
  } else if (grepl("E:",rstudioapi::getSourceEditorContext()$path)==T){
    save.image("E:/Mi unidad/Alvacast/SISTRAT 2022 (github)/11.RData")
  } else {
    save.image(paste0(sub("SUD_CL","",path),"11.RData"))
  }

sessionInfo()
sesion_info <- devtools::session_info()
dplyr::select(
  tibble::as_tibble(sesion_info$packages),
  c(package, loadedversion, source)
) %>% 
  DT::datatable(filter = 'top', colnames = c('Row number' =1,'Variable' = 2, 'Percentage'= 3),
              caption = htmltools::tags$caption(
        style = 'caption-side: top; text-align: left;',
        '', htmltools::em('Packages')),
      options=list(
initComplete = htmlwidgets::JS(
      "function(settings, json) {",
      "$(this.api().tables().body()).css({'font-size': '80%'});",
      "}")))
```

# Exportar

```{r export, warning=FALSE, echo=T}
  Base_fiscalia_v2 %>% 
  dplyr::mutate(accused=dplyr::case_when(encontrado_como_victima=="SI" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 encontrado_como_victima=="NO" & encontrado_como_imputado=="SI"~"IMPUTADO",
                                 T~"VICTIMA")) %>% 
  dplyr::filter(accused=="VICTIMA") %>% 
    rio::export(file = paste0(gsub("SUD_CL","",path),"fiscalia_mariel_ago_2022.dta"))
```


```{r label_to_stata, echo=T, paged.print=TRUE}

export_lab_stata_merge<-
  tibble::rownames_to_column(data.frame(Hmisc::label(Base_fiscalia_v2)))%>% data.frame() %>%
  dplyr::rename("code" = !!names(.[1]), "label" = !!names(.[2]))%>% data.frame()%>%
  dplyr::mutate(first= "cap noi label variable")%>%
  dplyr::mutate(final= paste0(first, " ",code,' "',label,'"'))%>%
  dplyr::select(-code,-label,-first)%>%
  dplyr::rename("*clear all"="final") %>% 
  rbind(paste0('cap noi save "', gsub('/', '\\', path, fixed=T),'\\fiscalia_mariel_ago_2022.dta", replace'))%>%
  rbind('cap noi drop id id_mod nombre_centro consentimiento_informado')%>%
  rbind('cap noi drop id id_mod nombre_centro')%>%
  rbind(paste0('cap noi save "', gsub('/', '\\', path, fixed=T),'\\fiscalia_mariel_ago_2022.dta", replace'))

rbind(paste0('cap noi use "', gsub('/', '\\', path, fixed=T),'\\fiscalia_mariel_ago_2022.dta", clear'),export_lab_stata_merge) %>% knitr::kable("html") %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size =10) %>% 
  kableExtra::scroll_box(width = "100%", height = "375px")

write.table(rbind(paste0('cap noi use "', gsub('/', '\\', path, fixed=T),'\\fiscalia_mariel_ago_2022.dta", clear'),export_lab_stata_merge), file = paste0(path,"/SUD_CL/_label_var_to_stata.do"), sep = "",row.names = FALSE, quote = FALSE, fileEncoding="UTF-8")
```

<br>

<div style="border: 1px solid #ddd; padding: 5px; overflow-y: scroll; height:350px; overflow-x: scroll; width:100%">

```{stata 2, collectcode=F, include=T, error=T, cleanlog=F}
*should be in the same folder of the .Rmd to work
cap noi do _label_var_to_stata.do
```

</div>
