---
title: "Risk among Drug Dependent Women Treated in Women-Only versus Mixed-Gender Programs in Chile*"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide  
    toc: true # table of content true
    toc_depth: 5  # upto three depths of headings (specified by #, ## and ###)
    toc_float: true
---



```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

<style type="text/css">
.tablelines table, .tablelines td, .tablelines th {
        border: 1px solid black;
        }
.centrado {
    text-align: center;
}
.table.center {
    margin-left:auto; 
    margin-right:auto;
  }
.table_wrapper{
    display: block;
    overflow-x: auto;
    white-space: nowrap;
}
code.r{
  font-size: 8px;
}
body{ /* Normal  */
      text-align: justify;
  }
.superbigimage{
    overflow-y:scroll;
    white-space: nowrap;
}
.superbigimage img{
    overflow-y: scroll;
    overflow-x: hidden;
}
</style>

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px; text-align: justify;}
</style>

```{r prev_setup, include = FALSE, cache=T}
rm(list=ls());gc()
if(!grepl("4.0.2",R.version.string)){stop("Different version (must be 4.0.2)")}
load("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/9.Rdata")
rm(list=setdiff(ls(), c("CONS_C1_df_dup_SEP_2020_match","CONS_C1_df_dup_SEP_2020","CONS_C1", "CONS_C1_df_dup_JUL_2020","CONS_C1_df_dup_JUN_2020")))

unlink('G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/SUD_CL/*_cache', recursive = TRUE)
```

```{r setup, include = FALSE, cache=T}
#Libraries used in the routine. Dont change the order
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})
copiar_nombres <- function(x,row.names=FALSE,col.names=TRUE,dec=",",...) {
  if(class(ungroup(x))[1]=="tbl_df"){
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)    
        }
  } else {
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)       
  }
 }
}  
#packageVersion("codebook")
#https://github.com/RevolutionAnalytics/checkpoint
#if(!require(checkpoint)){install.packages("checkpoint")}
#if(!require(here)){install.packages("here")}
#checkpoint::checkpoint("2020-02-19",project=here::here(),checkpointLocation=paste0(here::here(),"/dedup"), use.lock=F, use.knitr=T, auto.install.knitr = T,scan.rnw.with.knitr=T, forceInstall=T,scanForPackages = TRUE)
#checkpointArchives(tempdir(), full.names = TRUE)

#if(!require(tidyr)){install.packages("tidyr")}
#if(!require(DataExplorer)){install.packages("DataExplorer")}
#if(!require(stringi)){install.packages("stringi")}
#if(!require(stringr)){install.packages("stringr")}
#if(!require(ggplot2)){install.packages("ggplot2")}
#if(!require(Hmisc)){install.packages("Hmisc")}
#if(!require(kableExtra)){install.packages("kableExtra")}
#if(!require(plotly)){install.packages("plotly")}
#if(!require(rbokeh)){install.packages("rbokeh")}
#if(!require(altair)){install.packages("altair")}
#if(!require(zoo)){install.packages("zoo")}
#if(!require(codebook)){install.packages("codebook")}
#if(!require(broom)){install.packages("broom")}
#if(!require(sqldf)){install.packages("sqldf")} 
#if(!require(devtools)){install.packages("devtools")}
#if(!require(Statamarkdown)){install_github("hemken/Statamarkdown")}
#if(!require(data.table)){install.packages("data.table")}
#if(!require(dplyr)){install.packages("dplyr")}

#if(!require(boot)){install.packages("boot")}
#if(!require(plyr)){install.packages("plyr")}
#if(!require(matrixStats)){install.packages("matrixStats")}
#if(!require(radiant)){install.packages("radiant", repos = "https://radiant-rstats.github.io/minicran/")}

try(library(boot))
library(matrixStats)
library(knitr)
library(tidyr)
library(stringi)
library(stringr)
library(ggplot2)
library(Hmisc)
library(kableExtra)
library(plotly)
library(janitor)
library(rbokeh)
library(altair)
library(zoo)
library(broom)
library(sqldf)
library(devtools)
library(codebook)
library(data.table)
library(dplyr)
library(panelr)
library(RColorBrewer)
library(choroplethr)
library(choroplethrMaps)
library(choroplethrAdmin1)
library(lsmeans)
library(finalfit)
library(chilemapas)
suppressPackageStartupMessages(library(ggiraph))
suppressPackageStartupMessages(library(sf))
library(treemapify)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
library(choroplethrAdmin1)
library(tidyverse)
library(epiR)
library(survminer)
library(rateratio.test)  
library(ggfortify)
library(survMisc)

library(designmatch)
library(glpkAPI) #
library(foreign)
library(Hmisc)
library(gridExtra)
library(exactRankTests)
library(ggplot2)
library(reshape2)
library(stargazer)
library(Rglpk)
library(tableone)
library(MatchIt)
library(sensitivity2x2xk)
library(sensitivityfull)
library(cobalt)
library(eha)
library(igraph)
library(mstate)
library(Amelia)
library(DiagrammeR) 
library(mstate)
library(flexsurv)
library(muhaz)

#devtools::install_github('ChristopherLucas/MatchingFrontier')

if(!require(radiant.update)){install.packages("radiant.update", repos = "https://radiant-rstats.github.io/minicran/")}
#install.packages( repos = "https://radiant-rstats.github.io/minicran/")
#install.packages("radiant.update", repos = "https://radiant-rstats.github.io/minicran/")

#tryCatch(source("https://raw.githubusercontent.com/radiant-rstats/minicran/gh-pages/update.R"), error = function(e) print("updated package, radiant"))

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

try_with_time_limit <- function(expr, cpu = Inf, elapsed = Inf)
{
  y <- try({setTimeLimit(cpu, elapsed); expr}, silent = TRUE) 
  if(inherits(y, "try-error")) NULL else y 
}
eval_fork <- function(..., timeout=60){

  #this limit must always be higher than the timeout on the fork!
  setTimeLimit(timeout+5);      

  #dispatch based on method
  ##NOTE!!!!! Due to a bug in mcparallel, we cannot use silent=TRUE for now.
  myfork <- parallel::mcparallel({
    eval(...)
  }, silent=FALSE);

  #wait max n seconds for a result.
  myresult <- parallel::mccollect(myfork, wait=FALSE, timeout=timeout);

  #try to avoid bug/race condition where mccollect returns null without waiting full timeout.
  #see https://github.com/jeroenooms/opencpu/issues/131
  #waits for max another 2 seconds if proc looks dead 
  while(is.null(myresult) && totaltime < timeout && totaltime < 2) {
     Sys.sleep(.1)
     enddtime <- Sys.time();
     totaltime <- as.numeric(enddtime - starttime, units="secs")
     myresult <- parallel::mccollect(myfork, wait = FALSE, timeout = timeout);
  }

  #kill fork after collect has returned
  tools::pskill(myfork$pid, tools::SIGKILL);    
  tools::pskill(-1 * myfork$pid, tools::SIGKILL);  

  #clean up:
  parallel::mccollect(myfork, wait=FALSE);

  #timeout?
  if(is.null(myresult)){
    stop("R call did not return within ", timeout, " seconds. Terminating process.", call.=FALSE);      
  }

  #move this to distinguish between timeout and NULL returns
  myresult <- myresult[[1]];

  #reset timer
  setTimeLimit();     

  #forks don't throw errors themselves
  if(inherits(myresult,"try-error")){
    #stop(myresult, call.=FALSE);
    stop(attr(myresult, "condition"));
  }

  #send the buffered response
  return(myresult);  
}
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#GET LOCAL
#dir.create(paste0(getwd(),"/renv_local"))
#Sys.setenv(RENV_PATHS_LOCAL = paste0(getwd(),"/renv_local"))
#install.packages(paste0(getwd(),"/renv_local/gurobi_9.1-0.zip"), repos = NULL, type="source")
#install.packages(paste0("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/renv_local/gurobi_9.1-0.zip"), repos = NULL, type="source")
library(gurobi)
#"G:/Mi unidad/Alvacast/SISTRAT 2019 (github)"
#Sys.getenv("R_LIBS_USER")
```

# Steps

## Database consolidation


We selected women at baseline (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>% nrow() %>% format(big.mark=",")`) in the following variables of interest:

<!--- EN EXCEL:  ="- '"&L8&"'"&"("&"`"&K8&"`"&")" 
tipo_de_programa_2, edad_al_ing_grupos,  estado_conyugal_2, numero_de_hijos_mod, embarazo, sus_principal_mod, otras_sus1_mod, freq_cons_sus_prin, compromiso_biopsicosocial, tipo_centro, servicio_de_salud, tipo_de_plan_2, edad_ini_sus_prin_grupos, tenencia_de_la_vivienda_mod
ME FALTA TENENCIA DE LA VIVIENDA, EDAD INICIO SUSTANCIA PRINCIPAL, TIPO DE PLAN Y TIPO DE PROGRAMA, SERVICIO DE SALUD, COMPROMISO BIOPSICOSOCIAL, SUSTANCIA PRINCIPAL MOD Y OTRAS SUSTANCIAS, EMBARAZO, NUMERO DE HIJOS A TRATAMIENTO RESIDENCIAL Y NUMERO DE HIJOS.
--->

- 'Type of program'(`tipo_de_programa_2`)
- 'Marital status'(`estado_conyugal_2`)
- 'Educational Attainment' (`escolaridad_rec`)= We selected the most vulnerable category among continous treatments for the same user.
- 'Age at admission to treatment, grouped'(`edad_al_ing_grupos`)= We grouped people with less than 18 years old (`r scales::percent(CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1,edad_al_ing_grupos=='<18') %>% nrow()/nrow(CONS_C1_df_dup_SEP_2020 %>%  dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1)),accuracy = .01)`) with '18-29' years old (`r scales::percent(CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1,edad_al_ing_grupos=='18-29') %>% nrow()/nrow(CONS_C1_df_dup_SEP_2020 %>%  dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1)),accuracy = .01)`).
- 'Consumption frequency of primary or main substance'(`freq_cons_sus_prin`)= Among the categories of the Frequency of Drug Consumption, we grouped Less than 1 day a week (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(freq_cons_sus_prin) %>% dplyr::filter(freq_cons_sus_prin=="Less than 1 day a week") %>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`) with Did not use in the last 30 days (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(freq_cons_sus_prin) %>% dplyr::filter(freq_cons_sus_prin=="Did not use") %>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`)
- 'Pregnant at admission'(`embarazo`)
- 'Tenure status of households' (`tenencia_de_la_vivienda_mod`)= Three categories were collapsed into one single condition: Owner (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(tenencia_de_la_vivienda_mod) %>% dplyr::filter(tenencia_de_la_vivienda_mod=="Propia") %>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`), with Transferred dwellings (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(tenencia_de_la_vivienda_mod) %>% dplyr::filter(tenencia_de_la_vivienda_mod=="Cedida") %>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`) and Pays Dividend (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(tenencia_de_la_vivienda_mod) %>% dplyr::filter(tenencia_de_la_vivienda_mod=="Paga dividendo") %>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`).
- 'Primary or main substance'(`sus_principal_mod`)= We used the primary substance at admission of the largest treatment for continuous treatments. Every substance was chosen from the largest treatment, excepting cases where the value was not available in the largest treatment.
- 'Co-occurring SUD' (`num_otras_sus_mod`)= We counted the times that different substances at admission appear for each entry.
- 'Number of children (max. Value) (Dichotomized)'(`numero_de_hijos_mod_rec`)= We selected the number of children with the maximum value among continuous treatments. We decided to dichotomize between no children (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(numero_de_hijos_mod) %>% dplyr::filter(numero_de_hijos_mod==0) %>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`) and children (`r CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(as.character(sexo_2)=="Women") %>% dplyr::filter(dup==1) %>%  janitor::tabyl(numero_de_hijos_mod) %>% dplyr::mutate(numero_de_hijos_mod=as.numeric(numero_de_hijos_mod)) %>%  dplyr::filter(numero_de_hijos_mod>0) %>% summarise(n=sum(n),percent=sum(percent),valid_percent=sum(valid_percent))%>% dplyr::select(percent) %>% as.numeric() %>% scales::percent(accuracy = .01)`).
- 'Treatment Setting'(`tipo_de_plan_res`)= We dichotomized into Residntial and Outpatient treatments.

<br>

```{r tab1, echo=FALSE}
toString2<-
function (x, width = NULL, ...) 
        {
            string <- paste(x, collapse = "; ")
            if (missing(width) || is.null(width) || width == 0) 
                return(string)
            if (width < 0) 
                stop("'width' must be positive")
            if (nchar(string, type = "w") > width) {
                width <- max(6, width)
                string <- paste0(strtrim(string, width - 4), "....")
            }
            string
        }

CONS_C1_df_dup_SEP_2020_women<-
  CONS_C1_df_dup_SEP_2020 %>%
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  #FILTRO A MUJERES
  dplyr::filter(as.character(sexo_2)=="Women") %>% 
  dplyr::filter(dup==1) %>% 
  #TRATAMIENTOS RESIDENCIALES
  dplyr::mutate(tipo_de_plan_res=dplyr::case_when(grepl("PR",as.character(tipo_de_plan_2))~"Residential",
                                                  grepl("PAI",as.character(tipo_de_plan_2))~"Outpatient",
                                                  grepl("PAB",as.character(tipo_de_plan_2))~"Outpatient",
                                                  TRUE~NA_character_)) %>% 
  dplyr::mutate(tipo_de_plan_res=factor(tipo_de_plan_res)) %>% 
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  #EMBARAZO
  dplyr::mutate(embarazo=factor(if_else(as.character(embarazo)=="Si",TRUE,FALSE,NA))) %>% 
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  #TENENCIA VIVIENDA
  #Allegado, Arrienda, Cedida, Ocupación Irregular, Otros, Paga dividendo, Propia
#vive transitoriamente en casa ajena
  dplyr::mutate(tenencia_de_la_vivienda_mod=
                  factor(dplyr::case_when(tenencia_de_la_vivienda_mod=="Allegado"~"Stays temporarily with a relative",
                                 tenencia_de_la_vivienda_mod=="Arrienda"~"Renting",
                                 tenencia_de_la_vivienda_mod=="Cedida"~"Owner/Transferred dwellings/Pays Dividends",
                                 tenencia_de_la_vivienda_mod=="Ocupación Irregular"~"Illegal Settlement",
                                 tenencia_de_la_vivienda_mod=="Otros"~"Others",
                                 tenencia_de_la_vivienda_mod=="Paga dividendo"~"Owner/Transferred dwellings/Pays Dividends",
                                 tenencia_de_la_vivienda_mod=="Propia"~"Owner/Transferred dwellings/Pays Dividends",
                                 T~NA_character_))) %>% 
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  #EDAD EN GRUPOS: menores de 18, dejar en categoría combinada
  dplyr::mutate(edad_al_ing_grupos=if_else(edad_al_ing_grupos=='<18','18-29',as.character(edad_al_ing_grupos),NA_character_)) %>%
  dplyr::mutate(edad_al_ing_grupos=if_else(edad_al_ing_grupos=='18-29','<18-29',as.character(edad_al_ing_grupos),NA_character_)) %>%
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  #FRECUENCIA CONSUMO: Regroup 1 día a la semana y No usó en el último mes
  dplyr::mutate(freq_cons_sus_prin=if_else(freq_cons_sus_prin=='Did not use','Less than 1 day a week',as.character(freq_cons_sus_prin),NA_character_)) %>% 
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  #OTHER SUBSTANCES:
  dplyr::mutate_at(vars(c("otras_sus1_mod", "otras_sus2_mod", "otras_sus3_mod")), 
                   ~dplyr::case_when(
                    as.character(.)=="Pasta Base"~"Cocaine paste",
                    as.character(.)=="Cocaína"~"Cocaine hydrochloride",
                    as.character(.)=="Marihuana"~"Marijuana",
                    as.character(.)=="Alcohol"~"Alcohol",
                    as.character(.)=="Otros"~"Other",
                    T~NA_character_
                    )) %>% 
  dplyr::mutate(otras_sus_mod = pmap_chr(dplyr::select(.,otras_sus1_mod:otras_sus3_mod), ~toString2(unique(na.omit(c(...)))))) %>% 
  tidyr::separate(otras_sus_mod,into=paste0("otras_sus_mod_",1:3), sep="; ")%>%
  #dplyr::select(row,sus_principal_mod,otras_sus1_mod,otras_sus2_mod,otras_sus3_mod,otras_sus_mod_1,otras_sus_mod_2,otras_sus_mod_3)%>% 
  dplyr::mutate(otras_sus_mod_1=if_else(otras_sus_mod_1=="",NA_character_,otras_sus_mod_1)) %>% 
  rowwise %>%
  dplyr::mutate_at(.vars = vars(c("otras_sus_mod_1","otras_sus_mod_2", "otras_sus_mod_3")),
                 .funs = list(`nas`=~ifelse(is.na(.), 0, 1))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(num_otras_sus_mod = base::rowSums(dplyr::select(., otras_sus_mod_1_nas, otras_sus_mod_2_nas, otras_sus_mod_3_nas),na.rm=T))%>%
  dplyr::mutate(num_otras_sus_mod= dplyr::case_when(num_otras_sus_mod==0 & !is.na(sus_principal_mod) ~'No additional substance',
                                                    num_otras_sus_mod==1~'One additional substance',
                                                    num_otras_sus_mod==2~'More than one additional substance',
                                                    T~NA_character_)) %>% 
  #PARA ESTUDIARLOS
  #dplyr::select(row, sus_principal_mod, otras_sus1_mod, otras_sus2_mod, otras_sus3_mod, otras_sus_mod_1, otras_sus_mod_2, otras_sus_mod_3, otras_sus_mod_1_nas, otras_sus_mod_2_nas, otras_sus_mod_3_nas, num_otras_sus_mod) %>% 
  #janitor::tabyl(num_otras_sus_mod)
  #janitor::tabyl(num_otras_sus_mod)
  #dplyr::select(-c(otras_sus1_mod, otras_sus2_mod, otras_sus3_mod, otras_sus_mod_1, otras_sus_mod_2, otras_sus_mod_3, otras_sus_mod_1_nas, otras_sus_mod_2_nas, otras_sus_mod_3_nas)) %>% 
  #janitor::tabyl(sus_principal_mod, num_otras_sus_mod)
  
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
 #SUSTANCIA PRINCIPAL (TRATAMIENTO MÁS LARGO, IGUAL QUE OTRAS SUS1 A OTAS SUS3)
  
  #:#:#:#:#:#:#:#:#:#:#:#:#:#:#:  
 #TIENE O NO HIJOS Tieneo no hijos (variable dicotómica): si tiene o no hijos
  dplyr::mutate(numero_de_hijos_mod_rec=factor(dplyr::if_else(numero_de_hijos_mod>0, "Yes","No",NA_character_))) %>% 

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:   
#:#:#:#:#:#:#:#:#:#DAR ESTRUCTURA ORDINAL#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  dplyr::mutate(edad_al_ing_grupos=parse_factor(as.character(edad_al_ing_grupos),levels=c('<18-29', '30-39', '40-49', '50+'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
    dplyr::mutate(escolaridad_rec=parse_factor(as.character(escolaridad_rec),levels=c('3-Completed primary school or less', '2-Completed high school or less', '1-More than high school'), ordered =T,trim_ws=T,include_na =F, locale=locale(encoding = "Latin1"))) %>%  
  dplyr::mutate(freq_cons_sus_prin=parse_factor(as.character(freq_cons_sus_prin),levels=c('Less than 1 day a week','2 to 3 days a week','4 to 6 days a week','1 day a week or more','Daily'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
  dplyr::mutate(compromiso_biopsicosocial=parse_factor(as.character(compromiso_biopsicosocial),levels=c('1-Mild', '2-Moderate','3-Severe'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
    dplyr::mutate(num_otras_sus_mod=parse_factor(as.character(num_otras_sus_mod),levels=c('No additional substance', 'One additional substance','More than one additional substance'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
    dplyr::mutate(edad_ini_sus_prin_grupos=parse_factor(as.character(edad_ini_sus_prin_grupos),levels=c('<=15', '16-18', '19-24', '>=25'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  data.table::data.table()

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

attr(CONS_C1_df_dup_SEP_2020_women$tipo_de_programa_2,"label") <- 'Type of program'
attr(CONS_C1_df_dup_SEP_2020_women$edad_al_ing_grupos,"label") <- 'Age at admission to treatment, grouped.'
attr(CONS_C1_df_dup_SEP_2020_women$estado_conyugal_2,"label") <- 'Marital status'
attr(CONS_C1_df_dup_SEP_2020_women$numero_de_hijos_mod_rec,"label") <- 'Have children (Dichotomized)'
attr(CONS_C1_df_dup_SEP_2020_women$num_hijos_trat_res_mod,"label") <- 'Number of children into a residential treatment'
attr(CONS_C1_df_dup_SEP_2020_women$sus_principal_mod,"label") <- 'Primary or main substance'
attr(CONS_C1_df_dup_SEP_2020_women$num_otras_sus_mod,"label") <- 'Co-occurring SUD'
attr(CONS_C1_df_dup_SEP_2020_women$freq_cons_sus_prin,"label") <- 'Consumption frequency of primary or main substance'
attr(CONS_C1_df_dup_SEP_2020_women$compromiso_biopsicosocial,"label") <- 'Biopsychosocial involvement'
attr(CONS_C1_df_dup_SEP_2020_women$tipo_de_plan_res,"label") <- 'Setting of Treatment'
attr(CONS_C1_df_dup_SEP_2020_women$tenencia_de_la_vivienda_mod,"label") <- 'Tenure status of households'
attr(CONS_C1_df_dup_SEP_2020_women$escolaridad_rec,"label") <- 'Educational Attainment'

attr(CONS_C1_df_dup_SEP_2020_women$tipo_centro,"label") <- 'Type of center of the last entry'
attr(CONS_C1_df_dup_SEP_2020_women$embarazo,"label") <- 'Pregnant at admission'
attr(CONS_C1_df_dup_SEP_2020_women$edad_ini_sus_prin_grupos,"label") <- 'Age at first use of principal substance, grouped'

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#tipo_de_programa_2 edad_al_ing_grupos estado_conyugal_2 numero_de_hijos_mod_rec

#-         Estadoconyugal:
#-         Edad:menores de 18, dejar en categoría combinada
#-         Educationalattainment
#-         Sustancia“más vulnerable” à variableoriginal sustancia principal
#-         Frecuenciade consumo: reagrupar 1 día a la semana y de 1 a 3: las primeras 2 categoríasen una. Documentar cuál era el porcentaje de respuesta original.
#-         CompromisoBiopsicosocial?
#-         Tipode vivienda: propia con cedida, combinarla en una sola. Paga dividendo también.
#-         Co-occurringSUD: hacerlo en base a otras_sus1 a 3, coocurrencia por trastorno por uso desustancias. Ver el número, si hay 10% o más, crear una categoría mayor.
#-         Tieneo no hijos (variable dicotómica): si tiene o no hijos
library(compareGroups)
table22 <- 
  compareGroups::compareGroups(tipo_de_programa_2 ~ estado_conyugal_2+ edad_al_ing_grupos+ escolaridad_rec+ sus_principal_mod+ freq_cons_sus_prin+ compromiso_biopsicosocial+ tenencia_de_la_vivienda_mod+ num_otras_sus_mod+ numero_de_hijos_mod_rec+ tipo_de_plan_res,
                                       method= c(estado_conyugal_2=3,
                                                 edad_al_ing_grupos=3,
                                                 escolaridad_rec=3,
                                                 sus_principal_mod=3,
                                                 freq_cons_sus_prin=3,
                                                 compromiso_biopsicosocial=3,
                                                 tenencia_de_la_vivienda_mod=3,
                                                 num_otras_sus_mod=3,
                                                 numero_de_hijos_mod_rec=3,
                                                 tipo_de_plan_res=3
                                                 ),
                                       data = CONS_C1_df_dup_SEP_2020_women,
                                       include.miss = T,
                                       var.equal=T
)

pvals2 <- getResults(table22)
#p.adjust(pvals, method = "BH")
restab22 <- createTable(table22, show.p.overall = T)
compareGroups::export2md(restab22, size=13, first.strip=T, hide.no="no", position="center",
                         format="html",caption= "Table 1. Summary descriptives in Women, Between the Different Programs",
                         col.names=c("Variables","General population", "Women Specific", "Sig."))%>%
  kableExtra::add_footnote(c("Note. Variables of C1 dataset had to be standardized before comparison;", "Continuous variables are presented as Medians and Percentiles 25 and 75 were shown;", "Categorical variables are presented as number (%)"), notation = "none")%>%
  kableExtra::scroll_box(width = "100%", height = "375px")
```

<br>

## Imputation

<br>

We generated a plot to see all the missing values in the sample.

<br>

```{r miss_plot_perc_var, warning=F,message=F,fig.align='center', fig.cap="Figure 3. Bar plot of Percentage of Missing Values per Variables at Basline", error=T, height=600}
#<div style="border: 1px solid #ddd; padding: 5px; overflow-y: scroll; height:400px; overflow-x: scroll; width:100%">
library(dplyr)
library(ggplot2)

vector_variables<-
c("tipo_de_programa_2", "estado_conyugal_2", "edad_al_ing_grupos", "escolaridad_rec", "sus_principal_mod", "freq_cons_sus_prin", "compromiso_biopsicosocial", "tenencia_de_la_vivienda_mod", "num_otras_sus_mod", "numero_de_hijos_mod_rec", "motivodeegreso_mod_imp","tipo_de_plan_res")

missing.values<-
CONS_C1_df_dup_SEP_2020_women %>%
  rowwise %>%
  dplyr::mutate_at(.vars = vars(vector_variables),
                   .funs = ~ifelse(is.na(.), 1, 0)) %>% 
  dplyr::ungroup() %>% 
  dplyr::summarise_at(vars(vector_variables),~sum(.))
#t(missing.values)

miss_val_bar<-
melt(missing.values) %>% 
    mutate(perc=scales::percent(value/nrow(CONS_C1_df_dup_SEP_2020_women))) %>% 
    arrange(desc(perc))

plot_miss<-
missing.values %>%
  data.table::melt() %>%  #condicion_ocupacional_corr
  dplyr::filter(!variable %in% c("row", "hash_key", "dias_treat_imp_sin_na", "dup")) %>% 
  dplyr::mutate(perc= value/sum(nrow(CONS_C1_df_dup_SEP_2020_women))) %>% 
  dplyr::mutate(label_text= paste0("Variable= ",variable,"<br>n= ",value,"<br>",scales::percent(round(perc,3)))) %>%
  dplyr::mutate(perc=perc*100) %>% 
  ggplot() +
  geom_bar(aes(x=factor(variable), y=perc,label= label_text), stat = 'identity') +
  sjPlot::theme_sjplot()+
#  scale_y_continuous(limits=c(0,1), labels=percent)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size=9))+
  labs(x=NULL, y="% of Missing Values", caption=paste0("Nota. Percentage of missing values (n= ",sum(nrow(CONS_C1_df_dup_SEP_2020_women)),")"))

  ggplotly(plot_miss, tooltip = c("label_text"))%>% layout(xaxis= list(showticklabels = T), height = 600, width=800) %>%   layout(yaxis = list(tickformat='%',  range = c(0, 5)))
  #</div>
```

<br>

<br>

<br>

<br>

<br>

From the figure above, we could see that the Tenure status of households (`tenencia_de_la_vivienda_mod`) and the Biopsychosocial Involvement (`compromiso_biopsicosocial`) had a proportion of missing values, but no greater than 5%. This is why we imputed these values under MAR assumption.

<br>

```{r mice1_miss_values_and_gen_imputations, error=F, fig.align='center', fig.cap="Figure 4. Bar plot of Porcentaje of Missing Values per Variables", message=FALSE, warning=FALSE, results='hide'}

vector_variables_only_for_imputation<-
c("row", "hash_key", "tipo_de_programa_2", "estado_conyugal_2", "edad_al_ing_grupos", "escolaridad_rec", "sus_principal_mod", "freq_cons_sus_prin", "compromiso_biopsicosocial", "tenencia_de_la_vivienda_mod", "num_otras_sus_mod", "numero_de_hijos_mod_rec","motivodeegreso_mod_imp","tipo_de_plan_res")

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

  #HACER BASE ESPECIAL QUE CONTENGA UNA VARIABLE DE EDAD DE INICIO DE CONSUMO DE SUSTANCIA PRINCIPAL PARA EQUIPARAR
CONS_C1_df_dup_SEP_2020_women_miss<-
CONS_C1_df_dup_SEP_2020_women %>% 
    #dplyr::group_by(hash_key) %>% 
    #dplyr::mutate(rn=row_number()) %>% 
    #dplyr::ungroup() %>% 
  
  #:#:#:#:#:#:#:#:#:#:#:
  # ORDINALIZAR LAS VARIABLES ORDINALES: 
  dplyr::select_(.dots = vector_variables_only_for_imputation) %>% 
    data.table::data.table()
  
#CONS_C1_df_dup_SEP_2020 %>% janitor::tabyl(evaluacindelprocesoteraputico) 
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

library(Amelia)

amelia_fit <- amelia(CONS_C1_df_dup_SEP_2020_women_miss, 
#Warning message:
#In amcheck(x = x, m = m, idvars = numopts$idvars, priors = priors,  : 
#The number of categories in one of the variables marked nominal has greater than 10 categories. Check nominal specification.
                     m=61, 
                     parallel = "multicore",
                     idvars="row",
                     noms= c("tipo_de_programa_2", "estado_conyugal_2", "sus_principal_mod", "tenencia_de_la_vivienda_mod", "numero_de_hijos_mod_rec","motivodeegreso_mod_imp", "tipo_de_plan_res"),
                     ords= c("edad_al_ing_grupos", "escolaridad_rec", "freq_cons_sus_prin", "compromiso_biopsicosocial", "num_otras_sus_mod"),
                     cs = "hash_key",
                     incheck = TRUE)
# Se sacó el servicio de salud porque tiene mucha información: The number of categories in one of the variables marked nominal has greater than 10 categories. Check nominal specification.

#Error in yy %*% unique(na.omit(x.orig[, i])) :  non-conformable arguments.
```

<br>

### Age at Admission to Treatment (in groups)

We started looking over the missing values in the age at admission (in groups) (n=`r missing.values %>% dplyr::select(edad_al_ing_grupos) %>% as.numeric()`). 

<br>

```{r mice1_age_at_admission_groups, warning=F,message=F, error=T, eval=T}
#On this graph, a y = x line indicates the line of perfect agreement; that is, if the imputation model was a perfect predictor of the true value, all the imputations would fall on this line
no_mostrar=0
if(no_mostrar==1){
  res <- { 
    setTimeLimit(nn_K*500)
    ovr_imp_edad_ini_cons<-overimpute(amelia_fit, var = "edad_al_ing_grupos")
  }
}

paste0("Users that had more than one treatment with no date of admission: ",CONS_C1_df_dup_SEP_2020_women_miss %>% 
    dplyr::group_by(hash_key) %>% 
    dplyr::mutate(na_edad_ing=sum(is.na(edad_al_ing_grupos))) %>% 
    dplyr::ungroup() %>% 
    dplyr::filter(na_edad_ing>0) %>% 
    dplyr::group_by(hash_key) %>% 
    dplyr::summarise(n=n()) %>% dplyr::filter(n>1) %>% nrow())

#Hay poca relación en las imputaciones.
#table(is.na(CONS_C1_df_dup_SEP_2020_women_not_miss$edad_al_ing),exclude=NULL)

edad_al_ing_grupos_imputed<-
  cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$edad_al_ing_grupos,
       amelia_fit$imputations$imp2$edad_al_ing_grupos,
       amelia_fit$imputations$imp3$edad_al_ing_grupos,
       amelia_fit$imputations$imp4$edad_al_ing_grupos,
       amelia_fit$imputations$imp5$edad_al_ing_grupos,
       amelia_fit$imputations$imp6$edad_al_ing_grupos,
       amelia_fit$imputations$imp7$edad_al_ing_grupos,
       amelia_fit$imputations$imp8$edad_al_ing_grupos,
       amelia_fit$imputations$imp9$edad_al_ing_grupos,
       amelia_fit$imputations$imp10$edad_al_ing_grupos,
       amelia_fit$imputations$imp11$edad_al_ing_grupos,
       amelia_fit$imputations$imp12$edad_al_ing_grupos,
       amelia_fit$imputations$imp13$edad_al_ing_grupos,
       amelia_fit$imputations$imp14$edad_al_ing_grupos,
       amelia_fit$imputations$imp15$edad_al_ing_grupos,
       amelia_fit$imputations$imp16$edad_al_ing_grupos,
       amelia_fit$imputations$imp17$edad_al_ing_grupos,
       amelia_fit$imputations$imp18$edad_al_ing_grupos,
       amelia_fit$imputations$imp19$edad_al_ing_grupos,
       amelia_fit$imputations$imp20$edad_al_ing_grupos,
       amelia_fit$imputations$imp21$edad_al_ing_grupos,
       amelia_fit$imputations$imp22$edad_al_ing_grupos,
       amelia_fit$imputations$imp23$edad_al_ing_grupos,
       amelia_fit$imputations$imp24$edad_al_ing_grupos,
       amelia_fit$imputations$imp25$edad_al_ing_grupos,
       amelia_fit$imputations$imp26$edad_al_ing_grupos,
       amelia_fit$imputations$imp27$edad_al_ing_grupos,
       amelia_fit$imputations$imp28$edad_al_ing_grupos,
       amelia_fit$imputations$imp29$edad_al_ing_grupos,
       amelia_fit$imputations$imp30$edad_al_ing_grupos,
       amelia_fit$imputations$imp31$edad_al_ing_grupos,
       amelia_fit$imputations$imp32$edad_al_ing_grupos,
       amelia_fit$imputations$imp33$edad_al_ing_grupos,
       amelia_fit$imputations$imp34$edad_al_ing_grupos,
       amelia_fit$imputations$imp35$edad_al_ing_grupos,
       amelia_fit$imputations$imp36$edad_al_ing_grupos,
       amelia_fit$imputations$imp37$edad_al_ing_grupos,
       amelia_fit$imputations$imp38$edad_al_ing_grupos,
       amelia_fit$imputations$imp39$edad_al_ing_grupos,
       amelia_fit$imputations$imp40$edad_al_ing_grupos,
       amelia_fit$imputations$imp41$edad_al_ing_grupos,
       amelia_fit$imputations$imp42$edad_al_ing_grupos,
       amelia_fit$imputations$imp43$edad_al_ing_grupos,
       amelia_fit$imputations$imp44$edad_al_ing_grupos,
       amelia_fit$imputations$imp45$edad_al_ing_grupos,
       amelia_fit$imputations$imp46$edad_al_ing_grupos,
       amelia_fit$imputations$imp47$edad_al_ing_grupos,
       amelia_fit$imputations$imp48$edad_al_ing_grupos,
       amelia_fit$imputations$imp49$edad_al_ing_grupos,
       amelia_fit$imputations$imp50$edad_al_ing_grupos,
       amelia_fit$imputations$imp51$edad_al_ing_grupos,
       amelia_fit$imputations$imp52$edad_al_ing_grupos,
       amelia_fit$imputations$imp53$edad_al_ing_grupos,
       amelia_fit$imputations$imp54$edad_al_ing_grupos,
       amelia_fit$imputations$imp55$edad_al_ing_grupos,
       amelia_fit$imputations$imp56$edad_al_ing_grupos,
       amelia_fit$imputations$imp57$edad_al_ing_grupos,
       amelia_fit$imputations$imp58$edad_al_ing_grupos,
       amelia_fit$imputations$imp59$edad_al_ing_grupos,
       amelia_fit$imputations$imp60$edad_al_ing_grupos,
       amelia_fit$imputations$imp61$edad_al_ing_grupos
        ) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  #18-29 30-39 40-49 50+
  janitor::clean_names() %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>%
  dplyr::summarise(edad_18_29=sum(value == "<18-29",na.rm=T),
                   edad_30_39=sum(value == "30-39",na.rm=T),
                   edad_40_49=sum(value == "40-49",na.rm=T),
                  edad_50mas=sum(value =="50+",na.rm=T)) %>% 
  dplyr::ungroup() %>% 
  #dplyr::mutate(edad_suma = base::rowSums(dplyr::select(is.na(.),starts_with("edad"))))
  dplyr::mutate(ties= base::rowSums(dplyr::select(.,starts_with("edad"))>0)) %>% 
  dplyr::mutate(edad_al_ing_grupos_imp= dplyr::case_when(
      (edad_18_29> edad_30_39) & (edad_18_29> edad_40_49) & (edad_18_29> edad_50mas)~"<18-29",
      (edad_30_39> edad_18_29) & (edad_30_39> edad_40_49) & (edad_30_39> edad_50mas)~"30-39",
      (edad_40_49> edad_18_29) & (edad_40_49> edad_30_39) & (edad_40_49> edad_50mas)~"40-49",
      (edad_50mas> edad_18_29) & (edad_50mas> edad_30_39) & (edad_50mas> edad_40_49)~"50+"
      )) 

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:
# Reemplazo los valores perdidos:
CONS_C1_df_dup_SEP_2020_women_miss0<-
CONS_C1_df_dup_SEP_2020_women_miss %>% 
  dplyr::left_join(edad_al_ing_grupos_imputed,by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
  #si la edad al ingreso no existe, el valor promedio imutado es
  dplyr::mutate(edad_al_ing_grupos=dplyr::case_when(is.na(edad_al_ing_grupos)~edad_al_ing_grupos_imp,
                                                    T~as.character(edad_al_ing_grupos))) %>% 
  dplyr::select(-edad_18_29, -edad_30_39, -edad_40_49, -edad_50mas, -ties, -edad_al_ing_grupos_imp)

if(nrow(CONS_C1_df_dup_SEP_2020_women_miss0)-nrow(CONS_C1_df_dup_SEP_2020_women_miss)>0){
  warning("AGS: Some rows were added in the imputation")}
```

<br>

`r ifelse(anyNA(CONS_C1_df_dup_SEP_2020_women_miss0$edad_al_ing_grupos),paste0("There are still ",CONS_C1_df_dup_SEP_2020_women_miss0%>% dplyr::filter(is.na(edad_al_ing_grupos)) %>% nrow()," missing cases."),"After the imputation, there were no missing cases left.")`

<br>

### Primary or main substance

Then we imputed the primary/main substance at admission (n= `r missing.values %>% dplyr::select(sus_principal_mod) %>% as.numeric() %>%  format(big.mark=",")`).

<br>

```{r mice2_main_subs,eval=T, echo=T, paged.print=TRUE}
# Ver distintos valores propuestos para sustancia de inciio
sus_principal_mod_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$sus_principal_mod,
       amelia_fit$imputations$imp2$sus_principal_mod,
       amelia_fit$imputations$imp3$sus_principal_mod,
       amelia_fit$imputations$imp4$sus_principal_mod,
       amelia_fit$imputations$imp5$sus_principal_mod,
       amelia_fit$imputations$imp6$sus_principal_mod,
       amelia_fit$imputations$imp7$sus_principal_mod,
       amelia_fit$imputations$imp8$sus_principal_mod,
       amelia_fit$imputations$imp9$sus_principal_mod,
       amelia_fit$imputations$imp10$sus_principal_mod,
       amelia_fit$imputations$imp11$sus_principal_mod,
       amelia_fit$imputations$imp12$sus_principal_mod,
       amelia_fit$imputations$imp13$sus_principal_mod,
       amelia_fit$imputations$imp14$sus_principal_mod,
       amelia_fit$imputations$imp15$sus_principal_mod,
       amelia_fit$imputations$imp16$sus_principal_mod,
       amelia_fit$imputations$imp17$sus_principal_mod,
       amelia_fit$imputations$imp18$sus_principal_mod,
       amelia_fit$imputations$imp19$sus_principal_mod,
       amelia_fit$imputations$imp20$sus_principal_mod,
       amelia_fit$imputations$imp21$sus_principal_mod,
       amelia_fit$imputations$imp22$sus_principal_mod,
       amelia_fit$imputations$imp23$sus_principal_mod,
       amelia_fit$imputations$imp24$sus_principal_mod,
       amelia_fit$imputations$imp25$sus_principal_mod,
       amelia_fit$imputations$imp26$sus_principal_mod,
       amelia_fit$imputations$imp27$sus_principal_mod,
       amelia_fit$imputations$imp28$sus_principal_mod,
       amelia_fit$imputations$imp29$sus_principal_mod,
       amelia_fit$imputations$imp30$sus_principal_mod,
       amelia_fit$imputations$imp31$sus_principal_mod,
       amelia_fit$imputations$imp32$sus_principal_mod,
       amelia_fit$imputations$imp33$sus_principal_mod,
       amelia_fit$imputations$imp34$sus_principal_mod,
       amelia_fit$imputations$imp35$sus_principal_mod,
       amelia_fit$imputations$imp36$sus_principal_mod,
       amelia_fit$imputations$imp37$sus_principal_mod,
       amelia_fit$imputations$imp38$sus_principal_mod,
       amelia_fit$imputations$imp39$sus_principal_mod,
       amelia_fit$imputations$imp40$sus_principal_mod,
       amelia_fit$imputations$imp41$sus_principal_mod,
       amelia_fit$imputations$imp42$sus_principal_mod,
       amelia_fit$imputations$imp43$sus_principal_mod,
       amelia_fit$imputations$imp44$sus_principal_mod,
       amelia_fit$imputations$imp45$sus_principal_mod,
       amelia_fit$imputations$imp46$sus_principal_mod,
       amelia_fit$imputations$imp47$sus_principal_mod,
       amelia_fit$imputations$imp48$sus_principal_mod,
       amelia_fit$imputations$imp49$sus_principal_mod,
       amelia_fit$imputations$imp50$sus_principal_mod,
       amelia_fit$imputations$imp51$sus_principal_mod,
       amelia_fit$imputations$imp52$sus_principal_mod,
       amelia_fit$imputations$imp53$sus_principal_mod,
       amelia_fit$imputations$imp54$sus_principal_mod,
       amelia_fit$imputations$imp55$sus_principal_mod,
       amelia_fit$imputations$imp56$sus_principal_mod,
       amelia_fit$imputations$imp57$sus_principal_mod,
       amelia_fit$imputations$imp58$sus_principal_mod,
       amelia_fit$imputations$imp59$sus_principal_mod,
       amelia_fit$imputations$imp60$sus_principal_mod,
       amelia_fit$imputations$imp61$sus_principal_mod
       )  %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  #18-29 30-39 40-49 50+
  janitor::clean_names() %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>%
  dplyr::summarise(sus_prin_mar=sum(value == "Marijuana",na.rm=T),
                   sus_prin_oh=sum(value == "Alcohol",na.rm=T),
                   sus_prin_pb=sum(value == "Cocaine paste",na.rm=T),
                  sus_prin_coc=sum(value =="Cocaine hydrochloride",na.rm=T),
                  sus_prin_other=sum(value =="Other",na.rm=T)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(ties= base::rowSums(dplyr::select(.,starts_with("sus_prin_"))>0)) %>% 
  dplyr::mutate(sus_principal_mod_imp= dplyr::case_when(
  (sus_prin_mar> sus_prin_oh)& (sus_prin_mar> sus_prin_pb)& (sus_prin_mar> sus_prin_coc)& (sus_prin_mar> sus_prin_other)~"Marijuana",
  (sus_prin_oh> sus_prin_mar)& (sus_prin_oh> sus_prin_pb)& (sus_prin_oh> sus_prin_coc)& (sus_prin_oh> sus_prin_other)~"Alcohol",
  (sus_prin_pb> sus_prin_mar)& (sus_prin_pb> sus_prin_oh)& (sus_prin_pb> sus_prin_coc)& (sus_prin_pb> sus_prin_other)~"Cocaine paste",
  (sus_prin_coc> sus_prin_mar)& (sus_prin_coc> sus_prin_oh)& (sus_prin_coc> sus_prin_pb)& (sus_prin_coc> sus_prin_other)~"Cocaine hydrochloride",
  (sus_prin_other> sus_prin_mar)& (sus_prin_other> sus_prin_oh)& (sus_prin_other> sus_prin_pb)& (sus_prin_other> sus_prin_coc)~"Cocaine hydrochloride"
  )) 

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:
CONS_C1_df_dup_SEP_2020_women_miss1<-
CONS_C1_df_dup_SEP_2020_women_miss0 %>% 
   dplyr::left_join(sus_principal_mod_imputed, by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(sus_principal_mod=factor(dplyr::case_when(is.na(sus_principal_mod)~as.character(sus_principal_mod_imp),
                                 TRUE~as.character(sus_principal_mod)))) %>% 
  dplyr::select(-c(sus_prin_mar, sus_prin_oh, sus_prin_pb, sus_prin_coc, sus_prin_other, ties, sus_principal_mod_imp)) %>% 
  data.table()
#_#_#_#_#_#_#__#_##_#_#_#_#_#_#_#_#_#_#_#_#__#_##_#_#_#_#_##_#_#_#_#_#_#__#_##_#_#_#_#_#_#_#_#_#_#_#_#__#_##_#_#_#_#_#
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss1)-nrow(CONS_C1_df_dup_SEP_2020_women_miss0)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss1 %>% dplyr::filter(is.na(sus_principal_mod)) %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss1 %>% dplyr::filter(is.na(sus_principal_mod)) %>% nrow(),")."))`

<br>

### Co-occurring SUD

Another variable worth imputing is the presence of additional Substance Use Disorders (n= `r missing.values %>% dplyr::select(num_otras_sus_mod) %>% as.numeric() %>%  format(big.mark=",")`).

<br>

```{r mice3_num_otras_sus_mod, warning=F,message=F,fig.align='center', fig.cap="Figure 7. Bar plot of Percentage of Incorrect Imputed Values per Imputation Sample", error=F, height=600}

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
num_otras_sus_mod_imputed<-
  cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$num_otras_sus_mod,
       amelia_fit$imputations$imp2$num_otras_sus_mod,
       amelia_fit$imputations$imp3$num_otras_sus_mod,
       amelia_fit$imputations$imp4$num_otras_sus_mod,
       amelia_fit$imputations$imp5$num_otras_sus_mod,
       amelia_fit$imputations$imp6$num_otras_sus_mod,
       amelia_fit$imputations$imp7$num_otras_sus_mod,
       amelia_fit$imputations$imp8$num_otras_sus_mod,
       amelia_fit$imputations$imp9$num_otras_sus_mod,
       amelia_fit$imputations$imp10$num_otras_sus_mod,
       amelia_fit$imputations$imp11$num_otras_sus_mod,
       amelia_fit$imputations$imp12$num_otras_sus_mod,
       amelia_fit$imputations$imp13$num_otras_sus_mod,
       amelia_fit$imputations$imp14$num_otras_sus_mod,
       amelia_fit$imputations$imp15$num_otras_sus_mod,
       amelia_fit$imputations$imp16$num_otras_sus_mod,
       amelia_fit$imputations$imp17$num_otras_sus_mod,
       amelia_fit$imputations$imp18$num_otras_sus_mod,
       amelia_fit$imputations$imp19$num_otras_sus_mod,
       amelia_fit$imputations$imp20$num_otras_sus_mod,
       amelia_fit$imputations$imp21$num_otras_sus_mod,
       amelia_fit$imputations$imp22$num_otras_sus_mod,
       amelia_fit$imputations$imp23$num_otras_sus_mod,
       amelia_fit$imputations$imp24$num_otras_sus_mod,
       amelia_fit$imputations$imp25$num_otras_sus_mod,
       amelia_fit$imputations$imp26$num_otras_sus_mod,
       amelia_fit$imputations$imp27$num_otras_sus_mod,
       amelia_fit$imputations$imp28$num_otras_sus_mod,
       amelia_fit$imputations$imp29$num_otras_sus_mod,
       amelia_fit$imputations$imp30$num_otras_sus_mod,
       amelia_fit$imputations$imp31$num_otras_sus_mod,
       amelia_fit$imputations$imp32$num_otras_sus_mod,
       amelia_fit$imputations$imp33$num_otras_sus_mod,
       amelia_fit$imputations$imp34$num_otras_sus_mod,
       amelia_fit$imputations$imp35$num_otras_sus_mod,
       amelia_fit$imputations$imp36$num_otras_sus_mod,
       amelia_fit$imputations$imp37$num_otras_sus_mod,
       amelia_fit$imputations$imp38$num_otras_sus_mod,
       amelia_fit$imputations$imp39$num_otras_sus_mod,
       amelia_fit$imputations$imp40$num_otras_sus_mod,
       amelia_fit$imputations$imp41$num_otras_sus_mod,
       amelia_fit$imputations$imp42$num_otras_sus_mod,
       amelia_fit$imputations$imp43$num_otras_sus_mod,
       amelia_fit$imputations$imp44$num_otras_sus_mod,
       amelia_fit$imputations$imp45$num_otras_sus_mod,
       amelia_fit$imputations$imp46$num_otras_sus_mod,
       amelia_fit$imputations$imp47$num_otras_sus_mod,
       amelia_fit$imputations$imp48$num_otras_sus_mod,
       amelia_fit$imputations$imp49$num_otras_sus_mod,
       amelia_fit$imputations$imp50$num_otras_sus_mod,
       amelia_fit$imputations$imp51$num_otras_sus_mod,
       amelia_fit$imputations$imp52$num_otras_sus_mod,
       amelia_fit$imputations$imp53$num_otras_sus_mod,
       amelia_fit$imputations$imp54$num_otras_sus_mod,
       amelia_fit$imputations$imp55$num_otras_sus_mod,
       amelia_fit$imputations$imp56$num_otras_sus_mod,
       amelia_fit$imputations$imp57$num_otras_sus_mod,
       amelia_fit$imputations$imp58$num_otras_sus_mod,
       amelia_fit$imputations$imp59$num_otras_sus_mod,
       amelia_fit$imputations$imp60$num_otras_sus_mod,
       amelia_fit$imputations$imp61$num_otras_sus_mod
       ) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>%
  dplyr::summarise(no_ad_subs=sum(value == "No additional substance",na.rm=T),
                   one_ad_subs=sum(value == "One additional substance",na.rm=T),
                   more_one_ad_subs=sum(value == "More than one additional substance",na.rm=T)) %>% 
  dplyr::ungroup() %>% 
# Hacer la variable imputada
  dplyr::mutate(num_otras_sus_mod_imp= dplyr::case_when(
      (no_ad_subs>one_ad_subs)&(no_ad_subs>more_one_ad_subs)~"No additional substance",
      (one_ad_subs>no_ad_subs)&(one_ad_subs>more_one_ad_subs)~"One additional substance",
      (more_one_ad_subs>no_ad_subs)&(more_one_ad_subs>one_ad_subs)~"More than one additional substance",
      T~NA_character_))

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

CONS_C1_df_dup_SEP_2020_women_miss2<-
  CONS_C1_df_dup_SEP_2020_women_miss1 %>% 
  dplyr::left_join(num_otras_sus_mod_imputed[,c("amelia_fit_imputations_imp1_row","num_otras_sus_mod_imp")],
                   by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
  #si la edad al ingreso no existe, el valor promedio imutado es
  dplyr::mutate(num_otras_sus_mod= 
                  dplyr::case_when(is.na(num_otras_sus_mod)~num_otras_sus_mod_imp,
                                  T~as.character(num_otras_sus_mod))) %>% 
  dplyr::select(-num_otras_sus_mod_imp)

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#is.na(edad_ini_cons) & is.na(edad_ini_sus_prin) & is.na(min_edad_al_ing)~as.numeric(avg),
#table(is.na(CONS_C1_df_dup_SEP_2020_women_miss1$edad_ini_cons))
paste0("Number of rows with values that did not fulfilled the conditions: ",CONS_C1_df_dup_SEP_2020_women_miss2 %>%  dplyr::filter(is.na(num_otras_sus_mod)) %>% 
    dplyr::select(hash_key, edad_al_ing_grupos,num_otras_sus_mod) %>% nrow())

#Lo importante es tener en cuenta que las imputaciones se hicieron por filas; no, en cambio, ahora debemos reemplazar aquellos casos que tienen perdidos (no cumplieron con las condiciones) con el valor mínimo
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss2)-nrow(CONS_C1_df_dup_SEP_2020_women_miss1)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, there were `r CONS_C1_df_dup_SEP_2020_women_miss2 %>% dplyr::filter(is.na(num_otras_sus_mod)) %>% nrow()` values of co-occurring SUDs available.

<br>

### Frequency of Use of the Primary Substance at Admission

Another variable that is worth imputing is the Frequency of use of primary drug at admission (n= `r CONS_C1_df_dup_SEP_2020_women_miss2 %>% dplyr::filter(is.na(freq_cons_sus_prin)) %>% nrow()`). In case of ties, we selected the imputed values with the value with the most frequent drug use. 

<br>

```{r mice4_frequency_drug_use,eval=T, echo=T, paged.print=TRUE}
# Ver distintos valores propuestos para sustancia de inciio
freq_cons_sus_prin_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$freq_cons_sus_prin,
       amelia_fit$imputations$imp2$freq_cons_sus_prin,
       amelia_fit$imputations$imp3$freq_cons_sus_prin,
       amelia_fit$imputations$imp4$freq_cons_sus_prin,
       amelia_fit$imputations$imp5$freq_cons_sus_prin,
       amelia_fit$imputations$imp6$freq_cons_sus_prin,
       amelia_fit$imputations$imp7$freq_cons_sus_prin,
       amelia_fit$imputations$imp8$freq_cons_sus_prin,
       amelia_fit$imputations$imp9$freq_cons_sus_prin,
       amelia_fit$imputations$imp10$freq_cons_sus_prin,
       amelia_fit$imputations$imp11$freq_cons_sus_prin,
       amelia_fit$imputations$imp12$freq_cons_sus_prin,
       amelia_fit$imputations$imp13$freq_cons_sus_prin,
       amelia_fit$imputations$imp14$freq_cons_sus_prin,
       amelia_fit$imputations$imp15$freq_cons_sus_prin,
       amelia_fit$imputations$imp16$freq_cons_sus_prin,
       amelia_fit$imputations$imp17$freq_cons_sus_prin,
       amelia_fit$imputations$imp18$freq_cons_sus_prin,
       amelia_fit$imputations$imp19$freq_cons_sus_prin,
       amelia_fit$imputations$imp20$freq_cons_sus_prin,
       amelia_fit$imputations$imp21$freq_cons_sus_prin,
       amelia_fit$imputations$imp22$freq_cons_sus_prin,
       amelia_fit$imputations$imp23$freq_cons_sus_prin,
       amelia_fit$imputations$imp24$freq_cons_sus_prin,
       amelia_fit$imputations$imp25$freq_cons_sus_prin,
       amelia_fit$imputations$imp26$freq_cons_sus_prin,
       amelia_fit$imputations$imp27$freq_cons_sus_prin,
       amelia_fit$imputations$imp28$freq_cons_sus_prin,
       amelia_fit$imputations$imp29$freq_cons_sus_prin,
       amelia_fit$imputations$imp30$freq_cons_sus_prin,
       amelia_fit$imputations$imp31$freq_cons_sus_prin,
       amelia_fit$imputations$imp32$freq_cons_sus_prin,
       amelia_fit$imputations$imp33$freq_cons_sus_prin,
       amelia_fit$imputations$imp34$freq_cons_sus_prin,
       amelia_fit$imputations$imp35$freq_cons_sus_prin,
       amelia_fit$imputations$imp36$freq_cons_sus_prin,
       amelia_fit$imputations$imp37$freq_cons_sus_prin,
       amelia_fit$imputations$imp38$freq_cons_sus_prin,
       amelia_fit$imputations$imp39$freq_cons_sus_prin,
       amelia_fit$imputations$imp40$freq_cons_sus_prin,
       amelia_fit$imputations$imp41$freq_cons_sus_prin,
       amelia_fit$imputations$imp42$freq_cons_sus_prin,
       amelia_fit$imputations$imp43$freq_cons_sus_prin,
       amelia_fit$imputations$imp44$freq_cons_sus_prin,
       amelia_fit$imputations$imp45$freq_cons_sus_prin,
       amelia_fit$imputations$imp46$freq_cons_sus_prin,
       amelia_fit$imputations$imp47$freq_cons_sus_prin,
       amelia_fit$imputations$imp48$freq_cons_sus_prin,
       amelia_fit$imputations$imp49$freq_cons_sus_prin,
       amelia_fit$imputations$imp50$freq_cons_sus_prin,
       amelia_fit$imputations$imp51$freq_cons_sus_prin,
       amelia_fit$imputations$imp52$freq_cons_sus_prin,
       amelia_fit$imputations$imp53$freq_cons_sus_prin,
       amelia_fit$imputations$imp54$freq_cons_sus_prin,
       amelia_fit$imputations$imp55$freq_cons_sus_prin,
       amelia_fit$imputations$imp56$freq_cons_sus_prin,
       amelia_fit$imputations$imp57$freq_cons_sus_prin,
       amelia_fit$imputations$imp58$freq_cons_sus_prin,
       amelia_fit$imputations$imp59$freq_cons_sus_prin,
       amelia_fit$imputations$imp60$freq_cons_sus_prin,
       amelia_fit$imputations$imp61$freq_cons_sus_prin
       ) 

freq_cons_sus_prin_imputed<-
freq_cons_sus_prin_imputed %>% 
  data.frame() %>% 
dplyr::mutate(across(c(amelia_fit.imputations.imp1.freq_cons_sus_prin:amelia_fit.imputations.imp30.freq_cons_sus_prin),~dplyr::case_when(grepl("1 day a week or more",as.character(.))~1,TRUE~0), .names="1_day_{col}"))%>%
dplyr::mutate(across(c(amelia_fit.imputations.imp1.freq_cons_sus_prin:amelia_fit.imputations.imp30.freq_cons_sus_prin),~dplyr::case_when(grepl("2 to 3 days a week",as.character(.))~1,TRUE~0), .names="2_3_{col}"))%>%
dplyr::mutate(across(c(amelia_fit.imputations.imp1.freq_cons_sus_prin:amelia_fit.imputations.imp30.freq_cons_sus_prin),~dplyr::case_when(grepl("4 to 6 days a week",as.character(.))~1,TRUE~0), .names="4_6_{col}"))%>%
  dplyr::mutate(across(c(amelia_fit.imputations.imp1.freq_cons_sus_prin:amelia_fit.imputations.imp30.freq_cons_sus_prin),~dplyr::case_when(grepl("Less than 1 day a week",as.character(.))~1,TRUE~0), .names="less_1_{col}"))%>%
  dplyr::mutate(across(c(amelia_fit.imputations.imp1.freq_cons_sus_prin:amelia_fit.imputations.imp30.freq_cons_sus_prin),~dplyr::case_when(grepl("Did not use",as.character(.))~1,TRUE~0), .names="did_not_{col}"))%>%
    dplyr::mutate(across(c(amelia_fit.imputations.imp1.freq_cons_sus_prin:amelia_fit.imputations.imp30.freq_cons_sus_prin),~dplyr::case_when(grepl("Daily",as.character(.))~1,TRUE~0), .names="daily_{col}"))%>%
  dplyr::mutate(freq_cons_sus_prin_daily = base::rowSums(dplyr::select(., starts_with("daily_")))) %>% 
  dplyr::mutate(freq_cons_sus_prin_4_6 = base::rowSums(dplyr::select(., starts_with("4_6_"))))%>%
  dplyr::mutate(freq_cons_sus_prin_2_3 = base::rowSums(dplyr::select(., starts_with("2_3_"))))%>%
  dplyr::mutate(freq_cons_sus_prin_1_day = base::rowSums(dplyr::select(., starts_with("1_day_"))))%>%
  dplyr::mutate(freq_cons_sus_prin_less_1 = base::rowSums(dplyr::select(., starts_with("less_1_"))))%>%
  dplyr::mutate(freq_cons_sus_prin_did_not = base::rowSums(dplyr::select(., starts_with("did_not_")))) %>% 
  #dplyr::summarise(min_mar=max(sus_ini_mod_mvv_mar[sus_ini_mod_mvv_mar<30]),min_oh=max(sus_ini_mod_mvv_oh[sus_ini_mod_mvv_oh<30]),min_pb=max(sus_ini_mod_mvv_pb[sus_ini_mod_mvv_pb<30]),min_coc=max(sus_ini_mod_mvv_coc[sus_ini_mod_mvv_coc<30]),min_otr=max(sus_ini_mod_mvv_otr[sus_ini_mod_mvv_otr<30]))
  dplyr::mutate(freq_cons_sus_prin_tot=dplyr::case_when(freq_cons_sus_prin_1_day>0~1,TRUE~0)) %>% 
  dplyr::mutate(freq_cons_sus_prin_tot=dplyr::case_when(freq_cons_sus_prin_2_3>0~freq_cons_sus_prin_tot+1,TRUE~freq_cons_sus_prin_tot)) %>% 
  dplyr::mutate(freq_cons_sus_prin_tot=dplyr::case_when(freq_cons_sus_prin_4_6>0~freq_cons_sus_prin_tot+1,TRUE~freq_cons_sus_prin_tot)) %>% 
  dplyr::mutate(freq_cons_sus_prin_tot=dplyr::case_when(freq_cons_sus_prin_less_1>0~freq_cons_sus_prin_tot+1,TRUE~freq_cons_sus_prin_tot)) %>% 
  dplyr::mutate(freq_cons_sus_prin_tot=dplyr::case_when(freq_cons_sus_prin_did_not>0~freq_cons_sus_prin_tot+1,TRUE~freq_cons_sus_prin_tot)) %>% 
  dplyr::mutate(freq_cons_sus_prin_tot=dplyr::case_when(freq_cons_sus_prin_daily>0~freq_cons_sus_prin_tot+1,TRUE~freq_cons_sus_prin_tot)) %>% 
  #hierarchy
  dplyr::mutate(freq_cons_sus_prin_to_imputation=
                  dplyr::case_when(freq_cons_sus_prin_tot==1 & freq_cons_sus_prin_daily>0~"Daily",
                                     freq_cons_sus_prin_tot==1 & freq_cons_sus_prin_4_6>0~"4 to 6 days a week",freq_cons_sus_prin_tot==1 & freq_cons_sus_prin_2_3>0~"2 to 3 days a week",freq_cons_sus_prin_tot==1 & freq_cons_sus_prin_1_day>0~"1 day a week or more",freq_cons_sus_prin_tot==1 & freq_cons_sus_prin_less_1>0~"Less than 1 day a week",freq_cons_sus_prin_tot==1 & freq_cons_sus_prin_did_not>0~"Did not use",freq_cons_sus_prin_tot>1 & freq_cons_sus_prin_daily>0~"Daily",freq_cons_sus_prin_tot>1 & freq_cons_sus_prin_4_6>0~"4 to 6 days a week",freq_cons_sus_prin_tot>1 & freq_cons_sus_prin_2_3>0~"2 to 3 days a week",freq_cons_sus_prin_tot>1 & freq_cons_sus_prin_1_day>0~"1 day a week or more",freq_cons_sus_prin_tot>1 & freq_cons_sus_prin_less_1>0~"Less than 1 day a week",freq_cons_sus_prin_tot>1 & freq_cons_sus_prin_did_not>0~"Did not use")) %>% 
  janitor::clean_names()

freq_cons_sus_prin_imputed<-
dplyr::select(freq_cons_sus_prin_imputed,amelia_fit_imputations_imp1_row,freq_cons_sus_prin_to_imputation)

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:

CONS_C1_df_dup_SEP_2020_women_miss3<-
CONS_C1_df_dup_SEP_2020_women_miss2 %>% 
   dplyr::left_join(freq_cons_sus_prin_imputed, by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(freq_cons_sus_prin=factor(dplyr::case_when(is.na(freq_cons_sus_prin)~as.character(freq_cons_sus_prin_to_imputation), TRUE~as.character(freq_cons_sus_prin)))) %>% 
  dplyr::select(-freq_cons_sus_prin_to_imputation) %>% 
  data.table()
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss3)-nrow(CONS_C1_df_dup_SEP_2020_women_miss2)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss3 %>% dplyr::filter(is.na(freq_cons_sus_prin)) %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss3 %>% dplyr::filter(is.na(freq_cons_sus_prin)) %>% nrow(),")."))`

<br>

### Educational Attainment

Another variable that is worth imputing is the Educational Attainment (n= `r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(escolaridad_rec)) %>% nrow()`). In case of ties,w imputed for the most vulnerable category among the candidates.

<br>

```{r mice5_educational_att,eval=T, echo=T, paged.print=TRUE}
# Ver distintos valores propuestos para sustancia de inciio
escolaridad_rec_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
                  amelia_fit$imputations$imp1$escolaridad_rec,
                  amelia_fit$imputations$imp2$escolaridad_rec,
                  amelia_fit$imputations$imp3$escolaridad_rec,
                  amelia_fit$imputations$imp4$escolaridad_rec,
                  amelia_fit$imputations$imp5$escolaridad_rec,
                  amelia_fit$imputations$imp6$escolaridad_rec,
                  amelia_fit$imputations$imp7$escolaridad_rec,
                  amelia_fit$imputations$imp8$escolaridad_rec,
                  amelia_fit$imputations$imp9$escolaridad_rec,
                  amelia_fit$imputations$imp10$escolaridad_rec,
                  amelia_fit$imputations$imp11$escolaridad_rec,
                  amelia_fit$imputations$imp12$escolaridad_rec,
                  amelia_fit$imputations$imp13$escolaridad_rec,
                  amelia_fit$imputations$imp14$escolaridad_rec,
                  amelia_fit$imputations$imp15$escolaridad_rec,
                  amelia_fit$imputations$imp16$escolaridad_rec,
                  amelia_fit$imputations$imp17$escolaridad_rec,
                  amelia_fit$imputations$imp18$escolaridad_rec,
                  amelia_fit$imputations$imp19$escolaridad_rec,
                  amelia_fit$imputations$imp20$escolaridad_rec,
                  amelia_fit$imputations$imp21$escolaridad_rec,
                  amelia_fit$imputations$imp22$escolaridad_rec,
                  amelia_fit$imputations$imp23$escolaridad_rec,
                  amelia_fit$imputations$imp24$escolaridad_rec,
                  amelia_fit$imputations$imp25$escolaridad_rec,
                  amelia_fit$imputations$imp26$escolaridad_rec,
                  amelia_fit$imputations$imp27$escolaridad_rec,
                  amelia_fit$imputations$imp28$escolaridad_rec,
                  amelia_fit$imputations$imp29$escolaridad_rec,
                  amelia_fit$imputations$imp30$escolaridad_rec,
                  amelia_fit$imputations$imp31$escolaridad_rec,
                  amelia_fit$imputations$imp32$escolaridad_rec,
                  amelia_fit$imputations$imp33$escolaridad_rec,
                  amelia_fit$imputations$imp34$escolaridad_rec,
                  amelia_fit$imputations$imp35$escolaridad_rec,
                  amelia_fit$imputations$imp36$escolaridad_rec,
                  amelia_fit$imputations$imp37$escolaridad_rec,
                  amelia_fit$imputations$imp38$escolaridad_rec,
                  amelia_fit$imputations$imp39$escolaridad_rec,
                  amelia_fit$imputations$imp40$escolaridad_rec,
                  amelia_fit$imputations$imp41$escolaridad_rec,
                  amelia_fit$imputations$imp42$escolaridad_rec,
                  amelia_fit$imputations$imp43$escolaridad_rec,
                  amelia_fit$imputations$imp44$escolaridad_rec,
                  amelia_fit$imputations$imp45$escolaridad_rec,
                  amelia_fit$imputations$imp46$escolaridad_rec,
                  amelia_fit$imputations$imp47$escolaridad_rec,
                  amelia_fit$imputations$imp48$escolaridad_rec,
                  amelia_fit$imputations$imp49$escolaridad_rec,
                  amelia_fit$imputations$imp50$escolaridad_rec,
                  amelia_fit$imputations$imp51$escolaridad_rec,
                  amelia_fit$imputations$imp52$escolaridad_rec,
                  amelia_fit$imputations$imp53$escolaridad_rec,
                  amelia_fit$imputations$imp54$escolaridad_rec,
                  amelia_fit$imputations$imp55$escolaridad_rec,
                  amelia_fit$imputations$imp56$escolaridad_rec,
                  amelia_fit$imputations$imp57$escolaridad_rec,
                  amelia_fit$imputations$imp58$escolaridad_rec,
                  amelia_fit$imputations$imp59$escolaridad_rec,
                  amelia_fit$imputations$imp60$escolaridad_rec) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>%
  # 1-Mild 2-Moderate   3-Severe 
  dplyr::summarise(primary_3=sum(value == "3-Completed primary school or less",na.rm=T),
                   high_sc_2=sum(value == "2-Completed high school or less",na.rm=T),
                  more_h_sc_1=sum(value =="1-More than high school",na.rm=T)) %>% 
  dplyr::ungroup() %>%
    dplyr::mutate(escolaridad_rec_imp= dplyr::case_when(
      (more_h_sc_1>primary_3) & (more_h_sc_1>high_sc_2)~"1-More than high school",
      (high_sc_2>primary_3) & (high_sc_2>more_h_sc_1)~"2-Completed high school or less",
      (primary_3>more_h_sc_1) & (primary_3>high_sc_2)~"3-Completed primary school or less"
      )) %>% 
#2) Resolve ties    
  dplyr::mutate(ties= dplyr::case_when(is.na(escolaridad_rec_imp)~1,T~0)) %>% 
  dplyr::mutate(escolaridad_rec_imp= dplyr::case_when(ties==1 & ((primary_3>more_h_sc_1)|(primary_3>high_sc_2))~"3-Completed primary school or less", ties==1 & ((high_sc_2>primary_3)|(high_sc_2>more_h_sc_1))~"2-Completed high school or less",
                T~escolaridad_rec_imp))

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:
#CONS_C1_df_dup_SEP_2020 %>% janitor::tabyl(motivodeegreso_mod_imp,evaluacindelprocesoteraputico)

CONS_C1_df_dup_SEP_2020_women_miss4<-
CONS_C1_df_dup_SEP_2020_women_miss3 %>% 
   dplyr::left_join(escolaridad_rec_imputed[,c("amelia_fit_imputations_imp1_row","escolaridad_rec_imp")], by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(escolaridad_rec=factor(dplyr::case_when(is.na(escolaridad_rec)~ escolaridad_rec_imp,
                                                                        TRUE~as.character(escolaridad_rec)))) %>% 
     dplyr::mutate(escolaridad_rec=parse_factor(as.character(escolaridad_rec),levels=c("1-More than high school", "2-Completed high school or less","3-Completed primary school or less"), ordered =T,trim_ws=T,include_na =F, locale=locale(encoding = "UTF-8"))) %>% 
  dplyr::select(-escolaridad_rec_imp) %>% 
  data.table()
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss4)-nrow(CONS_C1_df_dup_SEP_2020_women_miss3)>0){
  warning("AGS: Some rows were added in the imputation")}
```

<br>

We ended having `r CONS_C1_df_dup_SEP_2020_women_miss4 %>%  dplyr::filter(is.na(escolaridad_rec)) %>%  nrow()` missing values in educational attainment.

<br>

### Marital status

Additionally, we replaced missing values of the marital status (n=`r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(estado_conyugal_2)) %>% nrow()`). Since different marital status were not clearly more vulnerable between each other, we selected the most frequent imputed value among the different imputed databases. Only in case of ties in the candidate values, we resolved them by discarding "married" status, which could be somehow less vulnerable than other categories.

<br>

```{r mice5_marital_status,eval=T, echo=T, paged.print=TRUE}
# Ver distintos valores propuestos para estado conyugal
estado_conyugal_2_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$estado_conyugal_2,
       amelia_fit$imputations$imp2$estado_conyugal_2,
       amelia_fit$imputations$imp3$estado_conyugal_2,
       amelia_fit$imputations$imp4$estado_conyugal_2,
       amelia_fit$imputations$imp5$estado_conyugal_2,
       amelia_fit$imputations$imp6$estado_conyugal_2,
       amelia_fit$imputations$imp7$estado_conyugal_2,
       amelia_fit$imputations$imp8$estado_conyugal_2,
       amelia_fit$imputations$imp9$estado_conyugal_2,
       amelia_fit$imputations$imp10$estado_conyugal_2,
       amelia_fit$imputations$imp11$estado_conyugal_2,
       amelia_fit$imputations$imp12$estado_conyugal_2,
       amelia_fit$imputations$imp13$estado_conyugal_2,
       amelia_fit$imputations$imp14$estado_conyugal_2,
       amelia_fit$imputations$imp15$estado_conyugal_2,
       amelia_fit$imputations$imp16$estado_conyugal_2,
       amelia_fit$imputations$imp17$estado_conyugal_2,
       amelia_fit$imputations$imp18$estado_conyugal_2,
       amelia_fit$imputations$imp19$estado_conyugal_2,
       amelia_fit$imputations$imp20$estado_conyugal_2,
       amelia_fit$imputations$imp21$estado_conyugal_2,
       amelia_fit$imputations$imp22$estado_conyugal_2,
       amelia_fit$imputations$imp23$estado_conyugal_2,
       amelia_fit$imputations$imp24$estado_conyugal_2,
       amelia_fit$imputations$imp25$estado_conyugal_2,
       amelia_fit$imputations$imp26$estado_conyugal_2,
       amelia_fit$imputations$imp27$estado_conyugal_2,
       amelia_fit$imputations$imp28$estado_conyugal_2,
       amelia_fit$imputations$imp29$estado_conyugal_2,
       amelia_fit$imputations$imp30$estado_conyugal_2,
       amelia_fit$imputations$imp31$estado_conyugal_2,
       amelia_fit$imputations$imp32$estado_conyugal_2,
       amelia_fit$imputations$imp33$estado_conyugal_2,
       amelia_fit$imputations$imp34$estado_conyugal_2,
       amelia_fit$imputations$imp35$estado_conyugal_2,
       amelia_fit$imputations$imp36$estado_conyugal_2,
       amelia_fit$imputations$imp37$estado_conyugal_2,
       amelia_fit$imputations$imp38$estado_conyugal_2,
       amelia_fit$imputations$imp39$estado_conyugal_2,
       amelia_fit$imputations$imp40$estado_conyugal_2,
       amelia_fit$imputations$imp41$estado_conyugal_2,
       amelia_fit$imputations$imp42$estado_conyugal_2,
       amelia_fit$imputations$imp43$estado_conyugal_2,
       amelia_fit$imputations$imp44$estado_conyugal_2,
       amelia_fit$imputations$imp45$estado_conyugal_2,
       amelia_fit$imputations$imp46$estado_conyugal_2,
       amelia_fit$imputations$imp47$estado_conyugal_2,
       amelia_fit$imputations$imp48$estado_conyugal_2,
       amelia_fit$imputations$imp49$estado_conyugal_2,
       amelia_fit$imputations$imp50$estado_conyugal_2,
       amelia_fit$imputations$imp51$estado_conyugal_2,
       amelia_fit$imputations$imp52$estado_conyugal_2,
       amelia_fit$imputations$imp53$estado_conyugal_2,
       amelia_fit$imputations$imp54$estado_conyugal_2,
       amelia_fit$imputations$imp55$estado_conyugal_2,
       amelia_fit$imputations$imp56$estado_conyugal_2,
       amelia_fit$imputations$imp57$estado_conyugal_2,
       amelia_fit$imputations$imp58$estado_conyugal_2,
       amelia_fit$imputations$imp59$estado_conyugal_2,
       amelia_fit$imputations$imp60$estado_conyugal_2,
       amelia_fit$imputations$imp61$estado_conyugal_2
       ) 

estado_conyugal_2_imputed<-
estado_conyugal_2_imputed %>% 
  data.frame() %>% 
dplyr::mutate(across(c(amelia_fit.imputations.imp1.estado_conyugal_2:amelia_fit.imputations.imp30.estado_conyugal_2),~dplyr::case_when(grepl("Married/Shared living arrangements",as.character(.))~1,TRUE~0), .names="married_{col}"))%>%
dplyr::mutate(across(c(amelia_fit.imputations.imp1.estado_conyugal_2:amelia_fit.imputations.imp30.estado_conyugal_2),~dplyr::case_when(grepl("Separated/Divorced",as.character(.))~1,TRUE~0), .names="sep_div_{col}"))%>%
dplyr::mutate(across(c(amelia_fit.imputations.imp1.estado_conyugal_2:amelia_fit.imputations.imp30.estado_conyugal_2),~dplyr::case_when(grepl("Single",as.character(.))~1,TRUE~0), .names="singl_{col}"))%>%
  dplyr::mutate(across(c(amelia_fit.imputations.imp1.estado_conyugal_2:amelia_fit.imputations.imp30.estado_conyugal_2),~dplyr::case_when(grepl("Widower",as.character(.))~1,TRUE~0), .names="widow_{col}"))%>%
 
  dplyr::mutate(estado_conyugal_2_married = base::rowSums(dplyr::select(., starts_with("married_"))))%>%
  dplyr::mutate(estado_conyugal_2_sep_div = base::rowSums(dplyr::select(., starts_with("sep_div_"))))%>%
  dplyr::mutate(estado_conyugal_2_singl = base::rowSums(dplyr::select(., starts_with("singl_"))))%>%
  dplyr::mutate(estado_conyugal_2_wid = base::rowSums(dplyr::select(., starts_with("widow_"))))%>%
  #dplyr::summarise(min_mar=max(sus_ini_mod_mvv_mar[sus_ini_mod_mvv_mar<30]),min_oh=max(sus_ini_mod_mvv_oh[sus_ini_mod_mvv_oh<30]),min_pb=max(sus_ini_mod_mvv_pb[sus_ini_mod_mvv_pb<30]),min_coc=max(sus_ini_mod_mvv_coc[sus_ini_mod_mvv_coc<30]),min_otr=max(sus_ini_mod_mvv_otr[sus_ini_mod_mvv_otr<30]))
  dplyr::mutate(estado_conyugal_2_tot=dplyr::case_when(estado_conyugal_2_married>0~1,TRUE~0)) %>% 
  dplyr::mutate(estado_conyugal_2_tot=dplyr::case_when(estado_conyugal_2_sep_div>0~estado_conyugal_2_tot+1,TRUE~estado_conyugal_2_tot)) %>% 
  dplyr::mutate(estado_conyugal_2_tot=dplyr::case_when(estado_conyugal_2_singl>0~estado_conyugal_2_tot+1,TRUE~estado_conyugal_2_tot)) %>% 
  dplyr::mutate(estado_conyugal_2_tot=dplyr::case_when(estado_conyugal_2_wid>0~estado_conyugal_2_tot+1,TRUE~estado_conyugal_2_tot)) %>% 
  janitor::clean_names()
  
estado_conyugal_2_imputed_cat_est_cony<-  
    estado_conyugal_2_imputed %>%
        tidyr::pivot_longer(c(estado_conyugal_2_married, estado_conyugal_2_sep_div, estado_conyugal_2_singl, estado_conyugal_2_wid), names_to = "cat_est_conyugal", values_to = "count") %>%
        dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
        dplyr::mutate(estado_conyugal_2_imputed_max=max(count,na.rm=T)) %>% 
        dplyr::ungroup() %>% 
        dplyr::filter(estado_conyugal_2_imputed_max==count) %>% 
        dplyr::select(amelia_fit_imputations_imp1_row,cat_est_conyugal,count) %>% 
        dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
        dplyr::mutate(n_row=n()) %>% 
        dplyr::ungroup() %>% 
        dplyr::mutate(cat_est_conyugal=dplyr::case_when(n_row>1~NA_character_,
                                                        TRUE~cat_est_conyugal)) %>% 
        dplyr::distinct(amelia_fit_imputations_imp1_row,.keep_all = T)
  
estado_conyugal_2_imputed<-
  estado_conyugal_2_imputed %>% 
    dplyr::left_join(estado_conyugal_2_imputed_cat_est_cony, by="amelia_fit_imputations_imp1_row") %>%
    dplyr::mutate(cat_est_conyugal=dplyr::case_when(cat_est_conyugal=="estado_conyugal_2_married"~"Married/Shared living arrangements",cat_est_conyugal=="estado_conyugal_2_sep_div"~"Separated/Divorced",cat_est_conyugal=="estado_conyugal_2_singl"~"Single",cat_est_conyugal=="estado_conyugal_2_wid"~"Widower"
    ))%>% 
  janitor::clean_names()

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:

CONS_C1_df_dup_SEP_2020_women_miss5_prev<-
CONS_C1_df_dup_SEP_2020_women_miss4 %>% 
   dplyr::left_join(dplyr::select(estado_conyugal_2_imputed,amelia_fit_imputations_imp1_row,cat_est_conyugal), by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(estado_conyugal_2=factor(dplyr::case_when(is.na(estado_conyugal_2)~as.character(cat_est_conyugal),TRUE~as.character(estado_conyugal_2)))) %>% 
  dplyr::select(-cat_est_conyugal) %>% 
  data.table()

# casos problemáticos de matrimonio c(59664, 17582, 161721, 36520)

no_calzaron_estado_cony<-
CONS_C1_df_dup_SEP_2020_women_miss5_prev %>% dplyr::filter(is.na(estado_conyugal_2)) %>% dplyr::distinct(row) %>% unlist()

estado_conyugal_2_imputed2<-
estado_conyugal_2_imputed %>% 
     dplyr::filter(amelia_fit_imputations_imp1_row %in%  no_calzaron_estado_cony) %>% 
  dplyr::select(amelia_fit_imputations_imp1_row, estado_conyugal_2_married, estado_conyugal_2_sep_div,estado_conyugal_2_singl, estado_conyugal_2_wid, estado_conyugal_2_tot, cat_est_conyugal) %>% 
  melt(id.vars="amelia_fit_imputations_imp1_row") %>% 
  dplyr::mutate(value=as.numeric(value)) %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::filter(value!="cat_est_conyugal") %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  slice_max(value, with_ties = T) %>% 
  dplyr::filter(variable!="estado_conyugal_2_married") %>% 
  dplyr::left_join(CONS_C1_df_dup_SEP_2020_women[,c("row","edad_al_ing")], by=c("amelia_fit_imputations_imp1_row"="row")) %>% 
  dplyr::mutate(value=dplyr::case_when(variable=="estado_conyugal_2_sep_div"~value*10,
                                       T~value)) %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  slice_max(value, with_ties = T) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(marital_status_imp=dplyr::case_when(grepl("_singl",variable)~"Single",
                grepl("_sep_div",variable)~"Separated/Divorced",
                grepl("_married",variable)~"Married/Shared living arrangements",
                grepl("_wid",variable)~"Widower"
                ))

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#2nd round of imputation for ties
CONS_C1_df_dup_SEP_2020_women_miss5<-
CONS_C1_df_dup_SEP_2020_women_miss5_prev %>% 
   dplyr::left_join(dplyr::select(estado_conyugal_2_imputed2,amelia_fit_imputations_imp1_row,marital_status_imp), by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(estado_conyugal_2=factor(dplyr::case_when(is.na(estado_conyugal_2)~as.character(marital_status_imp),TRUE~as.character(estado_conyugal_2)))) %>% 
  dplyr::select(-marital_status_imp) %>% 
  data.table()

#CONS_C1_df_dup_SEP_2020_women_miss5 %>% 
#dplyr::filter(hash_key %in% CONS_C1_df_dup_SEP_2020_women_miss5 %>% dplyr::filter(is.na(estado_conyugal_2)) %>% dplyr::distinct(hash_key) %>% unlist())

if(nrow(CONS_C1_df_dup_SEP_2020_women_miss5)-nrow(CONS_C1_df_dup_SEP_2020_women_miss4)>0){
  warning("AGS: Some rows were added in the imputation")}
```

<br>

We could not resolve Marital status in  `r CONS_C1_df_dup_SEP_2020_women_miss5 %>% dplyr::filter(is.na(estado_conyugal_2)) %>% nrow()` cases due to ties in the most frequent values. 

<br>

### Cause of Discharge

We looked over possible imputations to the truly missing values, discarding missing values due to censorship (n=`r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(motivodeegreso_mod_imp)) %>% dplyr::left_join(dplyr::select(CONS_C1_df_dup_SEP_2020,row,fech_egres_imp),by="row") %>% dplyr::filter(!is.na(fech_egres_imp))%>%  nrow()`). In case of ties, we replace with the more vulnerable value.
<!--- son casos que no tienen motivo de egreso, pero sí finalizó su tratamiento. Aunque no en el caso de todes. Ver change_dates_out_of_study.R--->
<br>

```{r mice9_caus_disch,eval=T, echo=T, paged.print=TRUE}
motivo_de_egreso_a_imputar<-
CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(motivodeegreso_mod_imp)) %>% dplyr::left_join(dplyr::select(CONS_C1_df_dup_SEP_2020,row,fech_egres_imp)) %>% dplyr::filter(!is.na(fech_egres_imp))%>%dplyr::select(row)

#CONS_C1_df_dup_SEP_2020 %>% dplyr::filter(is.na(motivodeegreso_mod_imp)) %>% 
#    dplyr::select(row, hash_key, motivodeegreso_mod_imp, fech_egres_imp)
#    dplyr::filter(fech_egres_imp=="2019-11-13")

motivodeegreso_mod_imp_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp2$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp3$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp4$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp5$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp6$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp7$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp8$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp9$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp10$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp11$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp12$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp13$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp14$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp15$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp16$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp17$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp18$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp19$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp20$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp21$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp22$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp23$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp24$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp25$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp26$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp27$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp28$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp29$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp30$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp31$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp32$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp33$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp34$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp35$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp36$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp37$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp38$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp39$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp40$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp41$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp42$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp43$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp44$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp45$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp46$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp47$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp48$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp49$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp50$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp51$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp52$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp53$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp54$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp55$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp56$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp57$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp58$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp59$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp60$motivodeegreso_mod_imp,
       amelia_fit$imputations$imp61$motivodeegreso_mod_imp
       ) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(amelia_fit_imputations_imp1_row %in% unlist(motivo_de_egreso_a_imputar$row)) %>% 
  #FILTRAR CASOS QUE SON ILÓGICOS: MUERTES CON TRATAMIENTOS POSTERIORES (1)
  dplyr::left_join(dplyr::select(CONS_C1_df_dup_SEP_2020,row,motivodeegreso_mod_imp, fech_egres_imp,dup, duplicates_filtered,evaluacindelprocesoteraputico,fech_ing_next_treat),by=c("amelia_fit_imputations_imp1_row"="row")) %>% 
  dplyr::mutate(value_death=dplyr::case_when(value=="Death"& !is.na(fech_ing_next_treat)~1,T~0)) %>% 
  dplyr::filter(value_death!=1) %>%  
  #FILTRAR CASOS QUE SON ILÓGICOS: NO PUEDEN HABER TRATAMIENTOS EN CURSO CON TRATAMIENTOS POSTERIORES (2)
  dplyr::mutate(value_fail=dplyr::case_when(value=="Ongoing treatment"& !is.na(fech_ing_next_treat)~1,T~0)) %>% 
  dplyr::filter(value_fail!=1) %>%  
  #FILTRAR CASOS QUE SON ILÓGICOS: NO PUEDE HABER OTRA COSA QUE TRATAMIENTO EN CURSO CON FECHA DE CENSURA
  dplyr::mutate(value_ong=dplyr::case_when(value!="Ongoing treatment" & fech_egres_imp=="2019-11-13"~1,T~0)) %>% 
  dplyr::filter(value_ong!=1) %>%  
  #:#:#:#:#:
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::summarise(adm_dis=sum(value == "Administrative discharge",na.rm=T),
                    death=sum(value == "Death",na.rm=T),
                    referral=sum(value == "Referral to another treatment",na.rm=T),
                    ther_dis=sum(value == "Therapeutic discharge",na.rm=T),
                    on_treat=sum(value == "Ongoing treatment",na.rm=T),
                    dropout=sum(value =="Drop-out",na.rm=T)) %>% 
  melt(id.vars="amelia_fit_imputations_imp1_row") %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::slice_max(value) %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::mutate(n=n()) %>% 
  dplyr::mutate(emp=dplyr::case_when(variable=="adm_dis" & n>1~1,T~0)) %>% 
  dplyr::filter(emp!=1) %>% 
  dplyr::mutate(motivodeegreso_mod_imp_imputation=
                  dplyr::case_when(variable=="adm_dis"~"Administrative discharge",
                                   variable=="death"~"Death",  
                                   variable=="ther_dis"~"Therapeutic discharge",
                                   variable=="on_treat"~"Ongoing treatment",
                                   variable=="referral"~"Referral to another treatment",
                                   variable=="dropout"~"Drop-out"))

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:
#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:
CONS_C1_df_dup_SEP_2020_women_miss6<-
CONS_C1_df_dup_SEP_2020_women_miss5 %>% 
   dplyr::left_join(motivodeegreso_mod_imp_imputed[,c("amelia_fit_imputations_imp1_row","motivodeegreso_mod_imp_imputation")], by=c("row"="amelia_fit_imputations_imp1_row")) %>%
  #dplyr::filter(is.na(motivodeegreso_mod_imp)) %>% dplyr::select(row,hash_key,motivodeegreso_mod_imp_original, motivodeegreso_mod_imp_imputation,motivodeegreso_mod_imp,fech_egres_num,fech_egres_imp)
  dplyr::left_join(cbind.data.frame(motivo_de_egreso_a_imputar,value_to_impute=1),"row") %>% 
  dplyr::mutate(motivodeegreso_mod_imp=factor(
     dplyr::case_when(is.na(motivodeegreso_mod_imp) & value_to_impute==1~motivodeegreso_mod_imp_imputation,
             T~as.character(motivodeegreso_mod_imp)))) %>% 
  dplyr::select(-motivodeegreso_mod_imp_imputation,-value_to_impute) %>% 
  data.table()
#CONS_C1_df_dup_SEP_2020_women_miss9 %>% janitor::tabyl(motivodeegreso_mod_imp,motivodeegreso_mod_imp_original)
#CONS_C1_df_dup_SEP_2020_women_miss9 %>% janitor::tabyl(motivodeegreso_mod_imp_original)

CONS_C1_df_dup_SEP_2020_women_miss6 %>% janitor::tabyl(motivodeegreso_mod_imp) %>%
    dplyr::mutate(percent=scales::percent(percent)) %>%  
    knitr::kable(.,format = "html", format.args = list(decimal.mark = ".", big.mark = ","),
               caption = paste0("Table 2. Imputed Cause of Discharge vs. Original Cause of Discharge"),
               #col.names = c("Cause of Discharge","1-High Achievement", "2- Medium Achievement","3- Minimum Achievement","Null Values"),
               align =rep('c', 101)) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size = 12) %>%
  kableExtra::add_footnote("Note. NA= Null values", notation="none") %>% 
  kableExtra::scroll_box(width = "100%", height = "375px") 
#

if(nrow(CONS_C1_df_dup_SEP_2020_women_miss6)-nrow(CONS_C1_df_dup_SEP_2020_women_miss5)>0){
  warning("AGS: Some rows were added in the imputation")}
```
<br>

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss6 %>% dplyr::filter(is.na(motivodeegreso_mod_imp)) %>% dplyr::left_join(dplyr::select(CONS_C1_df_dup_SEP_2020,row,fech_egres_imp),by="row") %>% dplyr::filter(fech_egres_imp<"2019-11-13") %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss6 %>% dplyr::filter(is.na(motivodeegreso_mod_imp)) %>% nrow(),")."))`

<!--- Si no hay motivo de egreso imputado, ver si son verdaderos perdidos--->

<br>

### Biopsychosocial involvement

Another variable that is worth imputing is the Biopsychosocial involvement (n= `r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(compromiso_biopsicosocial)) %>% nrow() %>% format(big.mark=",")`). In case of ties, we selected the imputed values with the value with the minimum involvement. In case of ties, we chose the most vulnerable value.

<br>

```{r mice10_comp_biopsicosoc,eval=T, echo=T, paged.print=TRUE}
# Ver distintos valores propuestos para sustancia de inciio

#No se ve un patrón de dependencia entre el compromiso biopsicosocial y el estatus de egreso
#  table(CONS_C1_df_dup_SEP_2020_women_miss$compromiso_biopsicosocial,
#       CONS_C1_df_dup_SEP_2020_women_miss$motivodeegreso_mod_imp)

comp_biopsisoc_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
         amelia_fit$imputations$imp1$compromiso_biopsicosocial,
       amelia_fit$imputations$imp2$compromiso_biopsicosocial,
       amelia_fit$imputations$imp3$compromiso_biopsicosocial,
       amelia_fit$imputations$imp4$compromiso_biopsicosocial,
       amelia_fit$imputations$imp5$compromiso_biopsicosocial,
       amelia_fit$imputations$imp6$compromiso_biopsicosocial,
       amelia_fit$imputations$imp7$compromiso_biopsicosocial,
       amelia_fit$imputations$imp8$compromiso_biopsicosocial,
       amelia_fit$imputations$imp9$compromiso_biopsicosocial,
       amelia_fit$imputations$imp10$compromiso_biopsicosocial,
       amelia_fit$imputations$imp11$compromiso_biopsicosocial,
       amelia_fit$imputations$imp12$compromiso_biopsicosocial,
       amelia_fit$imputations$imp13$compromiso_biopsicosocial,
       amelia_fit$imputations$imp14$compromiso_biopsicosocial,
       amelia_fit$imputations$imp15$compromiso_biopsicosocial,
       amelia_fit$imputations$imp16$compromiso_biopsicosocial,
       amelia_fit$imputations$imp17$compromiso_biopsicosocial,
       amelia_fit$imputations$imp18$compromiso_biopsicosocial,
       amelia_fit$imputations$imp19$compromiso_biopsicosocial,
       amelia_fit$imputations$imp20$compromiso_biopsicosocial,
       amelia_fit$imputations$imp21$compromiso_biopsicosocial,
       amelia_fit$imputations$imp22$compromiso_biopsicosocial,
       amelia_fit$imputations$imp23$compromiso_biopsicosocial,
       amelia_fit$imputations$imp24$compromiso_biopsicosocial,
       amelia_fit$imputations$imp25$compromiso_biopsicosocial,
       amelia_fit$imputations$imp26$compromiso_biopsicosocial,
       amelia_fit$imputations$imp27$compromiso_biopsicosocial,
       amelia_fit$imputations$imp28$compromiso_biopsicosocial,
       amelia_fit$imputations$imp29$compromiso_biopsicosocial,
       amelia_fit$imputations$imp30$compromiso_biopsicosocial,
       amelia_fit$imputations$imp31$compromiso_biopsicosocial,
       amelia_fit$imputations$imp32$compromiso_biopsicosocial,
       amelia_fit$imputations$imp33$compromiso_biopsicosocial,
       amelia_fit$imputations$imp34$compromiso_biopsicosocial,
       amelia_fit$imputations$imp35$compromiso_biopsicosocial,
       amelia_fit$imputations$imp36$compromiso_biopsicosocial,
       amelia_fit$imputations$imp37$compromiso_biopsicosocial,
       amelia_fit$imputations$imp38$compromiso_biopsicosocial,
       amelia_fit$imputations$imp39$compromiso_biopsicosocial,
       amelia_fit$imputations$imp40$compromiso_biopsicosocial,
       amelia_fit$imputations$imp41$compromiso_biopsicosocial,
       amelia_fit$imputations$imp42$compromiso_biopsicosocial,
       amelia_fit$imputations$imp43$compromiso_biopsicosocial,
       amelia_fit$imputations$imp44$compromiso_biopsicosocial,
       amelia_fit$imputations$imp45$compromiso_biopsicosocial,
       amelia_fit$imputations$imp46$compromiso_biopsicosocial,
       amelia_fit$imputations$imp47$compromiso_biopsicosocial,
       amelia_fit$imputations$imp48$compromiso_biopsicosocial,
       amelia_fit$imputations$imp49$compromiso_biopsicosocial,
       amelia_fit$imputations$imp50$compromiso_biopsicosocial,
       amelia_fit$imputations$imp51$compromiso_biopsicosocial,
       amelia_fit$imputations$imp52$compromiso_biopsicosocial,
       amelia_fit$imputations$imp53$compromiso_biopsicosocial,
       amelia_fit$imputations$imp54$compromiso_biopsicosocial,
       amelia_fit$imputations$imp55$compromiso_biopsicosocial,
       amelia_fit$imputations$imp56$compromiso_biopsicosocial,
       amelia_fit$imputations$imp57$compromiso_biopsicosocial,
       amelia_fit$imputations$imp58$compromiso_biopsicosocial,
       amelia_fit$imputations$imp59$compromiso_biopsicosocial,
       amelia_fit$imputations$imp60$compromiso_biopsicosocial,
       amelia_fit$imputations$imp61$compromiso_biopsicosocial
       ) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::arrange(amelia_fit_imputations_imp1_row) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>%
  # 1-Mild 2-Moderate   3-Severe 
  dplyr::summarise(severe_3=sum(value == "3-Severe",na.rm=T),
                   mod_2=sum(value == "2-Moderate",na.rm=T),
                  mild_1=sum(value =="1-Mild",na.rm=T)) %>% 
  dplyr::ungroup() %>%
    dplyr::mutate(comp_biopsisoc_imp= dplyr::case_when(
      (severe_3>mild_1) & (severe_3>mod_2)~"3-Severe",
      (mod_2>mild_1) & (mod_2>severe_3)~"2-Moderate",
      (mild_1>mod_2) & (mild_1>severe_3)~"1-Mild"
      )) %>% 
#2) Resolve ties    
  dplyr::mutate(ties= dplyr::case_when(is.na(comp_biopsisoc_imp)~1,T~0)) %>% 
  dplyr::mutate(comp_biopsisoc_imp= dplyr::case_when(ties==1 & ((severe_3>mod_2)|(severe_3>mild_1))~"3-Severe",
                                                     ties==1 & ((mod_2>mild_1)|(mod_2>severe_3))~"2-Moderate",
                T~comp_biopsisoc_imp))

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:
##
#CONS_C1_df_dup_SEP_2020 %>% janitor::tabyl(motivodeegreso_mod_imp,evaluacindelprocesoteraputico)

CONS_C1_df_dup_SEP_2020_women_miss7<-
CONS_C1_df_dup_SEP_2020_women_miss6 %>% 
   dplyr::left_join(comp_biopsisoc_imputed[,c("amelia_fit_imputations_imp1_row","comp_biopsisoc_imp")], by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(compromiso_biopsicosocial=factor(dplyr::case_when(is.na(compromiso_biopsicosocial) ~comp_biopsisoc_imp,
                                                                        TRUE~as.character(compromiso_biopsicosocial)))) %>% 
     dplyr::mutate(compromiso_biopsicosocial=parse_factor(as.character(compromiso_biopsicosocial),levels=c('1-Mild', '2-Moderate','3-Severe'), ordered =T,trim_ws=T,include_na =F, locale=locale(encoding = "UTF-8"))) %>% 
  dplyr::select(-comp_biopsisoc_imp) %>% 
  data.table()

if(nrow(CONS_C1_df_dup_SEP_2020_women_miss7)-nrow(CONS_C1_df_dup_SEP_2020_women_miss6)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss7 %>% dplyr::filter(is.na(compromiso_biopsicosocial)) %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss7 %>% dplyr::filter(is.na(compromiso_biopsicosocial)) %>% nrow(),")."))`

<br>

### Tenure status of households

Another variable that is worth imputing is the Tenure status of households (n= `r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(tenencia_de_la_vivienda_mod)) %>% nrow() %>% format(big.mark=",")`). In case of ties, we selected the imputed values with the value with the minimum involvement. In case of ties, we kept what we thought was the most vulnerable value (discarding "Owner" or "Renting" values).

<br>

```{r mice11_tenencia_vivienda, eval=T, echo=T, paged.print=TRUE}
tenencia_de_la_vivienda_mod_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
         amelia_fit$imputations$imp1$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp2$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp3$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp4$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp5$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp6$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp7$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp8$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp9$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp10$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp11$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp12$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp13$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp14$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp15$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp16$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp17$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp18$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp19$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp20$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp21$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp22$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp23$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp24$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp25$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp26$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp27$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp28$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp29$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp30$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp31$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp32$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp33$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp34$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp35$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp36$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp37$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp38$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp39$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp40$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp41$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp42$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp43$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp44$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp45$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp46$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp47$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp48$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp49$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp50$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp51$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp52$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp53$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp54$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp55$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp56$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp57$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp58$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp59$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp60$tenencia_de_la_vivienda_mod,
       amelia_fit$imputations$imp61$tenencia_de_la_vivienda_mod
       ) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row, value) %>% 
  tally() %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::top_n(1,n) %>% 
  dplyr::ungroup()

#tenencia_de_la_vivienda_mod_imputed %>% 
#  pivot_wider(id_cols="amelia_fit_imputations_imp1_row",names_from="value", values_from="n", values_fill=0) %>% 
#  dplyr::ungroup()

tenencia_de_la_vivienda_mod_imputed_dup<-
  tenencia_de_la_vivienda_mod_imputed %>% 
    dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
    dplyr::mutate(num=n()) %>% 
    dplyr::filter(num>1) %>% 
    dplyr::ungroup() %>% 
  #1) owner, discard if it is in the maximum
    dplyr::mutate(n=dplyr::case_when(value=="Owner/Transferred dwellings/Pays Dividends"~0,T~as.numeric(n))) %>% 
    dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
    dplyr::top_n(1,n) %>% 
    dplyr::ungroup() %>% 
    dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  #2) Renting vs. stays temporarily with a relative, keep the second
    dplyr::mutate(n=dplyr::case_when(value=="Renting"~0,T~as.numeric(n))) %>% 
    dplyr::top_n(1,n) %>% 
    dplyr::ungroup() %>% 
    dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
    dplyr::mutate(n_dup=n()) 

tenencia_de_la_vivienda_mod_imputed_final<-
tenencia_de_la_vivienda_mod_imputed %>% 
    dplyr::left_join(tenencia_de_la_vivienda_mod_imputed_dup, by=c("amelia_fit_imputations_imp1_row", "value")) %>% 
  #si es vacío, y no está en la base, es valor 0 (es difícil que)
    dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
    dplyr::mutate(sum= suppressWarnings(max(num, na.rm=T))) %>% 
    dplyr::ungroup() %>% 
  #descarto los que presentaron más de un valor para una misma fila y aquellos que no fueron seleccionados
    dplyr::mutate(descartar=dplyr::case_when(sum>1 & is.na(n.y)~1,T~0)) %>% 
    dplyr::filter(descartar==0)

ifelse(nrow(tenencia_de_la_vivienda_mod_imputed_final)/length(unique(CONS_C1_df_dup_SEP_2020_women_miss7$row))>1,
       "There are still more than one value in the imputation","")
                     
#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:
#CONS_C1_df_dup_SEP_2020 %>% janitor::tabyl(motivodeegreso_mod_imp,evaluacindelprocesoteraputico)

CONS_C1_df_dup_SEP_2020_women_miss8<-
CONS_C1_df_dup_SEP_2020_women_miss7 %>% 
   dplyr::left_join(tenencia_de_la_vivienda_mod_imputed_final[,c("amelia_fit_imputations_imp1_row","value")], by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
    dplyr::mutate(tenencia_de_la_vivienda_mod=factor(dplyr::case_when(is.na(tenencia_de_la_vivienda_mod) ~value,
                                                                        TRUE~as.character(tenencia_de_la_vivienda_mod)))) %>% 
  dplyr::select(-value) %>% 
  data.table()
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss8)-nrow(CONS_C1_df_dup_SEP_2020_women_miss7)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss8 %>% dplyr::filter(is.na(tenencia_de_la_vivienda_mod)) %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss8 %>% dplyr::filter(is.na(tenencia_de_la_vivienda_mod)) %>% nrow(),")."))`

<br>

### Number of children (max. Value) (Dichotomized)

A numeric variable that had a great proportion of missing values was this (n= `r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(numero_de_hijos_mod_rec)) %>% nrow() %>% format(big.mark=",")`).

As seen in the figure above, most of the imputations were around 1 and 3 children, leaving less space for an imputation of no children or more than 3. We imputed these values, by approximating the mean of the 61 candidate values to a discrete number.

<br>

```{r mice12_no_children, warning=F,message=F, error=T, eval=T}
numero_de_hijos_mod_rec_imputed<-
  cbind.data.frame(amelia_fit$imputations$imp1$row,
         amelia_fit$imputations$imp1$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp2$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp3$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp4$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp5$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp6$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp7$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp8$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp9$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp10$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp11$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp12$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp13$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp14$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp15$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp16$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp17$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp18$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp19$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp20$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp21$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp22$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp23$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp24$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp25$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp26$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp27$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp28$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp29$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp30$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp31$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp32$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp33$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp34$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp35$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp36$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp37$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp38$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp39$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp40$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp41$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp42$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp43$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp44$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp45$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp46$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp47$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp48$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp49$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp50$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp51$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp52$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp53$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp54$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp55$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp56$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp57$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp58$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp59$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp60$numero_de_hijos_mod_rec,
       amelia_fit$imputations$imp61$numero_de_hijos_mod_rec
       )  %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::summarise(children= sum(value=="Yes"),
                   no_children= sum(value=="No")) %>% 
  dplyr::mutate(numero_de_hijos_mod_rec_imp=dplyr::case_when(children>=31~"Yes",
                                                    no_children>=31~"No"))

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:

CONS_C1_df_dup_SEP_2020_women_miss9<-
CONS_C1_df_dup_SEP_2020_women_miss8 %>% 
    dplyr::left_join(dplyr::select(numero_de_hijos_mod_rec_imputed,amelia_fit_imputations_imp1_row,numero_de_hijos_mod_rec_imp), by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
  dplyr::mutate(numero_de_hijos_mod_rec=factor(dplyr::case_when(is.na(numero_de_hijos_mod_rec)~as.character(numero_de_hijos_mod_rec_imp),T~as.character(numero_de_hijos_mod_rec)))) %>%
  dplyr::select(-numero_de_hijos_mod_rec_imp) %>% 
  data.table()
#table(is.na(CONS_C1_df_dup_SEP_2020_women_miss12$numero_de_hijos_mod_rec))
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss9)-nrow(CONS_C1_df_dup_SEP_2020_women_miss8)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss9 %>% dplyr::filter(is.na(numero_de_hijos_mod_rec)) %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss9 %>% dplyr::filter(is.na(numero_de_hijos_mod_rec)) %>% nrow(),")."))`

<br>

### Type of Program

A numeric variable that was important to impute missing values was the type of program (n= `r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(tipo_de_programa_2)) %>% nrow() %>% format(big.mark=",")`).

<br>

```{r mice13_type_of_plan, warning=F,message=F, error=T, eval=T}
tipo_de_programa_2_imputed<-
  cbind.data.frame(amelia_fit$imputations$imp1$row,
         amelia_fit$imputations$imp1$tipo_de_programa_2,
       amelia_fit$imputations$imp2$tipo_de_programa_2,
       amelia_fit$imputations$imp3$tipo_de_programa_2,
       amelia_fit$imputations$imp4$tipo_de_programa_2,
       amelia_fit$imputations$imp5$tipo_de_programa_2,
       amelia_fit$imputations$imp6$tipo_de_programa_2,
       amelia_fit$imputations$imp7$tipo_de_programa_2,
       amelia_fit$imputations$imp8$tipo_de_programa_2,
       amelia_fit$imputations$imp9$tipo_de_programa_2,
       amelia_fit$imputations$imp10$tipo_de_programa_2,
       amelia_fit$imputations$imp11$tipo_de_programa_2,
       amelia_fit$imputations$imp12$tipo_de_programa_2,
       amelia_fit$imputations$imp13$tipo_de_programa_2,
       amelia_fit$imputations$imp14$tipo_de_programa_2,
       amelia_fit$imputations$imp15$tipo_de_programa_2,
       amelia_fit$imputations$imp16$tipo_de_programa_2,
       amelia_fit$imputations$imp17$tipo_de_programa_2,
       amelia_fit$imputations$imp18$tipo_de_programa_2,
       amelia_fit$imputations$imp19$tipo_de_programa_2,
       amelia_fit$imputations$imp20$tipo_de_programa_2,
       amelia_fit$imputations$imp21$tipo_de_programa_2,
       amelia_fit$imputations$imp22$tipo_de_programa_2,
       amelia_fit$imputations$imp23$tipo_de_programa_2,
       amelia_fit$imputations$imp24$tipo_de_programa_2,
       amelia_fit$imputations$imp25$tipo_de_programa_2,
       amelia_fit$imputations$imp26$tipo_de_programa_2,
       amelia_fit$imputations$imp27$tipo_de_programa_2,
       amelia_fit$imputations$imp28$tipo_de_programa_2,
       amelia_fit$imputations$imp29$tipo_de_programa_2,
       amelia_fit$imputations$imp30$tipo_de_programa_2,
       amelia_fit$imputations$imp31$tipo_de_programa_2,
       amelia_fit$imputations$imp32$tipo_de_programa_2,
       amelia_fit$imputations$imp33$tipo_de_programa_2,
       amelia_fit$imputations$imp34$tipo_de_programa_2,
       amelia_fit$imputations$imp35$tipo_de_programa_2,
       amelia_fit$imputations$imp36$tipo_de_programa_2,
       amelia_fit$imputations$imp37$tipo_de_programa_2,
       amelia_fit$imputations$imp38$tipo_de_programa_2,
       amelia_fit$imputations$imp39$tipo_de_programa_2,
       amelia_fit$imputations$imp40$tipo_de_programa_2,
       amelia_fit$imputations$imp41$tipo_de_programa_2,
       amelia_fit$imputations$imp42$tipo_de_programa_2,
       amelia_fit$imputations$imp43$tipo_de_programa_2,
       amelia_fit$imputations$imp44$tipo_de_programa_2,
       amelia_fit$imputations$imp45$tipo_de_programa_2,
       amelia_fit$imputations$imp46$tipo_de_programa_2,
       amelia_fit$imputations$imp47$tipo_de_programa_2,
       amelia_fit$imputations$imp48$tipo_de_programa_2,
       amelia_fit$imputations$imp49$tipo_de_programa_2,
       amelia_fit$imputations$imp50$tipo_de_programa_2,
       amelia_fit$imputations$imp51$tipo_de_programa_2,
       amelia_fit$imputations$imp52$tipo_de_programa_2,
       amelia_fit$imputations$imp53$tipo_de_programa_2,
       amelia_fit$imputations$imp54$tipo_de_programa_2,
       amelia_fit$imputations$imp55$tipo_de_programa_2,
       amelia_fit$imputations$imp56$tipo_de_programa_2,
       amelia_fit$imputations$imp57$tipo_de_programa_2,
       amelia_fit$imputations$imp58$tipo_de_programa_2,
       amelia_fit$imputations$imp59$tipo_de_programa_2,
       amelia_fit$imputations$imp60$tipo_de_programa_2,
       amelia_fit$imputations$imp61$tipo_de_programa_2
       )  %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::summarise(WE= sum(value=="Women specific"),
                   GP= sum(value=="General population")) %>% 
  dplyr::mutate(tipo_de_programa_2_imp=dplyr::case_when(WE>=31~"Women specific",
                                                    GP>=31~"General population"))

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:

CONS_C1_df_dup_SEP_2020_women_miss10<-
CONS_C1_df_dup_SEP_2020_women_miss9 %>% 
    dplyr::left_join(dplyr::select(tipo_de_programa_2_imputed,amelia_fit_imputations_imp1_row,tipo_de_programa_2_imp), by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
  dplyr::mutate(tipo_de_programa_2=factor(dplyr::case_when(is.na(tipo_de_programa_2)~as.character(tipo_de_programa_2_imp),T~as.character(tipo_de_programa_2)))) %>%
  dplyr::select(-tipo_de_programa_2_imp) %>% 
  data.table()
#table(is.na(CONS_C1_df_dup_SEP_2020_women_miss12$tipo_de_programa_2))
if(nrow(CONS_C1_df_dup_SEP_2020_women_miss10)-nrow(CONS_C1_df_dup_SEP_2020_women_miss9)>0){
  warning("AGS: Some rows were added in the imputation")}
```

As a result of the imputations, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss10 %>% dplyr::filter(is.na(tipo_de_programa_2)) %>% nrow()==0,paste0(" there were no missing values."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss10 %>% dplyr::filter(is.na(tipo_de_programa_2)) %>% nrow(),")."))`

<br>

### Type of Plan

We looked over possible imputations to the type of plan (n=`r CONS_C1_df_dup_SEP_2020_women_miss %>% dplyr::filter(is.na(tipo_de_plan_res)) %>% nrow()`).

<br>

```{r mice14_tipo_plan_res,eval=T, echo=T, paged.print=TRUE}
tipo_de_plan_res_imputed<-
 cbind.data.frame(amelia_fit$imputations$imp1$row,
       amelia_fit$imputations$imp1$tipo_de_plan_res,
       amelia_fit$imputations$imp2$tipo_de_plan_res,
       amelia_fit$imputations$imp3$tipo_de_plan_res,
       amelia_fit$imputations$imp4$tipo_de_plan_res,
       amelia_fit$imputations$imp5$tipo_de_plan_res,
       amelia_fit$imputations$imp6$tipo_de_plan_res,
       amelia_fit$imputations$imp7$tipo_de_plan_res,
       amelia_fit$imputations$imp8$tipo_de_plan_res,
       amelia_fit$imputations$imp9$tipo_de_plan_res,
       amelia_fit$imputations$imp10$tipo_de_plan_res,
       amelia_fit$imputations$imp11$tipo_de_plan_res,
       amelia_fit$imputations$imp12$tipo_de_plan_res,
       amelia_fit$imputations$imp13$tipo_de_plan_res,
       amelia_fit$imputations$imp14$tipo_de_plan_res,
       amelia_fit$imputations$imp15$tipo_de_plan_res,
       amelia_fit$imputations$imp16$tipo_de_plan_res,
       amelia_fit$imputations$imp17$tipo_de_plan_res,
       amelia_fit$imputations$imp18$tipo_de_plan_res,
       amelia_fit$imputations$imp19$tipo_de_plan_res,
       amelia_fit$imputations$imp20$tipo_de_plan_res,
       amelia_fit$imputations$imp21$tipo_de_plan_res,
       amelia_fit$imputations$imp22$tipo_de_plan_res,
       amelia_fit$imputations$imp23$tipo_de_plan_res,
       amelia_fit$imputations$imp24$tipo_de_plan_res,
       amelia_fit$imputations$imp25$tipo_de_plan_res,
       amelia_fit$imputations$imp26$tipo_de_plan_res,
       amelia_fit$imputations$imp27$tipo_de_plan_res,
       amelia_fit$imputations$imp28$tipo_de_plan_res,
       amelia_fit$imputations$imp29$tipo_de_plan_res,
       amelia_fit$imputations$imp30$tipo_de_plan_res,
       amelia_fit$imputations$imp31$tipo_de_plan_res,
       amelia_fit$imputations$imp32$tipo_de_plan_res,
       amelia_fit$imputations$imp33$tipo_de_plan_res,
       amelia_fit$imputations$imp34$tipo_de_plan_res,
       amelia_fit$imputations$imp35$tipo_de_plan_res,
       amelia_fit$imputations$imp36$tipo_de_plan_res,
       amelia_fit$imputations$imp37$tipo_de_plan_res,
       amelia_fit$imputations$imp38$tipo_de_plan_res,
       amelia_fit$imputations$imp39$tipo_de_plan_res,
       amelia_fit$imputations$imp40$tipo_de_plan_res,
       amelia_fit$imputations$imp41$tipo_de_plan_res,
       amelia_fit$imputations$imp42$tipo_de_plan_res,
       amelia_fit$imputations$imp43$tipo_de_plan_res,
       amelia_fit$imputations$imp44$tipo_de_plan_res,
       amelia_fit$imputations$imp45$tipo_de_plan_res,
       amelia_fit$imputations$imp46$tipo_de_plan_res,
       amelia_fit$imputations$imp47$tipo_de_plan_res,
       amelia_fit$imputations$imp48$tipo_de_plan_res,
       amelia_fit$imputations$imp49$tipo_de_plan_res,
       amelia_fit$imputations$imp50$tipo_de_plan_res,
       amelia_fit$imputations$imp51$tipo_de_plan_res,
       amelia_fit$imputations$imp52$tipo_de_plan_res,
       amelia_fit$imputations$imp53$tipo_de_plan_res,
       amelia_fit$imputations$imp54$tipo_de_plan_res,
       amelia_fit$imputations$imp55$tipo_de_plan_res,
       amelia_fit$imputations$imp56$tipo_de_plan_res,
       amelia_fit$imputations$imp57$tipo_de_plan_res,
       amelia_fit$imputations$imp58$tipo_de_plan_res,
       amelia_fit$imputations$imp59$tipo_de_plan_res,
       amelia_fit$imputations$imp60$tipo_de_plan_res,
       amelia_fit$imputations$imp61$tipo_de_plan_res
       ) %>% 
  melt(id.vars="amelia_fit$imputations$imp1$row") %>% 
  janitor::clean_names() %>% 
  dplyr::group_by(amelia_fit_imputations_imp1_row) %>% 
  dplyr::summarise(outpatient= sum(value=="Outpatient"),
                   residential= sum(value=="Residential")) %>% 
  dplyr::mutate(tipo_de_plan_res_imp=dplyr::case_when(outpatient>=31~"Outpatient",
                                                    residential>=31~"Residential"))

#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:#:#:#::#:#:#:

CONS_C1_df_dup_SEP_2020_women_miss11<-
CONS_C1_df_dup_SEP_2020_women_miss10 %>% 
    dplyr::left_join(dplyr::select(tipo_de_plan_res_imputed,amelia_fit_imputations_imp1_row,tipo_de_plan_res_imp), by=c("row"="amelia_fit_imputations_imp1_row")) %>% 
  dplyr::mutate(tipo_de_plan_res=factor(dplyr::case_when(is.na(tipo_de_plan_res)~as.character(tipo_de_plan_res_imp),T~as.character(tipo_de_plan_res)))) %>%
  dplyr::select(-tipo_de_plan_res_imp) %>% 
  data.table()
#table(is.na(CONS_C1_df_dup_SEP_2020_women_miss11$tipo_centro_pub))
#table(is.na(CONS_C1_df_dup_SEP_2020_women_miss11$nombre_region))
```

As a result, `r ifelse(CONS_C1_df_dup_SEP_2020_women_miss11 %>% dplyr::filter(is.na(tipo_de_plan_res)) %>% nrow()==0,paste0(" there were no missing values once imputed."),paste0(" some values were not possible to impute (n=",CONS_C1_df_dup_SEP_2020_women_miss11 %>% dplyr::filter(is.na(tipo_de_plan_res)) %>% nrow(),")."))`

<br>

## Sample Characteristics

We checked the characteristics of the sample depending on type of program.

<br>

```{r bal0,eval=T, echo=T, paged.print=TRUE}                                 
#añado los imputados
CONS_C1_df_dup_SEP_2020_women_miss_after_imp<-
CONS_C1_df_dup_SEP_2020_women_miss11 %>% 
#  relocate(otras_sus1_mod, .after = last_col()) %>% 
  dplyr::left_join(dplyr::select(CONS_C1_df_dup_SEP_2020, row, fech_ing, fech_egres_imp, fech_ing_num, fech_egres_num, dias_treat_imp_sin_na,fech_ing_next_treat), by="row")%>% 
  #dplyr::filter(fech_egres_num==18213,!is.na(motivodeegreso_mod_imp)) %>% 
  dplyr::mutate(motivodeegreso_mod_imp=factor(dplyr::case_when(dias_treat_imp_sin_na>=90 & motivodeegreso_mod_imp=="Drop-out"~ "Late Drop-out",
                                                        dias_treat_imp_sin_na<90 & motivodeegreso_mod_imp=="Drop-out"~ "Early Drop-out",
                                                        fech_egres_num==18213 & is.na(motivodeegreso_mod_imp)~"Ongoing treatment",
                                                        TRUE~as.character(motivodeegreso_mod_imp)
                                                        ))) %>%
  dplyr::mutate(sum_miss = base::rowSums(is.na(dplyr::select(.,c(tipo_de_programa_2:tipo_de_plan_res))))) %>% 
  dplyr::group_by(hash_key) %>% 
  dplyr::mutate(sum_miss=sum(sum_miss)) %>% 
  dplyr::ungroup() 

CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados <-
  CONS_C1_df_dup_SEP_2020_women_miss_after_imp %>% 
  dplyr::filter(sum_miss>0)

CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados %>% 
  rowwise %>%
  dplyr::mutate_at(.vars = vars(vector_variables),
                   .funs = ~ifelse(is.na(.), 1, 0)) %>% 
  dplyr::ungroup() %>% 
  dplyr::summarise_at(vars(vector_variables),~sum(.)) %>% 
  melt

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:   
#:#:#:#:#:#:#:#:#:#BASE DE DATOS DEFINITIVA#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
CONS_C1_df_dup_SEP_2020_women_miss_after_imp %>% 
  dplyr::filter(sum_miss==0) %>% 
  dplyr::select(-sum_miss) %>% 
#DAR FORMATO ORDINAL A LAS VARIABLES
  dplyr::mutate(edad_al_ing_grupos=parse_factor(as.character(edad_al_ing_grupos),levels=c('<18-29', '30-39', '40-49', '50+'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
    dplyr::mutate(escolaridad_rec=parse_factor(as.character(escolaridad_rec),levels=c('3-Completed primary school or less', '2-Completed high school or less', '1-More than high school'), ordered =T,trim_ws=T,include_na =F, locale=locale(encoding = "Latin1"))) %>%  
  dplyr::mutate(freq_cons_sus_prin=parse_factor(as.character(freq_cons_sus_prin),levels=c('Less than 1 day a week','2 to 3 days a week','4 to 6 days a week','1 day a week or more','Daily'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
  dplyr::mutate(compromiso_biopsicosocial=parse_factor(as.character(compromiso_biopsicosocial),levels=c('1-Mild', '2-Moderate','3-Severe'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
  dplyr::mutate(num_otras_sus_mod=parse_factor(as.character(num_otras_sus_mod),levels=c('No additional substance', 'One additional substance','More than one additional substance'), ordered =T,trim_ws=F,include_na =F)) %>% #, locale=locale(encoding = "Latin1")
  dplyr::mutate(fech_ing_next_treat_date=as.Date(fech_ing_next_treat)) %>% 
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
  data.table::data.table() %>% 
    assign("CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados",.,envir=.GlobalEnv)

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$tipo_de_programa_2,"label") <- 'Type of program'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$edad_al_ing_grupos,"label") <- 'Age at admission to treatment, grouped.'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$estado_conyugal_2,"label") <- 'Marital status'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$numero_de_hijos_mod_rec,"label") <- 'Have children (Dichotomized)'

attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$sus_principal_mod,"label") <- 'Primary or main substance'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$num_otras_sus_mod,"label") <- 'Co-occurring SUD'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$freq_cons_sus_prin,"label") <- 'Consumption frequency of primary or main substance'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$compromiso_biopsicosocial,"label") <- 'Biopsychosocial involvement'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$tenencia_de_la_vivienda_mod,"label") <- 'Tenure status of households'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$escolaridad_rec,"label") <- 'Educational Attainment'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$motivodeegreso_mod_imp,"label") <- 'Cause of Discharge'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$fech_ing_next_treat_date,"label") <- 'Date of Admission to Posterior Treatment'
attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$tipo_de_plan_res,"label") <- 'Setting of Treatment'
#attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$tipo_centro,"label") <- 'Type of center of the last entry'
#attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$embarazo,"label") <- 'Pregnant at admission'
#attr(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$edad_ini_sus_prin_grupos,"label") <- 'Age at first use of principal substance, grouped'


```

<br>

`r ifelse(dim(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados)[1]>0,
       paste0('Considering that some missing values were not able to imputation (due to ties in the candidate values for imputation or inconsistent values for imputations (n=',dim(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados)[1],',users=',length(unique(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados$hash_key)),'), we ended  the process having ', nrow(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados) %>%  format(big.mark=','),' compelte cases (users= ', length(unique(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$hash_key))%>%  format(big.mark=','),').'),
       paste0('We ended the process having ', nrow(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados) %>%  format(big.mark=','),' compelte cases (users= ', length(unique(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados$hash_key))%>%  format(big.mark=','),').')
       )`

<br>

```{r bal1,eval=F, echo=T, paged.print=TRUE}                                 
kableone <- function(x, ...) {
  capture.output(x <- print(x,...))
  knitr::kable(x,format= "html", format.args= list(decimal.mark= ".", big.mark= ","))
}
Variables_after_imp<-c("estado_conyugal_2","edad_al_ing_grupos","escolaridad_rec","sus_principal_mod","freq_cons_sus_prin","compromiso_biopsicosocial","tenencia_de_la_vivienda_mod","num_otras_sus_mod","numero_de_hijos_mod_rec","motivodeegreso_mod_imp","dias_treat_imp_sin_na","tipo_de_plan_res")
catVars_after_imp<-
c("estado_conyugal_2","edad_al_ing_grupos","escolaridad_rec","sus_principal_mod","freq_cons_sus_prin","compromiso_biopsicosocial","tenencia_de_la_vivienda_mod","num_otras_sus_mod","numero_de_hijos_mod_rec","motivodeegreso_mod_imp","tipo_de_plan_res")

pre_tab1<-Sys.time()
tab1<-
CreateTableOne(vars = Variables_after_imp, 
               strata = "tipo_de_programa_2", 
               data = CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados, 
               factorVars = catVars_after_imp, 
               smd=T)
post_tab1<-Sys.time()
diff_time_tab1=post_tab1-pre_tab1

kableone(tab1, 
         caption = paste0("Table 4. Covariate Balance in the Variables of Interest"),
         col.names= c("Variables","Ambulatory","Residential", "p-values","test","SMD"),
         nonnormal= c("edad_ini_cons","edad_al_ing","fech_ing_num"),#"\\hline",
                       smd=T, test=T, varLabels=T,noSpaces=T, printToggle=T, dropEqual=F) %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover","condensed"),font_size= 11) %>%
    row_spec(1, bold = T, italic =T,color ="black",hline_after=T,extra_latex_after="\\arrayrulecolor{white}",font_size= 11) %>%
    #kableExtra::pack_rows("", 2, 2) %>% 
    scroll_box(width = "100%", height = "400px") 
#"tipo_de_plan_ambulatorio",
#https://cran.r-project.org/web/packages/tableone/vignettes/smd.html
#http://rstudio-pubs-static.s3.amazonaws.com/405765_2ce448f9bde24148a5f94c535a34b70e.html
#https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html
#https://cran.r-project.org/web/packages/tableone/tableone.pdf
#https://www.rdocumentation.org/packages/tableone/versions/0.12.0/topics/CreateTableOne

## Construct a table 
#standardized mean differences of greater than 0.1
```

## Multi-state


Some transitions were shown to be simultaneous. Small adjustment such that transitions were sequential rather than simultaneous.

<br>

```{r fig1, image-ref-for-in-text, echo=T, fig.align='center', message=FALSE, fig.caption="Figure 4.Summary of Process of Data Cleaning and Standardization, Imputation & Matching", fig.height=10, error=T, eval=T}

#  dplyr::filter(motivodeegreso_mod_imp!="En curso")%>% #Sacar los tratamientos que estén en curso 

tab1_lab<- paste0('Original C1 Dataset \n(n = ', formatC(nrow(CONS_C1), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1%>% dplyr::distinct(HASH_KEY)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab2_lab<- paste0('C1 Dataset \n(n = ', formatC(nrow(CONS_C1_df_dup_SEP_2020), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1_df_dup_SEP_2020%>% dplyr::distinct(hash_key)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab1_5_lab<- paste0('&#8226; Duplicated entries\\l &#8226; Overlapping treatments of users\\l &#8226; Intermediate events of treatment (continuous referrals)')
tab22_lab<- paste0('C1 Dataset \n(n = ', formatC(nrow(CONS_C1_df_dup_SEP_2020_women), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1_df_dup_SEP_2020_women%>% dplyr::distinct(hash_key)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab32_lab <- paste0('&#8226;Select women (n= ',formatC(CONS_C1_df_dup_SEP_2020%>% dplyr::filter(sexo_2=="Women") %>% nrow(), format='f', big.mark=',', digits=0), '; users=',formatC(CONS_C1_df_dup_SEP_2020%>% dplyr::filter(sexo_2=="Women") %>% distinct(hash_key) %>% nrow(), format='f', big.mark=',', digits=0),')\\\\l&#8226;Select first treatments (n= ',formatC(CONS_C1_df_dup_SEP_2020%>% dplyr::filter(sexo_2=="Women", dup==1) %>% nrow(), format='f', big.mark=',', digits=0), '; users=',formatC(CONS_C1_df_dup_SEP_2020%>% dplyr::filter(sexo_2=="Women", dup==1) %>% distinct(hash_key) %>% nrow(), format='f', big.mark=',', digits=0),')\\\\l')
tab3_5_lab<- paste0('C1 Dataset \n(n = ', formatC(nrow(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_descartados%>% dplyr::distinct(hash_key)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab_miss <-paste0("  Impute missing values: (n=",CONS_C1_df_dup_SEP_2020_women_miss[,..vector_variables_only_for_imputation] %>% complete.cases() %>% janitor::tabyl() %>% dplyr::filter(.=="FALSE") %>% dplyr::select(n) %>% as.numeric() %>% format(big.mark=","),")")
tab4_lab<- paste0('Imputed C1 Dataset \n(n = ', formatC(nrow(CONS_C1_df_dup_SEP_2020_women_miss_after_imp), format='f', big.mark=',', digits=0), ';\nusers: ',formatC(CONS_C1_df_dup_SEP_2020_women_miss_after_imp%>% dplyr::distinct(hash_key)%>% nrow(), format='f', big.mark=',', digits=0),')')
tab_ref_lab <- tab_miss <-paste0("&#8226; Referrals (n=",CONS_C1_df_dup_SEP_2020_women_miss_after_imp %>% dplyr::filter(motivodeegreso_mod_imp=="Referral to another treatment") %>% nrow() %>% format(big.mark=","),")\\\\l&#8226; Referrals That Had a Readmission (n=",CONS_C1_df_dup_SEP_2020_women_miss_after_imp %>% dplyr::filter(motivodeegreso_mod_imp=="Referral to another treatment", !is.na(fech_ing_next_treat)) %>% nrow() %>% format(big.mark=","),")\\\\l")
tab_final <- tab_miss <-paste0("  Imputed C1 Dataset w/o Referrals w/ Readmissions: \n(n=",CONS_C1_df_dup_SEP_2020_women_miss_after_imp %>% dplyr::mutate(cens=ifelse(motivodeegreso_mod_imp=="Referral to another treatment"& !is.na(fech_ing_next_treat),1,0)) %>% dplyr::filter(cens==0) %>% nrow() %>% format(big.mark=","),'\n users= ',CONS_C1_df_dup_SEP_2020_women_miss_after_imp %>% dplyr::mutate(cens=ifelse(motivodeegreso_mod_imp=="Referral to another treatment"& !is.na(fech_ing_next_treat),1,0)) %>% dplyr::filter(cens==0) %>% distinct(hash_key) %>% nrow() %>% format(big.mark=","),")")

#https://stackoverflow.com/questions/46750364/diagrammer-and-graphviz
#https://mikeyharper.uk/flowcharts-in-r-using-diagrammer/
#http://blog.nguyenvq.com/blog/2012/05/29/better-decision-tree-graphics-for-rpart-via-party-and-partykit/
#http://blog.nguyenvq.com/blog/2014/01/17/skeleton-to-create-fast-automatic-tree-diagrams-using-r-and-graphviz/
#https://cran.r-project.org/web/packages/DiagrammeR/vignettes/graphviz-mermaid.html
#https://stackoverflow.com/questions/39133058/how-to-use-graphviz-graphs-in-diagrammer-for-r
#https://subscription.packtpub.com/book/big_data_and_business_intelligence/9781789802566/1/ch01lvl1sec21/creating-diagrams-via-the-diagrammer-package
#https://justlegal.be/2019/05/using-flowcharts-to-display-legal-procedures/
# paste0("No. of treatments: ",table(table(t_id_1)) %>% formatC(big.mark = ","),"; No. of controls: ",table(table(c_id_1))%>% formatC(big.mark = ","))
#
library(DiagrammeR) #⋉
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Times, shape = rectangle,fontsize = 9]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab32 [label = '@@5',fontsize = 7]
      tab22 [label = '@@6']
      tab3 [label = '&#8226;Duplicated entries\\l&#8226;Intermediate events of treatment (continuous referrals)\\l',fontsize = 7]
      tab4 [label = '@@4']
      blank [label = '', width = 0.0001, height = 0.0001]
      blank1 [label = '', width = 0.0001, height = 0.0001]
      blank2 [label = '', width = 0.0001, height = 0.0001]
      blank3 [label = '', width = 0.0001, height = 0.0001]
      tab5 [label = '&#8226;Logically inconsistent candidates for imputation\\l&#8226;Ties in candidates for imputation\\l',fontsize = 7]
      tab6 [label = '@@8',fontsize = 7,style=dotted]#
      tab7 [label = '@@9',style=dotted]#

      # edge definitions with the node IDs
      tab1 -> blank [arrowhead = none,label='  Data wrangling and normalization process',fontsize = 8];
      blank -> tab3
      blank -> tab2
      tab2 -> blank1 [arrowhead = none,label='  Sample selection',fontsize = 8];
      blank1 -> tab32
      blank1 -> tab22
      tab22 -> blank2 [arrowhead = none, label= '@@7', fontsize= 8];
      blank2 -> tab5 
      blank2 -> tab4 [label='  Result of the imputation of missing values',fontsize = 8];#
      tab4 -> blank3 [arrowhead = none,label='  Unkown exact times of discharge',fontsize = 8, style=dotted];#
      blank3 -> tab6 [style=dotted]
      blank3 -> tab7 [style=dotted]
            subgraph {
              rank = same; tab3; blank;
            }
              subgraph {
              rank = same; tab32; blank1;
            }
            subgraph {
              rank = same; tab5; blank2;
            }
            subgraph {
              rank = same; tab6; blank3;
            }
      }

      [1]:  tab1_lab
      [2]:  tab2_lab
      [3]:  tab1_5_lab
      [4]:  tab4_lab
      [5]:  tab32_lab
      [6]:  tab22_lab
      [7]:  tab_miss
      [8]:  tab_ref_lab
      [9]:  tab_final
      ")
#      {rank=same; 'tab2'' -> tab3 [label='',fontsize = 11]}; #⋉
#CONS_C1_df_dup_SEP_2020_irrs_health
```

### Transition matrix


The model schematic illustrates treatment progression and the possible transitions between the states and the model structure.

<br>

```{r fig5 mstate_models, echo=T, fig.align='center', message=FALSE, fig.caption="Figure 5. Tree Structure for the Multistate System", fig.height=8, fig.width=10, error=T, eval=T}
library(igraph)

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
## 3 ESTADOS SIMPLES ##
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
links<-data.frame(stringsAsFactors=FALSE,
  from = c(rep("Admitted to\nTreatment", 2),"Therapeutic\nDischarge"),
  to = c(rep(c("Therapeutic\nDischarge"),1), rep("Readmission", 2)),
  value = c("1","2","3"))

links2<-data.frame(stringsAsFactors=FALSE,
   from = c(rep("Admitted to\nTreatment", 3),"Therapeutic\nDischarge","Discharge w/o\nClinical Advice"),
   to = c(rep(c("Therapeutic\nDischarge","Discharge w/o\nClinical Advice"),1), rep("Readmission", 3)),
   value = c("1","2","3","4","5"))

#dev.off()
#https://www.r-graph-gallery.com/248-igraph-plotting-parameters.html
#https://rstudio-pubs-static.s3.amazonaws.com/341807_7b9d1a4e787146d492115f90ad75cd2d.html
par(mfrow=c(1, 2))  
#for (i in c(2560:2660)){
  set.seed(2630) #i #2660 #2646 #2642 #2630 #2650
  co <- layout.fruchterman.reingold(graph_from_data_frame(links, directed=TRUE))
  plot(graph_from_data_frame(links, directed=TRUE),
            asp = 0,
            layout= co,
            edge.label=links$value,
            edge.label.cex=3,
            edge.label.color="black",
            #vertex.label= rev(),
            vertex.color="white",
            vertex.size=120,
            vertex.size2=25,
            vertex.label.cex=1, 
            edge.arrow.size=1,
            edge.color="black",
            vertex.shape="rectangle",
            vertex.label.color="black",
            edge.curved=0,
            edge.width=1.5,
           #main=paste0(i),
            outputorder="edgesfirst",  
            vertex.label.dist=0,
            vertex.cex = 3)
#}
title("a) Three-states Model (Simplest)", sub = "No recurring states; Absorving state: Readmission;\nOther causes of discharge were not events of interest;\nModified version of an illness-death model") ## internal titles

set.seed(10990)#i #10990 10921 10898 10835
co2 <- layout.fruchterman.reingold(graph_from_data_frame(links2, directed=TRUE))
  plot(graph_from_data_frame(links2, directed=TRUE),
            asp = 0,
            layout= co2,
            edge.label=links2$value,
            edge.label.cex=2.5,
            edge.label.color="black",
            #vertex.label= rev(),
            vertex.color="white",
            vertex.size=120,
            vertex.size2=25,
            vertex.label.cex=1, 
            edge.arrow.size=1,
            edge.color="black",
            vertex.shape="rectangle",
            vertex.label.color="black",
            edge.curved=0,
            edge.width=1.5,
            outputorder="edgesfirst",
            #main=paste0(i),
            vertex.label.dist=0,
            vertex.cex = 3)
  title("b) Four-states Model", sub = "No recurring states; Absorving state: Readmission;\nOther causes of discharge were not events of interest") ## internal titles

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
## Probando con paquetes estadísticos
if(no_mostrar==1){
library(igraph)
Nodes <- c("Admitted to\nGP","Admitted to\nWE","Therapeutic\nDischarge","Discharge w/o\nClinical Advice","Readmission") #states possible in MSM
Edges <- list("Admitted to\nGP"=list(edges=c("Therapeutic\nDischarge","Discharge w/o\nClinical Advice")),
              "Admitted to\nWE"=list(edges=c("Therapeutic\nDischarge","Discharge w/o\nClinical Advice")),
              "Therapeutic\nDischarge"=list(edges=c("Readmission")),
              "Discharge /wo\nClinical Advice"=list(edges=c("Readmission")),
              "Readmission"=list(edges=NULL)) #transitions from each state

RCLTtree <- new("graphNEL",nodes=Nodes,edgeL=Edges,edgemode="directed")
plot(RCLTtree)
#https://www.rdocumentation.org/packages/msSurv/versions/1.2-2/topics/msSurv
msSurv(LTRCdata, RCLTtree, cens.type="ind", LT=FALSE, bs=FALSE, B=200)
}
```

<br>

Any observation where an event occurs which is not the event of interest for a specific transition is treated as a censored at the end of the study (2019, November 13) observation (only referrals and also had inexact dates of discharge), that is, in the same way as a patient that was lost to follow-up. If there is a readmission posterior to loss-to follow-up cases, these cases we obtained the length in days between being readmitted posterior and the time of admission, knowing that any intermediate date of discharge was interval-censored (the exact time in which users discharged is unknown, and its treatment outcomes are unknown, so there is no exact time-to-readmission). Covariates are fixed at baseline.

<!--- 
End of study: Since calendar time restricts observation to events that occurred in the past, anevent time may be right censored because the individual has not been followed long enoughyet. This is also called administrative censoring.
Loss to follow-up: The person has left the study, e.g. because of migration or study fatigue. Hemay have experienced the event already, but this information is missing.
Competing risk: Another event has occurred, which prevents occurrence of the event ofinterest.
--->

<br>

```{r msprep_1, eval=T, echo=T, paged.print=TRUE}                                 
#Data should be in a data frame with column names "id", "stop", "st.stage", and "stage" where "id" is the individual's identification number, "stop" is the transition time from state j to j', "st.stage" is the state the individual is transitioning from (i.e., j), and "stage" is the state the individual is transitioning to (i.e., j') and equals 0 if right censored.

## 80% of sample is LT, rest has start time of 0
### AGS: Parten en 0, salvo que estén truncados a la izquierda. 
### Parece que todos comparten un mismo tiempo ojetivo.
### AGS: Cuando hay un estado seguido no es necesario interval censoring, se dn en tun tiempo continuo
### El 0 es censura

library(mstate)

#### MSPREP= 3 STATES 
#_#_#_#_#_#_#_
CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep<-
  CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados %>% 
# 2021-03-24: Eliminate cases with readmissions posterior to interval-censored discharges
  #dplyr::mutate(cens=ifelse(motivodeegreso_mod_imp=="Referral to another treatment"& !is.na(fech_ing_next_treat),1,0)) %>% dplyr::filter(cens==0) %>% 
  dplyr::mutate(ther_disch=ifelse(motivodeegreso_mod_imp=="Therapeutic discharge",1,0)) %>% 
  # para problema para intervalos 0 entre un tratamiento nuevo y otro y entre el ingreso a un tratamiento y su término y que comento más abajo
  dplyr::mutate(cambio_fecha_ing= dplyr::case_when(dias_treat_imp_sin_na==0~1 ,T~0)) %>%
  dplyr::mutate(fech_ing_num= dplyr::case_when(cambio_fecha_ing==1~fech_ing_num-1,T~fech_ing_num)) %>% 
  dplyr::mutate(dias_treat_imp_sin_na= dplyr::case_when(cambio_fecha_ing==1~fech_egres_num-fech_ing_num, T~dias_treat_imp_sin_na)) %>% 
  dplyr::select(-cambio_fecha_ing) %>% 
  #If status=1, the corresponding transition has been observed. Si no no se ha observado
  # para efectos de este modelo simple, experimentar el alta terapéutica es el objetivo, por lo que el resto será censura
  dplyr::mutate(readmission=ifelse(!is.na(fech_ing_next_treat),1,0)) %>% 
  #time of arrival at the state
  dplyr::mutate(diff_bet_treat=fech_ing_next_treat-fech_egres_num) %>% 
  # para problema para intervalos 0 entre un tratamiento nuevo y otro y entre el ingreso a un tratamiento y su término y que comento más abajo. Le añado un día
  dplyr::mutate(cambio_fecha_ing_nuevo_t= dplyr::case_when(diff_bet_treat==0~1 ,T~0)) %>%
  dplyr::mutate(fech_ing_next_treat= dplyr::case_when(cambio_fecha_ing_nuevo_t==1~fech_ing_next_treat+1,T~fech_ing_next_treat)) %>% 
  dplyr::mutate(diff_bet_treat= dplyr::case_when(cambio_fecha_ing_nuevo_t==1~fech_ing_next_treat-fech_egres_num, T~diff_bet_treat)) %>% 
  dplyr::select(-cambio_fecha_ing_nuevo_t) %>% 
  #dplyr::filter(diff_bet_treat_corr!=diff_bet_treat)
  #ADD DATES TO THE FINAL FOLLOW UP OF THE STUDY IF CENSORED
  dplyr::mutate(dias_treat_imp_sin_na= dplyr::case_when(ther_disch==0~ as.numeric(as.Date("2019-11-13"))-fech_ing_num,T~dias_treat_imp_sin_na)) %>% 

  ## 2021-03-24, I had to reespecify times to objective times, in order to avoid further problems
  dplyr::mutate(date_ther_disch= dias_treat_imp_sin_na, #fech_ing_num+ 
  ## 2021-03-24, The posterior treatment has to include the days in the previous treatment
                date_post_treat= dplyr::case_when(ther_disch==1 & readmission==1~ dias_treat_imp_sin_na+ diff_bet_treat,
                                #if the first time is censored, 
                                ther_disch==0 & readmission==1~ fech_ing_next_treat-fech_ing_num,
                                readmission==0~ as.numeric(as.Date("2019-11-13"))-fech_ing_num)) %>% 
  ## EL RESTO DE LOS PACIENTES NO VAN A HABER REGISTRADO EVENTOS EN ESE TIEMPO, POR LO QUE LLEGARÁN AL FINAL DEL SEGUIMIENTO
  dplyr::select(row, fech_ing_num, date_ther_disch, ther_disch, date_post_treat, readmission, tipo_de_programa_2:numero_de_hijos_mod_rec,tipo_de_plan_res) %>% 
  as.data.frame() 

#### MSPREP= 4 STATES 
#_#_#_#_#_#_#_
CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep2<-
  CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados %>% 
  # 2021-03-24: Eliminate cases with readmissions posterior to interval-censored discharges
  #dplyr::mutate(cens=ifelse(motivodeegreso_mod_imp=="Referral to another treatment"& !is.na(fech_ing_next_treat),1,0)) %>% dplyr::filter(cens==0) %>% 
  dplyr::mutate(ther_disch=ifelse(motivodeegreso_mod_imp=="Therapeutic discharge",1,0)) %>% 
  # For problems with 0 intervals between a new treatment and other between the admission and discharge, I subtract 1 day of admission. Then, and if there is a change in the date, we replace it. If not, we maintain the original value
  dplyr::mutate(cambio_fecha_ing= dplyr::case_when(dias_treat_imp_sin_na==0~1 ,T~0)) %>%
  dplyr::mutate(fech_ing_num= dplyr::case_when(cambio_fecha_ing==1~fech_ing_num-1,T~fech_ing_num)) %>% 
  dplyr::mutate(dias_treat_imp_sin_na= dplyr::case_when(cambio_fecha_ing==1~fech_egres_num-fech_ing_num, T~dias_treat_imp_sin_na)) %>% 
  dplyr::select(-cambio_fecha_ing) %>% 
  #If status=1, the corresponding transition has been observed. If not, it assumes not observed
  dplyr::mutate(disch_wo_clin_adv=ifelse(motivodeegreso_mod_imp %in% c("Early Drop-out","Late Drop-out","Administrative discharge"),1,0)) %>% 
  dplyr::mutate(readmission=ifelse(!is.na(fech_ing_next_treat),1,0)) %>% 
  #time of arrival at the state of readmission
  dplyr::mutate(diff_bet_treat=fech_ing_next_treat-fech_egres_num) %>% 
  # For problems with 0 intervals between a new treatment and other between the admission and discharge, I add 1 day of admission to the next treatment. Then, and if there is a change in the date, we replace it. If not, we maintain the original value
  dplyr::mutate(cambio_fecha_ing_nuevo_t= dplyr::case_when(diff_bet_treat==0~1 ,T~0)) %>%
  dplyr::mutate(fech_ing_next_treat= dplyr::case_when(cambio_fecha_ing_nuevo_t==1~fech_ing_next_treat+1,T~fech_ing_next_treat)) %>% 
  dplyr::mutate(diff_bet_treat= dplyr::case_when(cambio_fecha_ing_nuevo_t==1~fech_ing_next_treat-fech_egres_num, T~diff_bet_treat)) %>% 
  dplyr::select(-cambio_fecha_ing_nuevo_t) %>% 
  #dplyr::filter(diff_bet_treat_corr!=diff_bet_treat)
  #ADD DATES TO THE FINAL FOLLOW UP OF THE STUDY IF CENSORED
  dplyr::mutate(days_to_ther_disch= dplyr::case_when(ther_disch==0~ as.numeric(as.Date("2019-11-13"))-fech_ing_num,T~dias_treat_imp_sin_na)) %>% 
  dplyr::mutate(days_to_disch_wo_clin_adv= dplyr::case_when(disch_wo_clin_adv==0~ as.numeric(as.Date("2019-11-13"))-fech_ing_num,T~dias_treat_imp_sin_na)) %>% 

  ## 2021-03-24, I had to reespecify times to objective times, in order to avoid further problems
  dplyr::mutate(date_ther_disch= days_to_ther_disch, #fech_ing_num+ 
    date_disch_wo_clin_adv= days_to_disch_wo_clin_adv,
  ## 2021-03-24, The posterior treatment has to include the days in the previous treatment
    date_post_treat= dplyr::case_when(ther_disch==1 & readmission==1~ days_to_ther_disch+ diff_bet_treat,
                    disch_wo_clin_adv==1 & readmission==1~ days_to_disch_wo_clin_adv+ diff_bet_treat,
                    #if the first time is censored, 
                    disch_wo_clin_adv==0 & ther_disch==0 & readmission==1~ fech_ing_next_treat-fech_ing_num,
                    ther_disch==1 & disch_wo_clin_adv==0 & readmission==1~ fech_ing_next_treat-fech_ing_num,
                    readmission==0~ as.numeric(as.Date("2019-11-13"))-fech_ing_num)) %>% 
  ## EL RESTO DE LOS PACIENTES NO VAN A HABER REGISTRADO EVENTOS EN ESE TIEMPO, POR LO QUE LLEGARÁN AL FINAL DEL SEGUIMIENTO
  dplyr::select(row, fech_ing_num, date_ther_disch, ther_disch, date_disch_wo_clin_adv, disch_wo_clin_adv, date_post_treat, readmission, tipo_de_programa_2:numero_de_hijos_mod_rec,tipo_de_plan_res) %>% 
  as.data.frame() 

tail(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep) %>% 
      knitr::kable(format= "html", format.args= list(decimal.mark= ".", big.mark= ","),
               caption="Table 5a. Data in Wide, 3-states",
               align= c("c",rep('c', 5)))%>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size= 11)%>% 
  kableExtra::add_footnote("Note= Proportions from the initial state") %>% 
  kableExtra::scroll_box(width = "100%", height = "350px")

tail(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep2) %>% 
      knitr::kable(format= "html", format.args= list(decimal.mark= ".", big.mark= ","),
               caption="Table 5b. Data in Wide, 4-states",
               align= c("c",rep('c', 5)))%>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size= 11)%>% 
  kableExtra::add_footnote("Note= Proportions from the initial state") %>% 
  kableExtra::scroll_box(width = "100%", height = "350px")
```

```{r msprep_2, eval=T, echo=T, paged.print=TRUE}                                 

#For censored state transitions it can be awkward having to replicate the censoring time for each non-visited state
#https://github.com/stulacy/multistateutils
mat_3_states <- trans.illdeath(names=c("Admission","Therapeutic\nDischarge","Readmission"))
#All possible paths through the multi-state model can be found here:
#paths(mat_3_states)

#Los números son determinados por posición en cada columna (o eje Y). 
#Si uno quiere definir para la otra fila, salta al siguiente vector: 
mat_4_states<- transMat(list(c(2,3,4), 4, 4, c()), 
                names = c("Admission", "Therapeutic\nDischarge", "Discharge Without\nMedical Advice", "Readmission"))

#illness-death model without recovery
ms_CONS_C1_SEP_2020_women_imputed <- msprep(time = c(NA, "date_ther_disch", "date_post_treat"), 
                                            status = c(NA, "ther_disch", "readmission"), 
                                            data = CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep,
                                            id = "row",
                                            trans = mat_3_states,
                                            keep =  c("tipo_de_programa_2","estado_conyugal_2","edad_al_ing_grupos","escolaridad_rec","sus_principal_mod", "freq_cons_sus_prin","compromiso_biopsicosocial","tenencia_de_la_vivienda_mod","num_otras_sus_mod","numero_de_hijos_mod_rec","tipo_de_plan_res"))
#model of 5 states without recovery.
ms2_CONS_C1_SEP_2020_women_imputed <- msprep(time = c(NA, "date_ther_disch", 
                                                      "date_disch_wo_clin_adv", "date_post_treat"), 
                                            status = c(NA, "ther_disch", "disch_wo_clin_adv", "readmission"), 
                                            data = CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep2,
                                            id = "row",
                                            trans = mat_4_states,
                                            keep = c("tipo_de_programa_2","estado_conyugal_2","edad_al_ing_grupos","escolaridad_rec","sus_principal_mod", "freq_cons_sus_prin","compromiso_biopsicosocial","tenencia_de_la_vivienda_mod","num_otras_sus_mod","numero_de_hijos_mod_rec","tipo_de_plan_res"))

#Starting from state 1, simultaneous transitions possible for subjects 36666 36586 56465 136847 37595 60609 51706 76376 117544 140210 at times 126 472 32 36 1 203 45 14 5 71; smallest receiving state chosen
invisible(c("This problem responds to differences between treatments 0. Should be resolved in the initial stages"))
if(no_mostrar==1){
  CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep2 %>% 
    dplyr::filter(row %in% unlist(
      ms2_CONS_C1_SEP_2020_women_imputed %>% 
        dplyr::filter(Tstop<=Tstart) %>% 
        dplyr::select(row,from,to,trans,Tstart,Tstop,time,status) %>% 
        distinct(row)
    )) %>%
    #dplyr::mutate(diff_bet_treat=fech_ing_next_treat-fech_egres_num)%>% 
    View()
}

if(no_mostrar==1){
CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados %>% 
    dplyr::filter(row %in% unlist(
        ms2_CONS_C1_SEP_2020_women_imputed %>% 
            dplyr::filter(Tstop<=Tstart) %>% 
            dplyr::select(row,from,to,trans,Tstart,Tstop,time,status) %>% 
            distinct(row)
    )) %>%
    dplyr::select(row, motivodeegreso_mod_imp, contains("fech"))
}
invisible(c("Investigate warning"))
#37595    Administrative discharge    2013-03-18    2013-03-19    2013-03-19
#

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#SCALE INTERVALS TO YEARS
ms_CONS_C1_SEP_2020_women_imputed[, c("Tstart", "Tstop", "time")] <- ms_CONS_C1_SEP_2020_women_imputed[, c("Tstart", "Tstop", "time")]/365.25
ms2_CONS_C1_SEP_2020_women_imputed[, c("Tstart", "Tstop", "time")] <- ms2_CONS_C1_SEP_2020_women_imputed[, c("Tstart", "Tstop", "time")]/365.25
```

<br>

Now we present the transition with the frequencies and proportoins

<br>

```{r trans_matrix1,eval=T, echo=T, paged.print=TRUE}                                 
data.frame(events(ms_CONS_C1_SEP_2020_women_imputed)$Frequencies) %>% 
    dplyr::filter(to!="total entering") %>% 
    left_join(data.frame(events(ms_CONS_C1_SEP_2020_women_imputed)$Proportions), by=c("from", "to")) %>% 
    dplyr::rename("Frequencies"="Freq.x", "Proportions"="Freq.y") %>% 
    dplyr::arrange(from, to) %>% 
    dplyr::mutate(diff=ifelse(as.character(from)!=as.character(to),0,1)) %>% 
    dplyr::filter(diff==0) %>%
    dplyr::select(-diff) %>% 
    dplyr::mutate(Proportions=scales::percent(Proportions)) %>% 
    knitr::kable(format= "html", format.args= list(decimal.mark= ".", big.mark= ","),
               caption="Table 6a. Empirical State Transition Matrix, 3 States Model",
               align= c("c",rep('c', 5)))%>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size= 11)%>% 
  kableExtra::add_footnote("Note= Proportions from the initial state") %>% 
  kableExtra::scroll_box(width = "100%", height = "350px")
```

```{r trans_matrix2,eval=T, echo=T, paged.print=TRUE}                                 
data.frame(events(ms2_CONS_C1_SEP_2020_women_imputed)$Frequencies) %>% 
    dplyr::filter(to!="total entering") %>% 
    left_join(data.frame(events(ms2_CONS_C1_SEP_2020_women_imputed)$Proportions), by=c("from", "to")) %>% 
    dplyr::rename("Frequencies"="Freq.x", "Proportions"="Freq.y") %>% 
    dplyr::arrange(from, to) %>% 
    dplyr::mutate(diff=ifelse(as.character(from)!=as.character(to),0,1)) %>% 
    dplyr::filter(diff==0) %>%
    dplyr::select(-diff) %>%
    dplyr::mutate(Proportions=scales::percent(Proportions)) %>% 
    knitr::kable(format= "html", format.args= list(decimal.mark= ".", big.mark= ","),
               caption="Table 6b. Empirical State Transition Matrix, 4 States Model",
               align= c("c",rep('c', 5)))%>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size= 11)%>% 
  kableExtra::add_footnote("Note= Proportions from the initial state")%>%
  kableExtra::scroll_box(width = "100%", height = "350px")
```

<br>

### Consideration of the Appropriateness of the proportional hazards assumption


```{r ph1,eval=T, echo=T, paged.print=TRUE, fig.height=13, fig.width=10, fig.cap="Figure 6a. Vissual Assessment of Hazards, Three-states Model (w/o covars)", fig.align="center"}                                 
#reescribo el tipo de programa para indicar 0 y 1s para tratamiento vs. control
if(dimnames(table(ms_CONS_C1_SEP_2020_women_imputed$tipo_de_programa_2))[[1]][1]=="General population"){
ms_CONS_C1_SEP_2020_women_imputed$tipo_de_programa_2<-ifelse(ms_CONS_C1_SEP_2020_women_imputed$tipo_de_programa_2=="Women specific",1,0)
}
if(dimnames(table(ms2_CONS_C1_SEP_2020_women_imputed$tipo_de_programa_2))[[1]][1]=="General population"){
ms2_CONS_C1_SEP_2020_women_imputed$tipo_de_programa_2<-ifelse(ms2_CONS_C1_SEP_2020_women_imputed$tipo_de_programa_2=="Women specific",1,0)
}

# ’expand.covs()’ permits to define the set of covariates which impacts
# each transition:
#NO SE SI CONVIENE TRAER ESTA FUNCION
#data_mstate <- expand.covs(ms2_CONS_C1_SEP_2020_women_imputed, names(CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados_msprep)[-c(1:6)], append = TRUE, longnames = FALSE)

plots<- data.frame(title=rep(c("(a) Admission → Ther. Disch.","(b) Admission → Readmission","(c) Ther. Disch. → Readmission"),1),trans=rep(1:3,1))

## SIN COVARIABLES
layout(matrix(1:6, nc = 2, byrow = F))
for(i in c(1:3)){
plot(log(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==0))$time), 
     log(-log(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==0))$surv)), type="l",
     xlab="log(Years)", ylab="", xaxs="i",yaxs="i",
     las=1,cex.lab=1.5, cex.axis=1.5)
lines(log(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==1))$time), 
      log(-log(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==1))$surv)), lty=2)
legend(0,-4, c("GP", "WE"), bty="n", lty=c(2,1), cex=1.5)
title(main=paste0("LOG CUMULATIVE HAZARD VS LOG TIME PLOT \n",plots[i,"title"]), cex.main=1.5)
}

for(i in c(1:3)){
plot(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==0))$time, 
     -log(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==0))$surv), type="l",
     xlab="Years", ylab="", xaxs="i",yaxs="i", 
     las=1,cex.lab=1.5, cex.axis=1.5, col=1)
lines(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==1))$time, 
      -log(survfit(Surv(time,status)~1, data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==plots[i,"trans"] & tipo_de_programa_2==1))$surv), lty=2)
legend(6,.1, c("GP", "WE"), bty="n", lty=c(2,1), cex=1.5)
title(main=paste0("CUMULATIVE HAZARD PLOT: -LOG(KM SURVIVAL) \n",plots[i,"title"]), cex.main=1.5)
}
```

<br>

As seen n the Figure above, the cumulative hazards does not follow a proportional trend in the transitions of (b) Admission → Readmission, and (c) Ther. Disch. → Readmission between General population or Women-specific programs.

<br>

<!----
# complementary log-log discrete-time logistic regression model is the slope coefficient of the underlying proportional hazards model
# At low hazard values, the functions are virtually identical
# While the logit link builds in a proportional odds assumption in the discrete-time model, the cloglog function
builds in a proportional hazards assumption. 
#No funciona haciendo sin covariables. Si te fijas, en el ejemplo de Williams, los modelos de supervivencia son NULOS, es decir, no tienen variables de control (Surv(years,status)~ 1)
--->

```{r ph2,eval=T, echo=T, paged.print=TRUE, fig.height=20, fig.width=10, fig.cap="Figure 6b. Vissual Assessment of Hazards, Four-states Model (w/o covars)", fig.align="center"}                                 
plots2<- data.frame(title=rep(c("(a) Admission → Ther. Disch.","(b) Admission → Discharge w/o Med. Adv.","(c) Admission → Readmission", "(d) Ther. Disch. → Readmission","(e) Discharge w/o Med. Adv. → Readmission"),1),trans=1:5)

layout(matrix(1:10, nc = 2, byrow = F))
for(i in c(1:5)){
plot(log(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==0))$time), 
     log(-log(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==0))$surv)), type="l",
     xlab="log(Years)", ylab="", xaxs="i",yaxs="i",
     las=1,cex.lab=1.5, cex.axis=1.5)
lines(log(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==1))$time), 
      log(-log(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==1))$surv)), lty=2)
legend(0,-4, c("GP", "WE"), bty="n", lty=c(2,1), cex=1.5)
title(main=paste0("LOG CUMULATIVE HAZARD VS LOG TIME PLOT \n",plots2[i,"title"]), cex.main=1.5)
}

for(i in c(1:5)){
plot(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==0))$time, 
     -log(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==0))$surv), type="l",
     xlab="Years", ylab="", xaxs="i",yaxs="i", 
     las=1,cex.lab=1.5, cex.axis=1.5, col=1)
lines(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==1))$time, 
      -log(survfit(Surv(time,status)~1, data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans==plots2[i,"trans"] & tipo_de_programa_2==1))$surv), lty=2)
legend(7.5,.23, c("GP", "WE"), bty="n", lty=c(2,1), cex=1.5)
title(main=paste0("CUMULATIVE HAZARD PLOT: -LOG(KM SURVIVAL) \n",plots2[i,"title"]), cex.main=1.5)
}
```

<br>

As seen in the figures above, the transition (b) Admission → Discharge w/o Med. Adv., did not show a proportional trajectory in time between women in the General-population and Women-specific programs in the clog-log plot. On the other part, the transitions (c) Admission → Readmission, (d) Ther. Disch. → Readmission, (e) Discharge w/o Med. Adv. → Readmission did not follow proportional cumulative hazards between women in the General-Population and Women-Specific programs.

<br>

```{r info_ph_assumption,eval=F, echo=T, paged.print=TRUE}                                 
#The Coxproportional hazards model can still be used, but the interpretation of the results is different. Thiswill be outlined in some detail in Section 3

#The effect of covariates on disease progression is most often modelled using the Cox proportionalhazards model. 

#https://onlinelibrary.wiley.com/doi/epdf/10.1002/sim.2712
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

#If the SR plot for a given variable shows deviation from a straight line while it stays flat for the rest of the variables, then it is something you shouldn't ignore. First thing you can do is to look at the results of the global test. The global test might indicate the overall assumption of PH holds true [or not]. If the global test is fine then switching the reference category of the variable for which the assumption didn't held true, you might be able to achieve PH. The hazards may be proportional when compared to one reference category but not the other. Hence, by switching the reference categories, you might be able to find the category which results in PH assumption being true.

#If the switching doesn't solve your problem, and assuming you have got the right variables in your model, then this indicates that the hazards is not proportional for this particular variable i.e. different hazards at different time points. Hence, you may want to introduce interaction between variable and time in your model.

#_________
#https://stats.stackexchange.com/questions/33615/schoenfeld-residuals?rq=1
#Judgement of proportional hazards(PH) should be based on the results from a formal statistical test and the Schoenfeld residuals (SR) plot together.

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

#The best cures for some problems--running an experiment longer or doing more aggressive follow-up to avoid a large proportion of censored values, or using a large enough sample size to lessen the problems of small sample sizes--are outside the scope of statistical analysis per se.

#Alternative procedures:
#Stratification: Dividing the sample into homogeneous subsamples
#Parametric methods: Using methods that assume a specific survival distribution
#Choosing a particular nonparametric test: Situations favoring one of Mantel-Cox, Gehan-Breslow, or Tarone-Ware over the others
#Other nonparametric tests

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

#Is it possible that the analysis could be valid despite the non-proportional hazards?

#As others have mentioned, large sample size may be a factor leading to the violation of the statistical test of the PH assumption. As @EdM mentioned, it will depend on your context/knowledge of the subject as to whether the deviations matter From page 1461 of this paper

#When the sample size is small, this method may lack power to detect deviations from PH; while for large sample sizes, hypothesis tests may be over sensitive to slight deviations from this assumption.

#The answer to this question suggests that the effect of fitting a Cox model with non-proportional hazards is "slightly less power" which can be recovered with robust standard errors, leading to the hazard ratios being interpreted as the time-weighted average of the hazard ratio

#This interesting paper (Why Test for Proportional Hazards?) was published recently highlighting that there are legitimate reasons to assume violation of PH, and that one of the effects is on the interpretation rather than invalidity of the results. They actually suggest that statistical testing of PH is unnecessary if it's expected that the hazard ratio varies over time. (I'd be interested to hear what others think of this paper)

#In the section "How should hazard ratios be interpreted?" on page 1402

#As a weighted average of the time-varying hazard ratios, the hazard ratio estimate from a Cox proportional hazards model is often used as a convenient summary of the treatment effect during the follow-up. However, a hazard ratio from a Cox model needs to be interpreted as a weighted average of the true hazard ratios over the entire follow-up period. The 95% confidence interval should be estimated using a valid method such as bootstrapping and also using inverse probability weighting to adjust for losses to follow-up.
#_________
#xtna (https://stats.stackexchange.com/users/307358/xtna), Violated non-proportional hazards - Cox regression model of time-dependent covariable, URL (version: 2021-01-15): https://stats.stackexchange.com/q/505055

#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

#The Cox proportional hazards model has traditionally been applied to assess the accuracy of prognostic models. However, it may be suboptimal due to the inflexibility to model the baseline survival function and when the proportional hazards assumption is violated

#_________
#Miladinovic B, Kumar A, Mhaskar R, Kim S, Schonwetter R, Djulbegovic B (2012) A Flexible Alternative to the Cox Proportional Hazards Model for Assessing the Prognostic Accuracy of Hospice Patient Survival. PLoS ONE 7(10): e47804. https://doi.org/10.1371/journal.pone.0047804
```

### Decision whether to use Markov or Semi-Markov

For the three-states model, we only looked at transition 3 as only transition where different times entering the state. Interested in knowing the risk of readmission in completion of a treatment w/therapeutic discharge (status) from different treatments and different time to progression.

In the four-states model, we looked at transition 4 and 5.

<br>

```{r markov_semimarkov,eval=T, echo=T, paged.print=TRUE}                                 
#state arrival extended (semi-)Markov to mean that the i → j transition hazard depends on thetime of arrival at state i. 

#Build a Cox proportional hazard model including treatment and time in previous state as covariates
CoxMarkov<-coxph(Surv(Tstart,Tstop,status)~factor(tipo_de_programa_2)+Tstart,
                  data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans==3),method = "breslow") 
HR<-round(exp(coef(CoxMarkov)),2)
CI<-round(exp(confint(CoxMarkov)),2)
P<-round(coef(summary(CoxMarkov))[,5],4)
colnames(CI)<-c("Lower 95% CI","Upper 95% CI")

#In Surv(Tstart, Tstop, status) : Stop time must be > start time, NA created
CoxMarkov2<-coxph(Surv(Tstart,Tstop,status)~factor(tipo_de_programa_2)+Tstart,
                  data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans  %in% c(4,5)),method = "breslow") 
HR2<-round(exp(coef(CoxMarkov2)),2)
CI2<-round(exp(confint(CoxMarkov2)),2)
P2<-round(coef(summary(CoxMarkov2))[,5],4)
tab_cox_markov<- as.data.frame(cbind(HR2,CI2,P2))
colnames(tab_cox_markov)<-c("HR","Lower 95% CI","Upper 95% CI", "P")

#Stop time must be > start time, NA created #INVESTIGATE - RESOLVED IN 2021-03-24

rbind.data.frame(as.data.frame(cbind(HR,CI,P)),tab_cox_markov) %>% 
  data.table(keep.rownames=T) %>% 
  dplyr::rename("Terms"="rn") %>% 
  dplyr::mutate(Terms=dplyr::case_when(grepl("tipo_de_", Terms)~"Type of Program",
                                    grepl("Tstart",Terms)~"Time in previous state(in years)")) %>% 
  dplyr::mutate(P=ifelse(P==as.character("0"),"<.001",P)) %>% 
  dplyr::rename("Sig."="P") %>% 
  dplyr::mutate(`95% CIs`=paste0(`Lower 95% CI`,", ",`Upper 95% CI`)) %>% 
  dplyr::select(-`Lower 95% CI`,-`Upper 95% CI`) %>% 
  dplyr::select(Terms, HR, `95% CIs`, Sig.) %>% 
      knitr::kable(format= "html", format.args= list(decimal.mark= ".", big.mark= ","),
               caption="Table 7. PH Model incluiding time in previous state & Type of Program as a covariate",
               align= c("c",rep('c', 5)))%>%
  kableExtra::pack_rows("Three-states", 1, 2) %>% 
  kableExtra::pack_rows("Four-states", 3, 4) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),font_size= 11)%>% 
  kableExtra::scroll_box(width = "100%", height = "350px")
#a variable appears on both the left and right sides of the formula
#this warning should be normal, since we are dealing with time to arrival at a determined state.
```

<br>

The model considered the transition from intermediate states to our absorbing state (being readmitted) is explained by the time spent in the previous health state. This covariate (time in the previous state) was shown to be statistically significant (p<.001); results indicated a longer duration spent in the first treatment is associated with increased risk of readmission. Therefore, a semi-Markov (called a Markov renewal model) or clock reset approach should be undertaken for both models. They bear the advantage that information from the process history can be included as transition-specific explanatory covariates.

<br>

```{r semimarkov_add_arrival,eval=T, echo=T, paged.print=TRUE}                                 

#Since prtime only makes sense for transition 3 (PR → RelDeath), we need the transition-specific covariate
#of prtime for transition 3, which is prtime.3. The corresponding model is termed the ”state
#arrival extended Markov PH” model in the tutorial, and appears on the right of Table III.

ms_CONS_C1_SEP_2020_women_imputed$arrival<-ms_CONS_C1_SEP_2020_women_imputed$Tstart
ms2_CONS_C1_SEP_2020_women_imputed$arrival<-ms2_CONS_C1_SEP_2020_women_imputed$Tstart

ms_CONS_C1_SEP_2020_women_imputed_exp <- expand.covs(ms_CONS_C1_SEP_2020_women_imputed, "arrival", append = TRUE, longnames = FALSE)
ms2_CONS_C1_SEP_2020_women_imputed_exp <- expand.covs(ms2_CONS_C1_SEP_2020_women_imputed, "arrival", append = TRUE, longnames = FALSE)
```

<br>

### Assessment of Fit of Transitions

<!--- 
Base-case parametric functions were selected with consideration of: goodness-of-fit (assesed by MSE y visual assessment) between predicted vs. observed RFS in each treatment arm during the trial period and plausibility of long term extrapolations based on external data and clinical expert opinion. Consstent with recommended practice, the same funcional forms were used in both arms.
 Bensimon, et al., 2019
--->

We need to derive appropriate functional forms and define respective survival functions. One reason to favor patametric models is that they can be easier to generalize. Seven candidate distributions were considered to model transitions from Adm→Ther.Disch., Adm.→Readm. and Ther.Disch.→Readm., including Weibull (assume a monotonically increasing or decreasing hazard), Log-logistic (non-monotonic hazards), Gompertz (assume a monotonically increasing or decreasing hazard), Log-normal (non-monotonic hazards), Exponential (constant hazard), Gamma & Generalized gamma (more flexible). 

<!---  (non-monotonic hazards) --->

The following plots  fitted survival curves from each model (coloured lines), with the Kaplan-Meier estimate, in black, obtained from an example of Jackson available (here)[https://cran.r-project.org/web/packages/fic/vignettes/survival.pdf], added to the contributions of Wathers & Cutler available (here)[https://digitalcommons.usu.edu/cgi/viewcontent.cgi?article=1936&context=gradreports].

<br>

```{r fit1,eval=T, echo=T, paged.print=TRUE, fig.height=13, fig.width=10, fig.cap="Figure 7a. Vissual Assessment of Survival Curves, Three-states Model",fig.align="center"}

tiempo_antes_fits<-Sys.time()

#Weathers, Brandon and Cutler, Richard Dr., "Comparision of Survival Curves Between Cox Proportional 
#Hazards, Random Forests, and Conditional Inference Forests in Survival Analysis" (2017). All Graduate 
#Plan B and other Reports. 927. 
#https://digitalcommons.usu.edu/gradreports/927 

#<div style="border: 1px solid #ddd; padding: 5px; overflow-y: scroll; height:350px; overflow-x: scroll; width:100%">            
#
#https://devinincerti.com/2019/01/01/sim-mstate.html

n_trans <- max(mat_3_states, na.rm = TRUE)
fits_wei <- vector(mode = "list", length = n_trans)
fits_llogis <- vector(mode = "list", length = n_trans)
fits_gomp <- vector(mode = "list", length = n_trans)
fits_logn <- vector(mode = "list", length = n_trans)
fits_exp <- vector(mode = "list", length = n_trans)
fits_gam <- vector(mode = "list", length = n_trans)
fits_ggam <- vector(mode = "list", length = n_trans)
fits_c_wei <- vector(mode = "list", length = n_trans)
fits_c_llogis <- vector(mode = "list", length = n_trans)
fits_c_gomp <- vector(mode = "list", length = n_trans)
fits_c_logn <- vector(mode = "list", length = n_trans)
fits_c_exp <- vector(mode = "list", length = n_trans)
fits_c_gam <- vector(mode = "list", length = n_trans)
fits_c_ggam <- vector(mode = "list", length = n_trans)
km.lc<-list()
fits_cox<-list()
fits_c_cox<-list()
#"gengamma"	Generalized gamma (stable parameterisation)
#"gengamma.orig"	Generalized gamma (original parameterisation)
#"genf"	Generalized F (stable parameterisation)
#"genf.orig"	Generalized F (original parameterisation)
#"weibull"	Weibull
#"gamma"	Gamma
#"exp"	Exponential
#"lnorm"	Log-normal
#"gompertz"	Gompertz

library(flexsurv)

#Specify the formula
fitform <- Surv(time, status) ~ 1


for (i in 1:n_trans){  
  fits_wei[[i]] <- flexsurvreg(formula=fitform,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "gompertz")
}

for (i in 1:n_trans){
  fits_llogis[[i]] <- flexsurvreg(formula=fitform,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "llogis")
}

for (i in 1:n_trans){
  fits_gam[[i]] <- flexsurvreg(formula=fitform,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "gamma")
}
#LOS ERRORES OCURREN CUANDO NO HAY COVARIABLES
#In (function (q, shape, rate = 1, scale = 1/rate, lower.tail = TRUE,  ... :   NaNs produced
#gamma no funcionó: NaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs produced
for (i in 1:n_trans){
  fits_ggam[[i]] <- flexsurvreg(formula=fitform,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "gengamma")
}

for (i in 1:n_trans){
  fits_gomp[[i]] <- flexsurvreg(formula=fitform,
                                data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                                dist = "weibull")
}


for (i in 1:n_trans){
  fits_logn[[i]] <- flexsurvreg(formula=fitform,
                                data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                                dist = "lnorm")
}

for (i in 1:n_trans){
  fits_exp[[i]] <- flexsurvreg(formula=fitform,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "exp")
}

for (i in 1:n_trans){
  fits_cox[[i]] <- coxph(fitform, data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i))
}

#_#_#_#_#_#_#_#_#_#_#_#_#_
#covariates

#Specify the formula
fitform2 <- Surv(time, status) ~  edad_al_ing_grupos+ escolaridad_rec+ sus_principal_mod+ 
         freq_cons_sus_prin+ compromiso_biopsicosocial+ tenencia_de_la_vivienda_mod+ 
         num_otras_sus_mod+ numero_de_hijos_mod_rec+ factor(tipo_de_programa_2)+ tipo_de_plan_res

for (i in 1:n_trans){  
  fits_c_wei[[i]] <- flexsurvreg(formula=fitform2,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "gompertz")
}

for (i in 1:n_trans){
  fits_c_llogis[[i]] <- flexsurvreg(formula=fitform,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "llogis")
}

for (i in 1:n_trans){
  fits_c_gam[[i]] <- flexsurvreg(formula=fitform2,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "gamma")
}
#LOS ERRORES OCURREN CUANDO NO HAY COVARIABLES
#In (function (q, shape, rate = 1, scale = 1/rate, lower.tail = TRUE,  ... :   NaNs produced
#gamma no funcionó: NaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs producedNaNs produced
for (i in 1:n_trans){
  fits_c_ggam[[i]] <- flexsurvreg(formula=fitform2,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "gengamma")
}

for (i in 1:n_trans){
  fits_c_gomp[[i]] <- flexsurvreg(formula=fitform2,
                                data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                                dist = "weibull")
}


for (i in 1:n_trans){
  fits_c_logn[[i]] <- flexsurvreg(formula=fitform2,
                                data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                                dist = "lnorm")
}

for (i in 1:n_trans){
  fits_c_exp[[i]] <- flexsurvreg(formula=fitform2,
                               data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i),
                               dist = "exp")
}

for (i in 1:n_trans){
  fits_c_cox[[i]] <- coxph(fitform2, data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i))
}

for (i in 1:n_trans){
km.lc[[i]] <- survfit(formula= fitform, data = subset(ms_CONS_C1_SEP_2020_women_imputed_exp, trans == i), conf.type = "log-log")
}
transition_label<- c(`1`="Transition 1: Admission to Ther.Discharge",`2`="Transition 2: Admission to Readmission",`3`="Transition 3: Ther.Discharge to Readmission")

layout(matrix(1:6, nc = 2, byrow = F))
for (i in 1:n_trans){
plot(km.lc[[i]], col="black", xlim=c(1,12),ylim=c(.4,1)); lines(fits_wei[[i]], col="navyblue");lines(fits_gomp[[i]], col="#B89673");lines(fits_llogis[[i]], col="#A0A36D");lines(fits_gam[[i]], col="#886894");lines(fits_ggam[[i]], col="darkorchid4");lines(fits_logn[[i]], col="#496A72");lines(fits_logn[[i]], col="gray70");lines(fits_exp[[i]],col="#496A72");lines(survfit(fits_cox[[i]], conf.int = T), col = "red")

legend("bottomleft", legend = c("Kaplan-Meier","Weibull (AFT)", "Gompertz", "Log-logistic", "Gamma",
                "Generalized gamma", "Lognormal", "Exponential","Cox"), col = 
         c("black","navyblue","#B89673","#A0A36D","#886894",
           "darkorchid4","#496A72","gray70","#496A72","red"), 
       title = "Distributions", cex = .95, bty = "n", lty=1)# lty = 1:2, 
title(main=transition_label[[i]])
}
for (i in 1:n_trans){
plot(km.lc[[i]], col="black", xlim=c(1,12),ylim=c(.4,1),xlab="Years",ylab="Survival"); lines(fits_c_wei[[i]], col="navyblue");lines(fits_c_gomp[[i]], col="#B89673");lines(fits_c_llogis[[i]], col="#A0A36D");lines(fits_c_gam[[i]], col="#886894");lines(fits_c_ggam[[i]], col="darkorchid4");lines(fits_c_logn[[i]], col="#496A72");lines(fits_c_logn[[i]], col="gray70");lines(fits_c_exp[[i]],col="#496A72");lines(survfit(fits_cox[[i]], conf.int = T), col = "red")
  
legend("bottomleft", legend = c("Kaplan-Meier","Weibull (AFT)", "Gompertz", "Log-logistic", "Gamma",
                "Generalized gamma", "Lognormal", "Exponential","Cox"), col = 
         c("black","navyblue","#B89673","#A0A36D","#886894",
           "darkorchid4","#496A72","gray70","#496A72","red"), 
       title = "Distributions", cex = .95, bty = "n", lty=1)# lty = 1:2, 
title(main=paste0(transition_label[[i]], " (w/ covariates)"))
}
#</div>
tiempo_despues_fits<-Sys.time()

tiempo_fits<-tiempo_despues_fits-tiempo_antes_fits
```

<br>

Additionally, we compared the hazards of these distributions with non-parametric techniques, using a smoothed hazard function from right-censored data using kernel-based methods (as Incerti shows in his [blog](https://devinincerti.com/2019/06/18/parametric_survival.html)). The confidence interval around the predicted hazard function is estimated using bootstrapping methods of 30,000 iterations.

<br>

```{r fit2,eval=T, echo=T, paged.print=TRUE, fig.height=13, fig.width=10, fig.cap="Figure 7b. Vissual Assessment of Hazards, Three-states Model (w/o covars)",fig.align="center"}
tiempo_antes_fits2<-Sys.time()

#```{r fit,eval=T, echo=T, paged.print=TRUE, fig.height=13, fig.width=10, fig.align="center", results = 'asis'}
kernel_haz_est<-list()
kernel_haz<-list()
for (i in 1:n_trans){
library("muhaz")
kernel_haz_est[[i]] <- muhaz(ms_CONS_C1_SEP_2020_women_imputed_exp[which(ms_CONS_C1_SEP_2020_women_imputed_exp$trans==i),"time"],
                        ms_CONS_C1_SEP_2020_women_imputed_exp[which(ms_CONS_C1_SEP_2020_women_imputed_exp$trans==i),"status"])
kernel_haz[[i]] <- data.table(time = kernel_haz_est[[i]]$est.grid,
                         est = kernel_haz_est[[i]]$haz.est,
                         method = "Kernel density")
}
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#create list of survreg for different transitions
#<- flexsurvreg_list(fit1, fit2, fit3)
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_

dists <- cbind.data.frame(
              formal=c("Weibull (AFT)", "Gompertz", "Log-logistic", "Gamma",
                "Generalized gamma", "Lognormal", "Exponential"),
              model=c("wei","gomp","llogis","gam","ggam", "logn","exp"))

#hr.exp <- round(exp(coef(get(paste0("fits_",dists[x,"model"]))[[y]])["groupGood"]),3)

fitted_flexsurvreg<-data.frame()
fit_flexsurvreg<-data.frame()
for (y in 1:n_trans){
  for (x in 1:nrow(dists)){
  cat(paste0("#### Flexible Survival Model: ",dists[x,"formal"], "; transition: ",y, "\n \n"))
    #capture.output(print(get(paste0("fits_",x))[[y]]))[10:35]
    #Return fitted survival, cumulative hazard or hazard at a series of times from a fitted model
    fitted_flexsurvreg<-rbind.data.frame(fitted_flexsurvreg,
          cbind.data.frame(dist= rep(paste(dists[x,"formal"],"(",
                                           round(exp(coef(get(paste0("fits_",dists[x,"model"]))[[y]])["factor(tipo_de_programa_2)1"]),3),")"
                                           ),), trans=rep(y,),
          as.data.frame(summary(get(paste0("fits_",dists[x,"model"]))[[y]], B=30000,type = "hazard", tidy=T))))
    fit_flexsurvreg<-rbind(fit_flexsurvreg,
                      cbind(dist= dists[x,"formal"], trans=y, 
                           AIC= get(paste0("fits_",dists[x,"model"]))[[y]]$AIC,
                           Llik= get(paste0("fits_",dists[x,"model"]))[[y]]$loglik,
                           npars= get(paste0("fits_",dists[x,"model"]))[[y]]$npars
                           )
                      )
    }
}
#http://colorschemedesigner.com/csd-3.5/#
#https://www.r-graph-gallery.com/42-colors-names.html
ggplot(fitted_flexsurvreg, aes(time, est, color=dist, fill=dist))+
    geom_line(size=1)+
    #geom_ribbon(aes(ymin=lcl, ymax=ucl), alpha=.5, linetype=0) +
    scale_color_manual(name="Distributions", values = c("navyblue","#B89673","#A0A36D","#886894","darkorchid4","#496A72","gray70","#496A72")) +
    scale_fill_manual(name="Distributions", values = c("navyblue","#B89673","#A0A36D","#886894","darkorchid4","#496A72","gray70","#496A72")) +
    #scale_linetype_manual(name = "",values = c(1, rep_len(2:, n_dists)))+
    facet_wrap(~trans,labeller = labeller(trans = transition_label))+
    theme_bw()+
  theme(legend.position="bottom")

## http://www.statistica.it/gianluca/teaching/r-hta-workshop/2019/Bullement.pdf
tiempo_despues_fits2<-Sys.time()

tiempo_fits<-tiempo_despues_fits2-tiempo_antes_fits2
```

<br>

### Cumulative Hazard - Non-parametric

```{r msfit,eval=T, echo=T, paged.print=TRUE, fig.height=8, fig.width=12, fig.cap="Figure 8a. Estimate of Cumulative Hazards (Semi-Markov), Stratified by Program", fig.align="center"}
if(no_mostrar==1){
  for(i in c(1:3)){
    print(survdiff(Surv(time,status==1)~tipo_de_programa_2,data=subset(ms_CONS_C1_SEP_2020_women_imputed, trans == i)))
    }
  for(i in c(1:5)){
    print(survdiff(Surv(time,status==1)~tipo_de_programa_2,data=subset(ms2_CONS_C1_SEP_2020_women_imputed, trans == i)))
  } 
}

#We consider first the model without any proportionality assumption on the baseline hazards; this is achieved by adding strata(trans) to the formula, which estimates separate baseline hazards for different values of trans (the transitions). 

pr0 <- subset(ms_CONS_C1_SEP_2020_women_imputed, tipo_de_programa_2==0)
pr1 <- subset(ms_CONS_C1_SEP_2020_women_imputed, tipo_de_programa_2==1)
attr(pr0, "trans") <- mat_3_states
attr(pr1, "trans") <- mat_3_states

#Since there are tied event times, we need to specify ties="breslow" in order to obtain the Aalen-Johansen estimator of
#the transition probability
#If we only want the cumulative hazard for the relapse → death transition, we can
#select the rows that refer to transition 3.
#The stacked format allows to calculate all cumulative hazards via the basic coxph function.
c0 <- coxph(Surv(time, status) ~ strata(trans), 
            data = pr0, method = "breslow")
c1 <- coxph(Surv(time, status) ~ strata(trans), 
            data = pr1, method = "breslow")

#The value of time is equal to Tstop−Tstart; it is of use in ’clock reset’-models, where the time t refers to the time spent in the current state

#The alternative is to first apply the msfit function, which we also need when computing the transition
#probabilities
msf0 <- msfit(object = c0, trans = mat_3_states)
msf1 <- msfit(object = c1,  trans = mat_3_states)
#Haz contains the estimated cumulative hazard for each of the transitions for the particular patient
#specified in newd, while varHaz contains the estimated variances of these cumulative hazards,
#as well as the covariances for each combination of two transitions. All are evaluated at the
#time points for which any event in any transition occurs, possibly augmented with the largest
#(non-event) time point in the data. The summary method for msfit objects is most conveniently
#used for a summary. If we also would like to have a look at the covariances, we could set the
#argument variance equal to TRUE.

#This is a list with elements Haz (with the estimated cumulative hazard values at all event
#times), varHaz (with the covariances of each pair of estimated cumulative hazards at each
#event time point, i.e., cov( c Abgh(t), Abkl(t))), and trans, in which the transition matrix is stored
#for further use. The (co)variances of the estimated cumulative hazards may be computed in
#two different ways: by means of the Aalen estimator or by means of the Greenwood estimator.
#An advantage of the Greenwood estimator is the fact that it yields exact multinomial standard
#errors for the transition probabilities when there is no censoring. The two estimators give
#almost equal results in all practical applications.

par(mfrow = c(1, 2))
plot(msf0, cols = rep(1, 3), lwd = 2, lty = 1:3, xlab = "Years since in the state",xlim=c(0,12),ylim=c(0,.6),
 ylab = "Baseline hazards for each transition", legend.pos = c(4, .15), main= "General Population")
 plot(msf1, cols = rep(1, 3), lwd = 2, lty = 1:3, xlab = "Years after baseline", xlim=c(0,12),ylim=c(0,.6),
 ylab = "", legend.pos = c(4, .15), main= "Women Especific")
```

Looking at the instantaneous transition rates, we can observe that women in Women-specific programs had a very similar transition rate from admission to readmission with the rate of those who did not experienced it to readmission. In case of the General-population programs, after 2 years the cumulative hazards of readmission without experiencing therapeutic discharge starts growing much more than the rates of those that experienced a therapeutic discharge. In both programs, the rate of therapeutic discharge stops increasing due to restrictions to the database (treatments longer than 1095 days were not considered as valid). Must take note that we are not seeing the effect of confounders in these progressions.

<br>

### Transition Probabilites

```{r probtrans,eval=T, echo=T, paged.print=TRUE, fig.height=8, fig.width=12, fig.cap="Figure 9a. Non.parametric estimates of stacked transition probabilities inmediately after etering the state", fig.align="center"}
#. Estimation of transition probabilities The cumulative hazard is one part of the story; it reflects the instantaneous
#transition rate. But we also want to know the probability to be in each of the three states over time.

#transition probabilities

#By default, probtrans uses forward prediction,
#which means that s is kept fixed and t > s. The argument predt specifies either s or t. In this
#case (forward prediction) it specifies s. 

#tem [[i]] contains predictions from state i. Each item of the list is a data frame with time containing all event
#time points, and pstate1, pstate2, etc the probabilities of being in state 1, 2, etc, and finally
#se1, se2 etc the standard errors of these estimated probabilities. The item [[3]] contains predictions Pˆ
#3h(0, t) (we chose s = 0) starting from the RelDeath state, which is absorbing.

#We use the probtrans function to compute the estimates.

# The function probtrans() calculates the estimated transition probabilities, and optionally
#the standard errors and/or the covariances of the transition probabilities. In the case of
#non-parametric models, the user can choose between Greenwood or Aalen standard errors
#in the method argument, in accordance with the choice in msfit(). Just as in the case of
#the estimates of the hazards, the estimates of the transition probabilities themselves do not
#depend on this choice.
# The argument predt gives the starting time for prediction, that is, the starting time for
#the calculation of the transition probabilities. Two directions of prediction have been implemented, which can be specified by the #direction argument: "forward" (the default) and "fixedhorizon". 
#Any string starting with "fo" or "fi" is sufficient to distinguish between
#the two options. The "forward" option means that the prediction is made from predt; in
#P(s, t), time s remains fixed at the value predt, while time t varies from s to the last (possibly
#censored) time point in the data. The "fixedhorizon" option means that the prediction is
#made for predt; in P(s, t), time t remains fixed at the value predt and time s varies from 0
#to predt. The use of the fixed horizon option will be illustrated in Section 4.1

invisible(c("TOdavía no sé dónde poner el predt. Me pasó algo muy raro cuando lo puse en 0. er cómo interpretarlo"))

pt0 <- probtrans(msf0, predt=0)[[2]]
pt1 <- probtrans(msf1, predt=0)[[2]]

pt0_ci95 <- probtrans(msf0, predt=0)
pt1_ci95 <- probtrans(msf1, predt=0)
#Error in IplusdA[from, from] <- IplusdA[from, from] - Haztt$dhaz[j] : 
  #NAs no son permitidos en asignaciones subscritas
# Era porque no existía un estado 1000 (predt=1), el que estaba haciendo alusión al estado y no al tiempo.

#g. If the transition probabilities from
#a particular starting state are required, the argument from must be added. These results
#show how the prognosis of a patient depends on his/her starting state and on the moment
#that is taken as the starting point for prediction.


#cumulative hazards. Their incremnenst will be used in the Aalen-Johansen estimator
par(mfrow=c(1,2))
plot(pt0$time, pt0$pstate2, type="s", lwd=2, ylim= c(0,1),
     xlab="Time since randomisation (years)", ylab="Probability")
lines(pt1$time, pt1$pstate2, type="s", lwd=2, lty=3)
legend("right", c("GP", "WE"), lwd=2, lty=1:2, bty="n")
title(main="Aalen-Johansen \nP(Therapeutic Discharge|Admission)")
plot(pt0$time, pt0$pstate3, type="s", lwd=2, ylim= c(0,1),
     xlab="Time since randomisation (years)", ylab="Probability")
lines(pt1$time, pt1$pstate3, type="s", lwd=2, lty=3)
legend("right", c("GP", "WE"), lwd=2, lty=1:2, bty="n")
title(main="Aalen-Johansen \nP(Readmission|Admission)")

#LMpt0 <- LMAJ(msdata=pr0, s=1000, from=2)
#LMpt1 <- LMAJ(msdata=pr1, s=1000, from=2)
```

<br>

This figure is not quite interpretable since models do not include the effect of covariates.

<br>

```{r probs,eval=F, echo=T, paged.print=TRUE, fig.height=8, fig.width=12, fig.cap="Figure 9a. Non.parametric estimates of stacked transition probabilities inmediately 1 day admitted", fig.align="center"}

```

```{r probtrans_ci95,eval=F, echo=T, paged.print=TRUE, fig.height=13, fig.width=10, fig.cap="Figure 8a. Aalen-Johansen estimator with confidence intervals", fig.align="center"}                                 

if (no_mostrar==1){
par(mfrow=c(2,2))
plot(simdatprob[[1]]$time,simdatprob[[1]]$pstate1,type="l",ylim=c(0,1),
xlab="time",ylab="transition prob")
lines(simdatprob[[1]]$time,simdatprob[[1]]$pstate1+1.96*simdatprob[[1]])
lines(simdatprob[[1]]$time,simdatprob[[1]]$pstate1-1.96*simdatprob[[1]])
title("P(staying healthy), no transition")
plot(simdatprob[[1]]$time,simdatprob[[1]]$pstate2,type="l",ylim=c(0,1),xlab="time",ylab="transition prob") lines(simdatprob[[1]]$time,simdatprob[[1]]$pstate2+1.96*simdatprob[[1]])
lines(simdatprob[[1]]$time,simdatprob[[1]]$pstate2-1.96*simdatprob[[1]])
title("P(having disease), transition 0-1, not 1-2")
plot(simdatprob[[1]]$time,simdatprob[[1]]$pstate3,type="l",ylim=c(0,1),xlab="time",ylab="transition prob") lines(simdatprob[[1]]$time,simdatprob[[1]]$pstate3+1.96*simdatprob[[1]])
lines(simdatprob[[1]]$time,simdatprob[[1]]$pstate3-1.96*simdatprob[[1]])
title("P(Death), transitions 0-2 or 0-1-2")
plot(simdatprob[[2]]$time,simdatprob[[2]]$pstate3,type="l",ylim=c(0,1),xlab="time",ylab="transition prob") lines(simdatprob[[2]]$time,simdatprob[[2]]$pstate3+1.96*simdatprob[[2]])
lines(simdatprob[[2]]$time,simdatprob[[2]]$pstate3-1.96*simdatprob[[2]])
title("P(Death|Sick) - transition 1-2")
}

plot(pt0_ci95[[1]]$time, pt0_ci95[[1]]$pstate1, type="l",ylim=c(0,1), xlab="Years", ylab="Transition Probabilities")
lines(pt0_ci95[[1]]$time,pt0_ci95[[1]]$pstate1+1.96*pt0_ci95[[1]]$pstate1)
lines(pt0_ci95[[1]]$time,pt0_ci95[[1]]$pstate1-1.96*pt0_ci95[[1]]$pstate1)
title("P(staying healthy), no transition")


```
<br>

### Calculations of State Occupancy Probabilities



# Session Info

```{r session_info, echo=T, paged.print=TRUE}
Sys.getenv("R_LIBS_USER")
rstudioapi::getSourceEditorContext()
save.image("G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/mult_state_carla.RData")

CONS_C1_df_dup_SEP_2020_women_miss_after_imp_conservados%>%
  dplyr::arrange(hash_key, desc(fech_ing))%>% 
  rio::export(file = "G:/Mi unidad/Alvacast/SISTRAT 2019 (github)/mult_state_carla.dta")

sessionInfo()
```




